---
title: "Chemistry-Math Outcomes"
author: "Ken Field"
date: "Last compiled on `r Sys.Date()`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("ltm")) install.packages("ltm"); library(ltm) #Cronbach’s Alpha
if (!require("MASS")) install.packages("MASS"); library(MASS) #stepAIC() function
if (!require('interactions')) install.packages('interactions'); library(interactions) #Interaction plots
if (!require('sandwich')) install.packages('sandwich'); library(sandwich) #robust errors
if (!require('pheatmap')) install.packages('pheatmap'); library(pheatmap) #heatmap
if (!require('pdftools')) install.packages('pdftools'); library(pdftools) #reading tables from pdfs
if (!require('performance')) install.packages('performance'); library(performance) # visualizing glm
if (!require('pscl')) install.packages('pscl'); library(pscl) # zero-inflated glm
# Always load last
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
```

We wish to determine if the new core classes (CURE Lab and BIO Seminar) are helping students to succeed academically in other STEM classes (Chemistry and Math).

## Loading Results

I asked the registrar to help me answer the following questions:
3. What was the DFW rate for BS Biology majors in CHEM 205, CHEM 211, MATH 201, and MATH 202 from SP 2017 to FA 2019?
4. What was the DFW rate for BS Biology majors in CHEM 205, CHEM 211, MATH 201, and MATH 202 from FA 2021 to SP 2022?

They sent us the files located in the "Grade Outcomes" folder.

## Chemistry and Math

Only including data for semesters with at least 10 students (i.e. leaving out all of the Math 202 data).
This data is for BS BIOL majors (undeclared BAs are too hard to identify). 

```{r Entering Results 2}
Chem_Math_DFW <- tibble(Class = "CHEM205", Year = "17-18", Semester = "Fall", DFW = 3+1+5, Total = 63)
Chem_Math_DFW <- Chem_Math_DFW %>%
  add_row(Class = "CHEM205", Year = "18-19", Semester = "Fall", DFW = 4, Total = 55) %>%
  add_row(Class = "CHEM205", Year = "19-20", Semester = "Fall", DFW = 3+1, Total = 48) %>%
  add_row(Class = "CHEM205", Year = "21-22", Semester = "Fall", DFW = 3+2+7, Total = 62) %>%
  add_row(Class = "CHEM211", Year = "17-18", Semester = "Spring", DFW = 3+1+4, Total = 60) %>%
  add_row(Class = "CHEM211", Year = "18-19", Semester = "Spring", DFW = 3+3+8, Total = 65) %>%
  add_row(Class = "CHEM211", Year = "21-22", Semester = "Spring", DFW = 1+4, Total = 51) %>%
  add_row(Class = "MATH201", Year = "17-18", Semester = "Fall", DFW = 1+1+4, Total = 37) %>%
  add_row(Class = "MATH201", Year = "18-19", Semester = "Fall", DFW = 2+2+5, Total = 32) %>%
  add_row(Class = "MATH201", Year = "19-20", Semester = "Fall", DFW = 0+2+5, Total = 29) %>%
  add_row(Class = "MATH201", Year = "21-22", Semester = "Fall", DFW = 3+5+16, Total = 50) 
Chem_Math_DFW <- Chem_Math_DFW %>%
  mutate(Pass = Total - DFW) %>%
  mutate(`DFW Rate (%)` = DFW / Total * 100)
```

Summarize results:

```{r Chem Math Summary}
Chem_Math_DFW %>%
  group_by(Class) %>%
  summarise(`Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
Chem_Math_DFW %>%
  group_by(Year) %>%
  summarise(`Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
# Fall Semester
Chem_Math_DFW %>%
  filter(Semester == "Fall") %>%
  group_by(Class) %>%
  summarise(DFW = mean(DFW), Enrollment = mean(Total), 
            `Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
# Spring Semester
Chem_Math_DFW %>%
  filter(Semester == "Spring") %>%
  group_by(Class) %>%
  summarise(DFW = mean(DFW), Enrollment = mean(Total),
            `Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
```

Well, I don't need to do any statistics to see that things haven't improved in the last year. 
The DFW rates for BS Biology majors are higher in 21-22 than in the previous years tested. 
I will actually run the test anyway to see if they are significantly higher.

```{r}
Old_Chem_Math_DFW <- Chem_Math_DFW %>%
  filter(Year != "21-22") %>%
  select(`DFW Rate (%)`)
New_Chem_Math_DFW <- Chem_Math_DFW %>%
  filter(Year == "21-22") %>%
  select(`DFW Rate (%)`)

shapiro.test(Old_Chem_Math_DFW$`DFW Rate (%)`)
shapiro.test(New_Chem_Math_DFW$`DFW Rate (%)`)

t.test(Old_Chem_Math_DFW$`DFW Rate (%)`, New_Chem_Math_DFW$`DFW Rate (%)`)
```

The Shapiro-Wilk normality tests demonstrated no evidence that the distributions were
different from normal.

The Welch Two Sample t-test demonstrated that the DFW rates for Biology majors in their
Chemistry and Math classes are not significantly different in the old and new curricula.

This is probably due to confounding effects of the pandemic and other factors. 

To make this comparison equivalent to the Biology analysis, I should convert to a negative binomial glm.

```{r}
summary(Chem_Math_DFW)
Chem_Math_DFW_selected <- Chem_Math_DFW %>%
  select(-Pass, -`DFW Rate (%)`) %>%
  mutate(Curriculum = Year) %>%
  mutate(across(Curriculum, str_replace, '17-18|18-19|19-20', 'Prior')) %>%
  mutate(across(Curriculum, str_replace, '21-22', 'New')) %>%
  mutate(across(Curriculum, factor, levels = c("Prior", "New"))) %>%
  mutate(across(Class, str_replace, 'CHEM205|CHEM211', 'Chemistry')) %>%
  mutate(across(Class, str_replace, 'MATH201', 'Calculus'))
Chem_Math_DFW_binary_dat <- pmap_dfr(Chem_Math_DFW_selected, 
                      function(Class, Year, Semester, Curriculum, DFW, Total) {
                           data.frame(Class = as.factor(Class),
                                      Year = as.factor(Year),
                                      Semester = as.factor(Semester),
                                      Curriculum = Curriculum,
                                      DFW = c( rep(1, DFW),
                                               rep(0, Total - DFW) ) )
                      }
)
summary(Chem_Math_DFW_binary_dat)
Chem_Math.glm <- glm.nb(DFW ~ Curriculum + Semester + Class, data = Chem_Math_DFW_binary_dat) 
summary(Chem_Math.glm)
cat_plot(Chem_Math.glm, pred = Class, modx = Curriculum,  
         interval = TRUE, errorbar.width = 0.5, 
         x.label = "", y.label = "DFW Likelihood in Chemistry/Math")
```

```{r}
exp(-2.1954)
exp(-2.1954+0.8637)
exp(0.4216)
exp(0.4216+0.2024)
exp(0.4216-0.2024)
```


This analysis is more clear than the previous one. 
It shows that our First-year Biology (and affiliated) majors had 1.52-fold (SE 1.24 - 1.86) higher rates of DFW in their Chemistry and Math courses during the new curriculum than in prior semesters (p = 0.037254). 

This does not support the hypothesis that changing our Biology curriculum enabled our students to have greater success in these other classes.

But rather it probably indicates that this cohort of students had other factors that contributed to academic struggles, obviously the effects of COVID-19 played a major role. 

Conclusion: the observation that we had lower DFW rates in biology classes for this group of students is a major success for this approach because this cohort of students had significantly higher DFW rates in their chemistry and math classes.