---
title: "Outcomes"
author: "Ken Field"
date: "Last compiled on `r Sys.Date()`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("ltm")) install.packages("ltm"); library(ltm) #Cronbach’s Alpha
if (!require("MASS")) install.packages("MASS"); library(MASS) #stepAIC() function
if (!require('interactions')) install.packages('interactions'); library(interactions) #Interaction plots
if (!require('sandwich')) install.packages('sandwich'); library(sandwich) #robust errors
if (!require('pheatmap')) install.packages('pheatmap'); library(pheatmap) #heatmap
if (!require('pdftools')) install.packages('pdftools'); library(pdftools) #reading tables from pdfs
if (!require('performance')) install.packages('performance'); library(performance) # visualizing glm
if (!require('pscl')) install.packages('pscl'); library(pscl) # zero-inflated glm
if (!require('DHARMa')) install.packages('DHARMa'); library(DHARMa) # for testing glms
if (!require('car')) install.packages('car'); library(car) # for Anova
if (!require("magrittr")) install.packages("magrittr"); library(magrittr)
if (!require("conflicted")) install.packages("conflicted"); library(conflicted)
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
conflict_prefer_all("dplyr", quiet = TRUE)
```

We wish to determine if the new core classes (CURE Lab and BIO Seminar) are helping students to succeed academically.

## Loading Results

I asked the registrar to help me answer the following questions:
1. What was the DFW rate for first-year students in BIOL 205 and 206 from SP 2017 to FA 2019?
2. What was the DFW rate for all students in BIOL 201 and 202 from FA 2021 to SP 2024?

They sent us the files located in the "Grade Outcomes" folder.
I have removed any identifying information for the students and instructors.

Note that the analysis 205 and 206 only includes first-year students in these Biology classes, even though there are other students in these classes.
This is to make it more comparable to 201 and 202 which are not taken by nearly as broad a spectrum of students.

Importing data for 205 and 206.

Note that for this analysis, we have separated non-white students into Asian students and Other non-white students.

Prior to transformation, the Ethnicity data looked like:
                 Asian Black/African American        Hispanic/Latino         Multiple Races       U.S. Nonresident                  White 
                    67                     38                     71                     51                     27                    606
                    
To be consistent, we will remove the U.S. Nonresident students and combine the Black/African American, Hispanic/Latino, and Multiple Races students into the non-white category.                    

```{r Entering Results 1, echo=FALSE}
BIOL205_206 <- read_excel("Grade Outcomes/BIOL205_206 Grade Distribution_First Years by Gender & Ethnicity.xlsx", 
                          sheet = "Detail by Student") %>%
  select("Academic Period Description", "Course Identification", "Student Classification", 
         "Gender Description", "Ethnicity Description", "First-Generation Indicator", "Final Grade") %>%
  filter(`Student Classification` == "FR") %>%
  select(-`Student Classification`) %>%
  rename(Semester = `Academic Period Description`, Course = `Course Identification`,
         Gender = `Gender Description`, 
         Grade = `Final Grade`) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  mutate(across(Grade, str_replace, 'A|B|C', 'Pass')) %>%
  mutate(across(Grade, str_replace, 'Pass-', 'Pass')) %>%
  mutate(across(Grade, str_replace, 'Pass\\+', 'Pass')) %>%
  filter(`Ethnicity Description` != "Unknown") %>%
  filter(`Ethnicity Description` != "U.S. Nonresident") %>%
  mutate(`Race.Ethnicity` = case_when(
    `Ethnicity Description` == "Asian" ~ "Asian",
    `Ethnicity Description` == "Hispanic/Latino" ~ "Other non-white",
    `Ethnicity Description` == "Black/African American" ~ "Other non-white",
    `Ethnicity Description` == "Multiple Races" ~ "Other non-white",
    TRUE ~ "White"
  )) %>%
  select(-`Ethnicity Description`) %>%
  mutate(Curriculum = "Old")


names(BIOL205_206)
summary(as.factor(BIOL205_206$Course))
summary(as.factor(BIOL205_206$Grade))
summary(as.factor(BIOL205_206$Semester))
summary(as.factor(BIOL205_206$Gender))
summary(as.factor(BIOL205_206$`Race.Ethnicity`))
```

Importing data from 201 and 202.
The spreadsheets have a very awkward format and were checked carefully. 
Before I imported the data, I consolidated it within excel to make the three years have a consistent format.

```{r, echo=FALSE}
D_F_W_Report_BIOL201_202_AY21_22 <- read_excel("Grade Outcomes/D, F, W Report_BIOL201 & 202 AY21-22.v2.xlsx", 
                                               sheet = "forImport")
D_F_W_Report_BIOL201_202_AY22_23 <- read_excel("Grade Outcomes/D, F, W Report_BIOL201 & 202 AY22-23.v2.xlsx", 
                                               sheet = "forImport")
Grade_Distribution_BIOL_201_202_AY23_24 <- read_excel("Grade Outcomes/Grade Distribution_BIOL 201 & 202 AY23-24.v2.xlsx", 
                                                      sheet = "forImport")
```

Converting Totals into Passes by subtracting each D, F, or W.

```{r, echo=FALSE}
names(D_F_W_Report_BIOL201_202_AY21_22)
DFW_21_22 <- D_F_W_Report_BIOL201_202_AY21_22 %>%
  mutate(Pass_Female_White = Female_Total_White - (F_Female_White + W_Female_White)) %>%
  select(-Female_Total_White) %>%
  mutate(Pass_Male_White = Male_Total_White - (D_Male_White + W_Male_White)) %>%
  select(-Male_Total_White) %>%
  mutate(Pass_Female_nonWhite = Female_Total_nonWhite - (F_Female_nonWhite + W_Female_nonWhite)) %>%
  select(-Female_Total_nonWhite) %>%
  mutate(Pass_Male_nonWhite = Male_Total_nonWhite - (D_Male_nonWhite + W_Male_nonWhite)) %>%
  select(-Male_Total_nonWhite) %>%
  mutate(Pass_Female_Asian = Female_Total_Asian - (F_Female_Asian + W_Female_Asian)) %>%
  select(-Female_Total_Asian) %>%
  mutate(Pass_Male_Asian = Male_Total_Asian - (D_Male_Asian + W_Male_Asian)) %>%
  select(-Male_Total_Asian)

names(D_F_W_Report_BIOL201_202_AY22_23)
DFW_22_23 <- D_F_W_Report_BIOL201_202_AY22_23 %>%
  mutate(Pass_Female_White = Female_Total_White - (D_Female_White + F_Female_White + W_Female_White)) %>%
  select(-Female_Total_White) %>%
  mutate(Pass_Male_White = Male_Total_White - (W_Male_White)) %>%
  select(-Male_Total_White) %>%
  mutate(Pass_Female_nonWhite = Female_Total_nonWhite - (D_Female_nonWhite + F_Female_nonWhite + W_Female_nonWhite)) %>%
  select(-Female_Total_nonWhite) %>%
  mutate(Pass_Male_nonWhite = Male_Total_nonWhite - (W_Male_nonWhite)) %>%
  select(-Male_Total_nonWhite) %>%
  mutate(Pass_Female_Asian = Female_Total_Asian - (D_Female_Asian + F_Female_Asian + W_Female_Asian)) %>%
  select(-Female_Total_Asian) %>%
  mutate(Pass_Male_Asian = Male_Total_Asian - (W_Male_Asian)) %>%
  select(-Male_Total_Asian)

names(Grade_Distribution_BIOL_201_202_AY23_24)
DFW_23_24 <- Grade_Distribution_BIOL_201_202_AY23_24 %>%
  mutate(Pass_Female_White = Female_Total_White - (D_Female_White + F_Female_White + W_Female_White)) %>%
  select(-Female_Total_White) %>%
  mutate(Pass_Male_White = Male_Total_White - (D_Male_White + F_Male_White)) %>%
  select(-Male_Total_White) %>%
  mutate(Pass_Female_nonWhite = Female_Total_nonWhite - (D_Female_nonWhite + F_Female_nonWhite + W_Female_nonWhite)) %>%
  select(-Female_Total_nonWhite) %>%
  mutate(Pass_Male_nonWhite = Male_Total_nonWhite - (D_Male_nonWhite + F_Male_nonWhite)) %>%
  select(-Male_Total_nonWhite) %>%
  mutate(Pass_Female_Asian = Female_Total_Asian - (D_Female_Asian + F_Female_Asian + W_Female_Asian)) %>%
  select(-Female_Total_Asian) %>%
  mutate(Pass_Male_Asian = Male_Total_Asian - (D_Male_Asian + F_Male_Asian)) %>%
  select(-Male_Total_Asian)
```

Now pivoting the table and splitting the categories

```{r}
names(DFW_21_22)
DFW_21_22_long <- DFW_21_22 %>%
  pivot_longer(cols = D_Male_White:Pass_Male_Asian, 
               names_to = "Group", values_to = "Count") %>%
  separate_wider_delim(Group, delim = "_", names = c("Grade", "Gender", "Race.Ethnicity")) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  uncount(weights = Count) 
summary(as.factor(DFW_21_22_long$Grade))

names(DFW_22_23)
DFW_22_23_long <- DFW_22_23 %>%
  pivot_longer(cols = D_Female_White:Pass_Male_Asian, 
               names_to = "Group", values_to = "Count") %>%
  separate_wider_delim(Group, delim = "_", names = c("Grade", "Gender", "Race.Ethnicity")) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  uncount(weights = Count) 
summary(as.factor(DFW_22_23_long$Grade))

names(DFW_23_24)
DFW_23_24_long <- DFW_23_24 %>%
  pivot_longer(cols = D_Female_White:Pass_Male_Asian, 
               names_to = "Group", values_to = "Count") %>%
  separate_wider_delim(Group, delim = "_", names = c("Grade", "Gender", "Race.Ethnicity")) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  uncount(weights = Count) 
summary(as.factor(DFW_23_24_long$Grade))

DFW_201_202 <- DFW_21_22_long %>%
  add_row(DFW_22_23_long) %>%
  add_row(DFW_23_24_long) %>%
  mutate(Race.Ethnicity = case_when(
    Race.Ethnicity == "nonWhite" ~ "Other non-white",
    TRUE ~ Race.Ethnicity
  )) %>%
  mutate(Curriculum = "New")

```

Combining the two datasets

```{r}
All_DFW <- BIOL205_206 %>%
  select(names(DFW_201_202)) %>%
  add_row(DFW_201_202) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(Curriculum = fct_relevel(Curriculum, c("Old", "New"))) %>%
  mutate(`Race.Ethnicity` = fct_relevel(`Race.Ethnicity`, c("White", "Asian", "Other non-white")))

Only202_DFW <- All_DFW %>%
  filter(Course != "BIOL201")

summary(All_DFW)
summary(Only202_DFW)

All_DFW %>%
  filter(Course == "BIOL202") |>
  group_by(`Race.Ethnicity`) %>%
  summarise(n = n())

All_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())

Only202_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())
Only202_DFW %>%
  group_by(Course, Grade) %>%
  summarise(n = n())
```

## Modeling results with a binomial glm

Note that originally a negative binomial glm was performed, but a binomial is more appropriate now that DFW grades have been aggregated.

### Both 201 and 202

```{r, echo=FALSE, warning=FALSE}
All_DFW <- All_DFW %>%
  mutate(DFW = Grade == "DFW")

model1 <- glm.nb(DFW ~ Curriculum, data = All_DFW)
summary(model1)
model_full <- glm.nb(DFW ~ Curriculum + Gender + `Race.Ethnicity`, data = All_DFW)
summary(model_full)

binomial_model <- glm(DFW ~ Curriculum, family = "binomial", data = All_DFW)
summary(binomial_model)

full_binomial_model <- glm(DFW ~ Curriculum + Gender + `Race.Ethnicity`, family = "binomial", data = All_DFW)
summary(full_binomial_model)

Anova(full_binomial_model, type = "3", test.statistic = "F")
```



A very big effect of the new curriculum and a smaller but significant effect of Race.Ethnicity.

Removing gender from the model as it does not appear to be significant.



```{r, echo=FALSE}
selected_binomial_model <-  glm(DFW ~ Curriculum + `Race.Ethnicity`, family = "binomial", data = All_DFW)
summary(selected_binomial_model)

Anova(selected_binomial_model, type = "3", test.statistic = "F")
newdata <- data.frame(Curriculum = c("Old", "New", "Old", "New", "Old", "New")) %>%
  mutate('Race.Ethnicity' = c("White", "White", "Asian", "Asian", "Other non-white", "Other non-white"))
predict.glm(selected_binomial_model, newdata=newdata, type="response")
selected_binomial_model
check_overdispersion(selected_binomial_model)
performance(selected_binomial_model)
summary(selected_binomial_model)
```

```{r, echo=FALSE}
exp(-2.2279)
exp(-2.2279+0.130)
exp(-2.2279-0.130)
```


```{r, echo=FALSE}
1/ exp(-1.22)
1/ exp(-1.22+0.21)
1/ exp(-1.22-0.21)
```

The model indicates that students under the old curriculum were 3.4-fold (2.7 - 4.2) more likely to earn a DFW in the first two Biology courses (p = 6.11e-9). 

```{r, echo=FALSE}
exp(1.08)
exp(1.08+0.20)
exp(1.08-0.20)
```

Students of color (excluding Asian students) were 2.9-fold (2.4 - 3.6) more likely to earn a DFW than white students in both curricula (p = 4.70e-08)

```{r, Combo 201 and 202, echo=FALSE}
cat_plot(selected_binomial_model, pred = Curriculum, modx = `Race.Ethnicity`, interval = TRUE)
```

### Only 201 and 202 by Semester

We want to see how much of the difference between 201 and 202 can be explained by the semester that they are more 
likely to be offered. 

```{r, echo=FALSE}
All_DFW_Semester <- All_DFW %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring"))
Only201202_DFW_Semester <- All_DFW_Semester %>%
  filter(Course %in% c("BIOL201", "BIOL202"))

model_semester <- glm(DFW ~ FallSpring * Course, family = "binomial", data = Only201202_DFW_Semester)
summary(model_semester)
selected_model_semester <- stepAIC(model_semester)
summary(selected_model_semester)
```

This demonstrates that the DFW rates are signficantly lower in BIOL202 than BIOL201, 
after accounting for the effect of Fall versus Spring.

That is not surprising given the different objectives of these courses.


### Only 202

Adding Fall vs Spring to the full model.

```{r, echo=FALSE, warning=FALSE}
Only202_DFW <- Only202_DFW %>%
  mutate(DFW = Grade == "DFW") %>%
  mutate(Fall_Spring = case_when(str_detect(Semester, "Fall") ~ "Fall", 
                                 str_detect(Semester, "Spring") ~ "Spring"))

model1_202 <- glm(DFW ~ Curriculum, data = Only202_DFW, family = "binomial")
summary(model1_202)
model_full_202 <- glm(DFW ~ Fall_Spring + Curriculum + Gender + `Race.Ethnicity`, 
                      data = Only202_DFW,  family = "binomial")
summary(model_full_202)
```

Fall_Spring is playing a smaller, but significant, role compared to Curriculum. 
We need to account for that.

```{r, echo=FALSE, warning=FALSE}
selected_model_202 <- model_full_202 %>%
  stepAIC(direction = "backward")
summary(selected_model_202)
```


```{r, echo=FALSE}
selected_model_202
check_overdispersion(model_full_202)
performance(model_full_202)
summary(model_full_202)
Anova(model_full_202,  type = "3", test.statistic = "F")
```


Curriculum effect:

```{r, echo=FALSE}
1/ exp(-2.17)
1/ exp(-2.17+0.517)
1/ exp(-2.17-0.517)
```

The model indicates that students in CURE Lab were 8.8-fold (5.2 - 14.7) less likely to earn a DFW than in first two Biology courses of the prior curriculum (p = 2.76e-05), after controlling for the effect of semester. 


```{r, echo=FALSE}
cat_plot(model_full_202, pred = Curriculum, modx = `Race.Ethnicity`, mod2 = Fall_Spring, interval = TRUE)
```


#### Figure 8

**Now modified to separate Asian students**

```{r Figure 8, echo=FALSE}
catplot_202 <- cat_plot(model_full_202, pred = `Race.Ethnicity`, modx = Curriculum, mod2 = Fall_Spring,
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Asian Students", "Other Students\nof Color"),
         modx.labels = c("Prior", "CURE"),
         x.label = "", y.label = "DFW Likelihood")
catplot_202_fixed <- catplot_202 + theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(), 
                  axis.line = element_line(colour = "black"), 
                  legend.position="none",
                  plot.title = element_text(size = 10, face = "plain")) 

catplot_202_fixed
```

### Only 201

```{r, echo=FALSE, warning=FALSE}
Only201_DFW <- All_DFW %>%
  filter(Course != "BIOL202") %>%
  mutate(Fall_Spring = case_when(str_detect(Semester, "Fall") ~ "Fall", 
                                 str_detect(Semester, "Spring") ~ "Spring"))

summary(All_DFW)
summary(Only201_DFW)

All_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())

Only201_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())
Only201_DFW %>%
  group_by(Course, Grade) %>%
  summarise(n = n())
Only201_DFW <- Only201_DFW %>%
  mutate(DFW = Grade == "DFW")

model1_201 <- glm(DFW ~ Curriculum, data = Only201_DFW, family = "binomial")
summary(model1_201)
model_full_201 <- glm(DFW ~ Fall_Spring + Curriculum + Gender + `Race.Ethnicity`, 
                         data = Only201_DFW, family = "binomial")
summary(model_full_201)
```


```{r, echo=FALSE}
1/ exp(-0.9367)
1/ exp(-0.9367 +0.2122)
1/ exp(-0.9367 -0.2122)
```

The model indicates that students in BIOL 201 were 2.6-fold (2.1 - 3.1) less likely to earn a DFW than in first two Biology courses of the prior curriculum (p = 2.01e-05), after controlling for the effect of semester.

```{r, echo=FALSE}
exp(0.5556)
exp(0.5556+0.1779)
exp(0.5556-0.1779)
```

```{r, echo=FALSE}
cat_plot(model_full_201, pred = Curriculum, modx = Race.Ethnicity, interval = TRUE)
```


#### Figure 8 201 version

```{r Figure 9 201, echo=FALSE}
catplot_201 <- cat_plot(model_full_201, pred = `Race.Ethnicity`, modx = Curriculum, mod2 = Fall_Spring,
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Asian Students", "Other Students\nof Color"),
         modx.labels = c("Prior", "CURE"),
         x.label = "", y.label = "DFW Likelihood")
catplot_201_fixed <- catplot_201 + theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(), 
                  axis.line = element_line(colour = "black"), 
                  legend.position="none",
                  plot.title = element_text(size = 10, face = "plain")) 

catplot_201_fixed
```

## First-gen status

One of the studies of COVID impacts demonstrated that first-gen students were more highly impacted than other students.
We would like to see how that factor translates to our outcomes.

```{r, echo=FALSE}
Firstgen_201_202 <- read_excel("Grade Outcomes/Grade Distribution_BIOL 201 & 202_2021 to 2024.Firstgen.xlsx", 
                               sheet = "Grade Detail", col_types = c("skip", "text", "text", 
                                                                     "text", "text", "skip", "text", "text"))
Firstgen_201_202 <- Firstgen_201_202 %>%
  select(Course = `Course Identification`, Semester = `Academic Period Description`, `Final Grade`,
         Gender = `Gender Description`, `First-Generation Indicator`) %>%
  filter(`Final Grade` != "NC")
Firstgen_201_202_clean <- Firstgen_201_202 %>%
  mutate(Grade = case_when(`Final Grade` %in% c("D", "F", "W") ~ "DFW",
                           .default = "Pass")) %>%
  mutate(Curriculum = "New") %>%
  select(-`Final Grade`)

All_DFW_Firstgen <- BIOL205_206 %>%
  select(names(Firstgen_201_202_clean)) %>%
  add_row(Firstgen_201_202_clean) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(Curriculum = fct_relevel(Curriculum, c("Old", "New"))) %>%
  mutate(Fall_Spring = case_when(str_detect(Semester, "Fall") ~ "Fall", 
                                 str_detect(Semester, "Spring") ~ "Spring")) %>%
  mutate(Fall_Spring = as.factor(Fall_Spring)) %>%
  mutate(DFW = (Grade == "DFW"))

Only202_DFW_Firstgen <- All_DFW_Firstgen %>%
  filter(Course != "BIOL201")
Only201_DFW_Firstgen <- All_DFW_Firstgen %>%
  filter(Course != "BIOL202")

summary(All_DFW_Firstgen)
summary(Only202_DFW_Firstgen)

All_DFW_Firstgen %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())

Only202_DFW_Firstgen %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())

Only202_DFW_Firstgen %>%
  group_by(Course, Grade) %>%
  summarise(n = n())

Only202_DFW_Firstgen %>%
  group_by(Curriculum, Grade, `First-Generation Indicator`) %>%
  summarise(n = n())
```

```{r, echo=FALSE, warning=FALSE}
model1_Firstgen_202 <- glm(DFW ~ `First-Generation Indicator` * Curriculum, 
                           data = Only202_DFW_Firstgen, family = "binomial")
summary(model1_Firstgen_202)
model_full_Firstgen_202 <- glm(DFW ~ `First-Generation Indicator` * Fall_Spring * Curriculum, 
                               data = Only202_DFW_Firstgen, family = "binomial")
summary(model_full_Firstgen_202)
```


```{r, echo=FALSE, warning=FALSE}
selected_model_Firstgen_202 <- model_full_Firstgen_202 %>%
  stepAIC(direction = "backward")
summary(selected_model_Firstgen_202)
```


```{r}
# First gen
exp(0.4747)
exp(0.4747-0.2849)
exp(0.4747+0.2849)
# Race.Ethnicity (from earlier 202 model)
exp(0.3754)
exp(0.3754-0.2567)
exp(0.3754+0.2567)
```


That analysis showed that including first-generation status marginally improved the model, but it was very minor compared to semester and curriculum. This was true for both the effect size and the significance.

The effect size of first-gen status (1.61 (1.21-2.13)) and significance (p = 0.0957) was similar to the effect of Race.Ethnicity in the earlier model, (1.46 (1.12-1.88), p = 0.1436), after accounting for the effects of semester and curriculum.

