---
title: "Post Benefits Question"
author: "Ken Field"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("ltm")) install.packages("ltm"); library(ltm) #Cronbach’s Alpha
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
```

## Loading Results

Loading in the results without instructor information. 
Note that because we want to analyze demographics for this question, we cannot look at instructor because that would lead to individuals being identifiable. 
We also need to be careful about looking at both gender and race at the same time.

```{r}
NoInstructor <- read_delim("Deidentified Surveys/NoInstructor.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
NoInstructorQuestions <- read_delim("Deidentified Surveys/NoInstructorQuestions.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
```

## Benefits of research experience

This question (post-survey question 10) was only in the post-survey.
I am going to try to keep the demographics for this analysis later.

Note that pre-survey question 10 matched with post-survey question 9, while pre-survey question 11 matched with post-survey question 13. Post-survey question 10 was not matched with a pre-survey question.

```{r Post Q10}
PostQ10 <- NoInstructor %>%
  select(Semester_pre, ends_with("_post")) %>%
  select(Semester = Semester_pre, Gender = Q2_post, Ethnicity = Q3_post, starts_with("Q10"))

Q10Text <- NoInstructorQuestions %>%
  filter(startsWith(value, "Q10")) %>%
  filter(endsWith(value, "_post"))
Q10Text$Question[01]
Q10TextClean <- Q10Text %>%
  mutate(Question = str_remove(Q10Text$Question, "In this section of the survey you will be asked to consider a variety of possible benefits you may have gained from your research experience. If for any reason you prefer not to answer, or consider the question irrelevant to you, please choose the \"\"Not applicable / Prefer not to answer\"\" option - "))
Q10TextClean$Question
```

Now to see the responses:

```{r}
head(PostQ10)
Q10Factors <- PostQ10 %>%
  select(starts_with("Q")) %>%
  mutate_all(funs(ordered(.,(levels = c("Very large gain", "Large gain", 
                                       "Moderate gain", "Small gain", 
                                       "No gain or very small gain"))))) 
Q10Clean <- PostQ10 %>%
  select(-starts_with("Q")) %>%
  cbind(Q10Factors) %>%
  mutate(Gender = as.factor(Gender)) %>%
  mutate(Ethnicity = as.factor(Ethnicity))
summary(Q10Clean)
```

```{r}
dataQ10 <- as.data.frame(table(Q10Clean$Q10_1_post)) %>%
  full_join(as.data.frame(table(Q10Clean$Q10_2_post)), by = "Var1") %>% 
  full_join(as.data.frame(table(Q10Clean$Q10_3_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_4_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_5_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_6_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_7_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_8_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_9_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_10_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_11_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_12_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_13_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_14_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_15_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_16_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_17_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_18_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_19_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_20_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_21_post)), by = "Var1") 

names(dataQ10) <- c("Var1", names(Q10Clean)[4:24])
names(dataQ10) <- gsub("_post", "", names(dataQ10))
rownames(dataQ10) <- dataQ10$Var1
dataQ10 <- dataQ10 %>%
  select(-Var1)

ggballoonplot(t(dataQ10))

print("In this section of the survey you will be asked to consider a variety of possible benefits you may have gained from your research experience. If for any reason you prefer not to answer, or consider the question irrelevant to you, please choose the Not applicable / Prefer not to answer option - ")

print(Q10TextClean)
```

## Cleaning Demographics 

```{r Demographics}
Q10 <- Q10Clean 
names(Q10) <- gsub("Q10_", "Q", names(Q10))
names(Q10) <- gsub("_post", "", names(Q10))
# Remove two individuals to avoid identification
Q10_demo <- Q10 %>%
  filter(Gender %in% c("Male", "Female")) 
Q10_demo <- Q10_demo %>%
  filter(Ethnicity != "Prefer not to answer") %>% 
  mutate(Race = recode(Ethnicity, "White" = "white", .default = "non-white")) %>%
  select(-Ethnicity) %>%
  rename(Q01=Q1, Q02=Q2, Q03=Q3, Q04=Q4, Q05=Q5, Q06=Q6, Q07=Q7, Q08=Q8, Q09=Q9)

```

## Bar plots

```{r Q10 Bar}
ggplot(Q10_demo) +
  geom_bar(aes(x = Gender, fill = Q01), position = 'fill', width = 0.5, na.rm = TRUE) +
  facet_grid(Q10_demo$Race) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Gender') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

Because of the small numbers, we will not look at each question by both Gender and Race.

Instead I will prepare the data to look at all of the questions at once.

```{r}
Q10_demo_long <- Q10_demo %>% 
  pivot_longer(cols = `Q01`:`Q21`, 
               names_to = "Question", 
               values_to = "Response")
```

```{r Q10 By Gender, fig.width=4, fig.height=8}
ggplot(Q10_demo_long) +
  geom_bar(aes(x = Gender, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_long$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Gender') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

```{r Q10 By Race, fig.width=4, fig.height=8}
ggplot(Q10_demo_long) +
  geom_bar(aes(x = Race, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_long$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Race') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

## Statistical models

For each question, testing whether gender or race were significant.
I am also including semester because we expect students who have had a prior semester of the new Biology core to also have had some influence on their responses.

Note that the dependent variable in the model is calculated as "5-as.numeric(Response)" because the responses range from 1=Very large gain to 5=No gain or very small gain. 
This converts the response variable into a numeric value from 0 to 4 with a positive estimate meaning an improvement in the response on the qualitative scale.

```{r Q01 model}
print(Q10TextClean$Question[01])
Q01_select <- Q10_demo_long %>%
  filter(Question == "Q01") %>%
  na.omit() 
Q01_model <- glm(data = Q01_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q01_model)
```

```{r Q02 model}
print(Q10TextClean$Question[02])
Q02_select <- Q10_demo_long %>%
  filter(Question == "Q02") %>%
  na.omit() 
Q02_model <- glm(data = Q02_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q02_model)
```

```{r Q03 model}
print(Q10TextClean$Question[03])
Q03_select <- Q10_demo_long %>%
  filter(Question == "Q03") %>%
  na.omit() 
Q03_model <- glm(data = Q03_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q03_model)

Q03_select %>% group_by(Response) %>% tally()
```

```{r Q04 model}
print(Q10TextClean$Question[04])
Q04_select <- Q10_demo_long %>%
  filter(Question == "Q04") %>%
  na.omit() 
Q04_model <- glm(data = Q04_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q04_model)
```

```{r Q05 model}
print(Q10TextClean$Question[05])
Q05_select <- Q10_demo_long %>%
  filter(Question == "Q05") %>%
  na.omit() 
Q05_model <- glm(data = Q05_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q05_model)
```

```{r Q06 model}
print(Q10TextClean$Question[06])
Q06_select <- Q10_demo_long %>%
  filter(Question == "Q06") %>%
  na.omit() 
Q06_model <- glm(data = Q06_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q06_model)
```

```{r Q07 model}
print(Q10TextClean$Question[07])
Q07_select <- Q10_demo_long %>%
  filter(Question == "Q07") %>%
  na.omit() 
Q07_model <- glm(data = Q07_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q07_model)
```

```{r Q08 model}
print(Q10TextClean$Question[08])
Q08_select <- Q10_demo_long %>%
  filter(Question == "Q08") %>%
  na.omit() 
Q08_model <- glm(data = Q08_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q08_model)
```

```{r Q09 model}
print(Q10TextClean$Question[09])
Q09_select <- Q10_demo_long %>%
  filter(Question == "Q09") %>%
  na.omit() 
Q09_model <- glm(data = Q09_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q09_model)
```

```{r Q10 model}
print(Q10TextClean$Question[10])
Q10_select <- Q10_demo_long %>%
  filter(Question == "Q10") %>%
  na.omit() 
Q10_model <- glm(data = Q10_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q10_model)
```

```{r Q11 model}
print(Q10TextClean$Question[11])
Q11_select <- Q10_demo_long %>%
  filter(Question == "Q11") %>%
  na.omit() 
Q11_model <- glm(data = Q11_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q11_model)
```

```{r Q12 model}
print(Q10TextClean$Question[12])
Q12_select <- Q10_demo_long %>%
  filter(Question == "Q12") %>%
  na.omit() 
Q12_model <- glm(data = Q12_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q12_model)
```

```{r Q13 model}
print(Q10TextClean$Question[13])
Q13_select <- Q10_demo_long %>%
  filter(Question == "Q13") %>%
  na.omit() 
Q13_model <- glm(data = Q13_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q13_model)
```

```{r Q14 model}
print(Q10TextClean$Question[14])
Q14_select <- Q10_demo_long %>%
  filter(Question == "Q14") %>%
  na.omit() 
Q14_model <- glm(data = Q14_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q14_model)
```

```{r Q15 model}
print(Q10TextClean$Question[15])
Q15_select <- Q10_demo_long %>%
  filter(Question == "Q15") %>%
  na.omit() 
Q15_model <- glm(data = Q15_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q15_model)
```

```{r Q16 model}
print(Q10TextClean$Question[16])
Q16_select <- Q10_demo_long %>%
  filter(Question == "Q16") %>%
  na.omit() 
Q16_model <- glm(data = Q16_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q16_model)
```

```{r Q17 model}
print(Q10TextClean$Question[17])
Q17_select <- Q10_demo_long %>%
  filter(Question == "Q17") %>%
  na.omit() 
Q17_model <- glm(data = Q17_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q17_model)
```

```{r Q18 model}
print(Q10TextClean$Question[18])
Q18_select <- Q10_demo_long %>%
  filter(Question == "Q18") %>%
  na.omit() 
Q18_model <- glm(data = Q18_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q18_model)
```

```{r Q19 model}
print(Q10TextClean$Question[19])
Q19_select <- Q10_demo_long %>%
  filter(Question == "Q19") %>%
  na.omit() 
Q19_model <- glm(data = Q19_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q19_model)
```

```{r Q20 model}
print(Q10TextClean$Question[20])
Q20_select <- Q10_demo_long %>%
  filter(Question == "Q20") %>%
  na.omit() 
Q20_model <- glm(data = Q20_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q20_model)
```

```{r Q21 model}
print(Q10TextClean$Question[21])
Q21_select <- Q10_demo_long %>%
  filter(Question == "Q21") %>%
  na.omit() 
Q21_model <- glm(data = Q21_select, 
                 5-as.numeric(Response) ~ Semester + Gender * Race) %>%
  stepAIC(direction = "backward")
summary(Q21_model)
```

## Summary

Most of the responses showed a dependence on the semester, although the significance was sometimes marginal. 
This needs to be interpretted carefully as the responses in the Spring semester, if different, were always less positive than in the Fall. 
That is, the students in the Spring percieved less of a gain in these measures due to the CURE Lab than those in the Fall semester. 
This is consistent with the hypothesis that BIO Seminar provided some gain in these measures and, therefore, the gains due to the CURE Lab were smaller. 

Questions that showed dependence on the Semester, but not Race or Gender:

2  3  8  9 10 11 12 13 14 16 17 19 20

Question that showed dependence on Semester and Race, but not Gender: 

1

Question that showed dependence on Semester and Gender, but not Race: 

18

Question that showed dependence on Race, but not Semester or Gender:

21

Question that showed dependence on the Semester, Race, Gender, and the interaction between Race and Gender:

4

Questions that did not depend on Semester, Race, or Gender:

5  6  7 15

Here is the list of questions for reference:

Preface: In this section of the survey you will be asked to consider a variety of possible benefits you may have gained from your research experience. If for any reason you prefer not to answer, or consider the question irrelevant to you, please choose the "Not applicable / Prefer not to answer" option 

 [1] "Clarification of a career path"                                      
 [2] "Skill in the interpretation of results"                              
 [3] "Tolerance for obstacles faced in the research process"               
 [4] "Readiness for more demanding research"                               
 [5] "Understanding how knowledge is constructed"                          
 [6] "Understanding of the research process in your field"                 
 [7] "Ability to integrate theory and practice"                            
 [8] "Understanding of how scientists work on real problems"               
 [9] "Understanding that scientific assertions require supporting evidence"
[10] "Ability to analyze data and other information"                       
[11] "Understanding science"                                               
[12] "Learning ethical conduct in your field"                              
[13] "Learning laboratory techniques"                                      
[14] "Ability to read and understand primary literature"                   
[15] "Skill in how to give an effective oral presentation"                 
[16] "Skill in science writing"                                            
[17] "Self-confidence"                                                     
[18] "Understanding of how scientists think"                               
[19] "Learning to work independently"                                      
[20] "Becoming part of a learning community"                               
[21] "Confidence in my potential to be a teacher of science"

## Final Figures

Added Q04 back to this figure.

### Final Figure 6

```{r Q10 By Semester, fig.height=10}
Q10_demo_semester <- Q10_demo_long %>%
  filter(Question %in% c('Q02','Q03','Q04', 'Q08','Q09','Q10','Q11','Q12','Q13','Q14',
                         'Q16','Q17','Q19','Q20'))
ggplot(Q10_demo_semester) +
  geom_bar(aes(x = Semester, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_semester$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Semester') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

### Final Figure 7A

```{r Q10 By Semester and race, fig.height=2}
Q10_demo_semester_race <- Q10_demo_long %>%
  filter(Question == 'Q01')
ggplot(Q10_demo_semester_race) +
  geom_bar(aes(x = Semester, fill = Response), position = 'fill', width = 0.75) +
  facet_wrap(~ as.factor(Q10_demo_semester_race$Question) + Q10_demo_semester_race$Race) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Semester') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

### Final Figure 7C

```{r Q10 By None, fig.height=2}
Q10_demo_none <- Q10_demo_long %>%
  filter(Question %in% c('Q05','Q06','Q07','Q15', 'Q21'))
ggplot(Q10_demo_none) +
  geom_bar(aes(x = Question, fill = Response), position = 'fill', width = 0.75) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Question') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

### Final Figure 7B

```{r Q10.18 By Semester and gender, fig.height=2}
Q10_demo_semester_gender <- Q10_demo_long %>%
  filter(Question == 'Q18')
ggplot(Q10_demo_semester_gender) +
  geom_bar(aes(x = Semester, fill = Response), position = 'fill', width = 0.75) +
  facet_wrap(~ as.factor(Q10_demo_semester_gender$Question) + Q10_demo_semester_gender$Gender) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Semester') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```


```{r Q10 By All, fig.height=3}
Q10_demo_all <- Q10_demo_long %>%
  filter(Question == 'Q04')
ggplot(Q10_demo_all) +
  geom_bar(aes(x = Semester, fill = Response), position = 'fill', width = 0.75) +
  facet_wrap(~ Q10_demo_all$Race + Q10_demo_all$Gender) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Semester') +
  fill_palette(c("#2171b5","#6baed6","#bdd7e7","#eff3ff","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

Now that I look at this figure, we should not include it because of the ability to identify students. 
Instead I will add this question to the semester-only question (Figure 6) because even though the interaction was included in the model, it had a high p value (>0.1) and none of the other variables were significant either. 
