---
title: "Improvements by Instructor"
author: "Ken Field"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("MASS")) install.packages("MASS"); library(MASS) #stepAIC() function
if (!require("car")) install.packages("car"); library(car) #Anova function
if (!require('interactions')) install.packages('interactions'); library(interactions) #Interaction plots
if (!require('sandwich')) install.packages('sandwich'); library(sandwich) #robust errors
if (!require('pheatmap')) install.packages('pheatmap'); library(pheatmap) #heatmap
if (!require('knitr')) install.packages('knitr'); library(knitr) #kable
if (!require("performance")) install.packages("performance"); library(performance)
if (!require('nlme')) install.packages('nlme'); library(nlme) #to all ML estimates in glm
if (!require('lme4')) install.packages('lme4'); library(lme4) #mixed effects models
if (!require("conflicted")) install.packages("conflicted"); library(conflicted)
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
conflict_prefer_all("dplyr", quiet = TRUE)
```

## Loading Results

Loading in the results without instructor information:

```{r Load data}
NoDemographicsYear1 <- read_delim("Deidentified Surveys/Year1.NoDemographics.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE) %>%
  rename(Semester = Semester_pre)
NoDemographicsYear2 <- read_delim("Deidentified Surveys/Year2.NoDemographics.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
NoDemographicsYear3 <- read_delim("Deidentified Surveys/Year3.NoDemographics.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
NoDemographics <- bind_rows(NoDemographicsYear1, NoDemographicsYear2, NoDemographicsYear3)

NoDemographicsQuestions <- read_delim("Deidentified Surveys/Year3.NoDemographicsQuestions.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
```

Cleaning up the factors and removing anyone who did not agree to the informed consent.

```{r Cleaning}
NoDemographics <- NoDemographics %>%
  mutate(Semester = factor(Semester, levels = c("Fall 2021", "Spring 2022",
                                                "Fall 2022", "Spring 2023",
                                                "Fall 2023", "Spring 2024"))) %>%
  mutate(across(Instructor, str_replace, 'Prof. ', ''))
NoDemographics <- NoDemographics %>%
  filter(Q1_pre == "Agree")
```

We have hypothesized that instructors may be less successful in improving learning elements during the first time
that they have taught the class. To test this hypothesis, we will need to code a new variable, that I will call Rookie.
To do this, I logged into Cognos and ran a "Class Info by Term and Instructor" report. Note that I had to identify the 
instructor pseudonyms using the Deidentification Rmd, but I have not included that information here.

- 'McGonagall' 'Fall 2021'
- 'Dumbledore' 'Fall 2021'
- 'Hagrid' 'Spring 2022'
- 'Lupin' 'Fall 2021'
- 'Sinistra' 'Spring 2022'

```{r}
NoDemographics <- NoDemographics %>%
  mutate(Rookie = case_when((Instructor == 'McGonagall') & (Semester == 'Fall 2021') ~ "Rookie", 
                     (Instructor == 'Dumbledore') & (Semester == 'Fall 2021') ~ "Rookie",
                     (Instructor == 'Hagrid') & (Semester == 'Spring 2022') ~ "Rookie",
                     (Instructor == 'Lupin') & (Semester == 'Fall 2021') ~ "Rookie",
                     (Instructor == 'Sinistra') & (Semester == 'Spring 2022') ~ "Rookie",
                     .default = "Veteran"))
  
```

## Improvement in learning elements

Comparing the responses to Pre10 and Post9:

```{r Pre Q10, echo=FALSE}
PreQ10 <- NoDemographics %>%
  select(Semester, Instructor, Rookie, starts_with("Q10")) %>%
  select(Semester, Instructor, Rookie, ends_with("_pre"))
Q10Text <- NoDemographicsQuestions %>%
  filter(startsWith(value, "Q10")) %>%
  filter(endsWith(value, "_pre"))
Q10Text$Question[1]
Q10TextClean <- Q10Text %>%
  mutate(Question = str_remove(Q10Text$Question, "Please look over this inventory of elements that might be included in a course. For each element, give an estimate of your current level of ability before the course begins. Your current level of ability may be a result of courses in high school or college, or it may be a result of other experiences such as jobs or special programs. If students are expected to do the following course elements, what would be their level of expertise\\? - "))
Q10TextClean$Question
```


```{r Post Q9, echo=FALSE}
PostQ9 <- NoDemographics %>%
  select(starts_with("Q9")) %>%
  select(ends_with("_post"))

Q9Text <- NoDemographicsQuestions %>%
  filter(startsWith(value, "Q9")) %>%
  filter(endsWith(value, "_post"))
Q9Text$Question[1]
Q9TextClean <- Q9Text %>%
  mutate(Question = str_remove(Q9Text$Question, "Please rate how much learning you gained from each element you experienced in this course. The scale measuring your gain is from \\(no or very small gain\\) to \\(very large gain\\). Some elements may not have happened at all. If the item is not relevant or you prefer not to answer, please choose the \"\"not applicable\"\" option. If students were expected to do the following course elements, what would be their level of gained experience\\? - "))
Q9TextClean$Question

Q9TextClean$Question == Q10TextClean$Question
```

Now to compare the pre and post responses for those questions:

```{r, echo=FALSE}
MergedQ10 <- bind_cols(PreQ10, PostQ9)
head(MergedQ10)
Q10Factors <- MergedQ10 %>%
  select(starts_with("Q")) %>%
  mutate_all(funs(ordered(.,(levels = c("None", "Little", 
                                       "Some", "Much", "Extensive"))))) 
Q10Clean <- MergedQ10 %>%
  select(-starts_with("Q")) %>%
  cbind(Q10Factors)
```

### Classroom

To run a mixed effects model we need to use a random effect variable with at least 5 to 8 distinct levels.
We could use Instructor as the random effect, but that would barely meet this criteria and also would ignore the within-class clustering.
Therefore, we will generate a dummy-variable of classroom, that will be unique for each instructor:semester combination. 

```{r}
Q10Clean <- Q10Clean |>
  mutate(Classroom = interaction(Instructor, Semester))
```



## Sample Size

### Table S1

```{r Sample Size Table}
Q10Clean %>%
  group_by(Instructor, Semester, Rookie) %>%
  count() %>%
  print()
```

First let's just look at the contingency tables to see if everything looks right.

```{r, echo=FALSE}
print("Rows represents pre-survey response, Columns represent post-survey response.")
print("First for All sections then by Instructor.")
Q10TextClean$Question[1]
table(Q10Clean$Q10_1_pre, Q10Clean$Q9_1_post)
print("By Instructor")
Q10TextClean$Question[1]
table(Q10Clean$Q10_1_pre, Q10Clean$Q9_1_post, Q10Clean$Instructor)
```

Balloon Plot

On these plots, the answers on the x axis are the pre-survey results and on the y-axis
are the post survey results. 
Responses above the "none" level indicate students who felt that they increased in this element.


The pre-survey questions were asked as:
Please look over this inventory of elements that might be included in a course. For each element, give an estimate of your current level of ability before the course begins. Your current level of ability may be a result of courses in high school or college, or it may be a result of other experiences such as jobs or special programs. If students are expected to do the following course elements, what would be their level of expertise? 


The post-survey questions were asked: 
Please rate how much learning you gained from each element you experienced in this course. The scale measuring your gain is from (no or very small gain) to (very large gain). Some elements may not have happened at all. If the item is not relevant or you prefer not to answer, please choose the "not applicable" option. If students were expected to do the following course elements, what would be their level of gained experience? 

```{r Balloon Plot Setup, echo=FALSE}
summary(as.factor(Q10Clean$Instructor))
numInstructors <- 5
colorcolumn <- rep.int(c(rep.int("None",5), rep.int("Little",5), rep.int("Some",5), 
                 rep.int("Much",5), rep.int("Extensive", 5)), numInstructors)

colorcolumn <- factor(colorcolumn, 
                         levels = c("Extensive", "Much", "Some", "Little", "None"))
```


After feedback from the reviewers we have adopted a simpler approach to the analysis. 
We are dropping the interaction term between Rookie and Instructor as that was heavily confounded by semester.
We considered using a mixed effects model with semester taught as a random effect. 
This did not significantly change the outcome of the analysis and did not match our a priori analysis plan, so it was not included.
We are going to report F-test results for all variables (no model selection) and then use an alpha cutoff of 0.05 to determine which visualizations to show.
Further reading also suggested to use an F-test for testing Gaussian GLMs, rather than an LRT or Chi-squared test

## Q10 Figures  {.tabset .tabset-pills}

### Q10_1

```{r Q10_1, echo=FALSE}
Q10Clean %>%
  select(Q10_1_pre, Q9_1_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_1_pre", y = "Q9_1_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[1], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
levels(as.factor(Q10Clean$Instructor))

# NA's are going to cause problems with the model selection, so I will prepare to remove them 
Q10Clean_withNA <- Q10Clean

Q10Clean_withNA %>%
  select(Q10_1_pre, Q9_1_post, Instructor, Rookie, Semester, Classroom) %>%
  na.omit() %>%
  mutate(Q9_1_post = as.numeric(Q9_1_post)) %>%
  mutate(Q10_1_pre = as.numeric(Q10_1_pre)) -> Q_1Clean

imp_model_Q10_1 <- glm(Q9_1_post ~ Q10_1_pre + Instructor + Rookie, data = Q_1Clean)
summary(imp_model_Q10_1)

Anova(imp_model_Q10_1, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_1 <- lmer(Q9_1_post ~ Q10_1_pre + Instructor + (1 | Classroom), data = Q_1Clean)
summary(lmer_model_Q10_1)
Anova(lmer_model_Q10_1, type = "3", test.statistic = "F")

# Fit both models with ML
imp_model_Q10_1_ml <- gls(Q9_1_post ~ Q10_1_pre + Instructor, data = Q_1Clean, 
                          method = "ML")
lme_model_Q10_1_ml <- lme(fixed = Q9_1_post ~ Q10_1_pre + Instructor, 
                          random = ~ 1 | Semester, 
                          data = Q_1Clean, method = "ML")
compare_performance(imp_model_Q10_1_ml, lme_model_Q10_1_ml)
anova(imp_model_Q10_1_ml, lme_model_Q10_1_ml)

# Verified that the p values are being calculated properly
type3 = list(Instructor = contr.sum, Rookie = contr.sum)
imp_model_Q10_1b <- glm(Q9_1_post ~ Q10_1_pre + Instructor, contrasts = type3, data = Q_1Clean)
summary(imp_model_Q10_1b)
Anova(imp_model_Q10_1b, type = "3", test.statistic = "F")
```

Nothing met the alpha cutoff of 0.05

### Q10_2

```{r Q10_2, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_2_pre, Q9_2_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_2_pre", y = "Q9_2_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[2], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))


# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_2_pre, Q9_2_post, Instructor, Rookie, Classroom) %>%
  na.omit() %>%
  as.data.frame() -> Q_2Clean

imp_model_Q10_2 <- glm(as.numeric(Q9_2_post) ~ as.numeric(Q10_2_pre) + Instructor + Rookie, data = Q_2Clean)
summary(imp_model_Q10_2)

car::Anova(imp_model_Q10_2, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_2 <- lmerTest::lmer(as.numeric(Q9_2_post) ~ as.numeric(Q10_2_pre) + Instructor + (1 | Classroom),
                                   data = Q_2Clean)
summary(lmer_model_Q10_2)
car::Anova(lmer_model_Q10_2, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_2, lmer_model_Q10_2)

# Fit both models with ML
imp_model_Q10_2_ml <- gls(as.numeric(Q9_2_post) ~ as.numeric(Q10_2_pre) + Instructor, data = Q_2Clean, 
                          method = "ML")
lme_model_Q10_2_ml <- lme(fixed = as.numeric(Q9_2_post) ~ as.numeric(Q10_2_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_2Clean, method = "ML")
compare_performance(imp_model_Q10_2_ml, lme_model_Q10_2_ml)
anova(imp_model_Q10_2_ml, lme_model_Q10_2_ml)
```

Nothing met the cutoff

### Q10_3

```{r Q10_3, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_3_pre, Q9_3_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_3_pre", y = "Q9_3_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[3], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_3_pre, Q9_3_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_3Clean
# This was the first question with NA responses, so they had to be removed.

imp_model_Q10_3 <- glm(as.numeric(Q9_3_post) ~ 
                      as.numeric(Q10_3_pre) + Instructor + Rookie, data = Q_3Clean)
summary(imp_model_Q10_3)
car::Anova(imp_model_Q10_3, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_3 <- lmerTest::lmer(as.numeric(Q9_3_post) ~ as.numeric(Q10_3_pre) + Instructor + (1 | Classroom),
                                   data = Q_3Clean)
summary(lmer_model_Q10_3)
car::Anova(lmer_model_Q10_3, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_3, lmer_model_Q10_3)

# Fit both models with ML
imp_model_Q10_3_ml <- gls(as.numeric(Q9_3_post) ~ as.numeric(Q10_3_pre) + Instructor, data = Q_3Clean, 
                          method = "ML")
lme_model_Q10_3_ml <- lme(fixed = as.numeric(Q9_3_post) ~ as.numeric(Q10_3_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_3Clean, method = "ML")
compare_performance(imp_model_Q10_3_ml, lme_model_Q10_3_ml)
anova(imp_model_Q10_3_ml, lme_model_Q10_3_ml)
```

Nothing meets alpha cutoff.

### Q10_4

```{r Q10_4, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_4_pre, Q9_4_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_4_pre", y = "Q9_4_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[4], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_4_pre, Q9_4_post, Instructor, Rookie, Classroom) %>%
  na.omit() %>%
  mutate(Q9_4_post = as.numeric(Q9_4_post)) %>%
  mutate(Q10_4_pre = as.numeric(Q10_4_pre)) -> Q_4Clean

imp_model_Q10_4 <- glm(Q9_4_post ~ Q10_4_pre + Instructor + Rookie, data = Q_4Clean)
summary(imp_model_Q10_4)

car::Anova(imp_model_Q10_4, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_4 <- lmerTest::lmer(as.numeric(Q9_4_post) ~ as.numeric(Q10_4_pre) + Instructor + (1 | Classroom),
                                   data = Q_4Clean)
summary(lmer_model_Q10_4)
car::Anova(lmer_model_Q10_4, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_4, lmer_model_Q10_4)

# Fit both models with ML
imp_model_Q10_4_ml <- gls(as.numeric(Q9_4_post) ~ as.numeric(Q10_4_pre) + Instructor, data = Q_4Clean, 
                          method = "ML")
lme_model_Q10_4_ml <- lme(fixed = as.numeric(Q9_4_post) ~ as.numeric(Q10_4_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_4Clean, method = "ML")
compare_performance(imp_model_Q10_4_ml, lme_model_Q10_4_ml)
anova(imp_model_Q10_4_ml, lme_model_Q10_4_ml)
```

*Instructor* meets alpha cutoff.

### Final Figure 3A Q10_5

```{r Fig 3 Q10_5, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_5_pre, Q9_5_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_5_pre", y = "Q9_5_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[5], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_5_pre, Q9_5_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_5Clean

imp_model_Q10_5 <- glm(as.numeric(Q9_5_post) ~ 
                      as.numeric(Q10_5_pre) + Instructor + Rookie, data = Q_5Clean)
summary(imp_model_Q10_5)

car::Anova(imp_model_Q10_5, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_5 <- lmerTest::lmer(as.numeric(Q9_5_post) ~ as.numeric(Q10_5_pre) + Instructor + (1 | Classroom),
                                   data = Q_5Clean)
summary(lmer_model_Q10_5)
car::Anova(lmer_model_Q10_5, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_5, lmer_model_Q10_5)

# Fit both models with ML
imp_model_Q10_5_ml <- gls(as.numeric(Q9_5_post) ~ as.numeric(Q10_5_pre) + Instructor, data = Q_5Clean, 
                          method = "ML")
lme_model_Q10_5_ml <- lme(fixed = as.numeric(Q9_5_post) ~ as.numeric(Q10_5_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_5Clean, method = "ML")
compare_performance(imp_model_Q10_5_ml, lme_model_Q10_5_ml)
anova(imp_model_Q10_5_ml, lme_model_Q10_5_ml)
```

*Instructor* meets alpha cutoff.

### Q10_6

```{r Q10_6, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_6_pre, Q9_6_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_6_pre", y = "Q9_6_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[6], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_6_pre, Q9_6_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_6Clean

imp_model_Q10_6 <- glm(as.numeric(Q9_6_post) ~ 
                      as.numeric(Q10_6_pre) + Instructor + Rookie, data = Q_6Clean)
summary(imp_model_Q10_6)
car::Anova(imp_model_Q10_6, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_6 <- lmerTest::lmer(as.numeric(Q9_6_post) ~ as.numeric(Q10_6_pre) + Instructor + (1 | Classroom),
                                   data = Q_6Clean)
summary(lmer_model_Q10_6)
car::Anova(lmer_model_Q10_6, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_6, lmer_model_Q10_6)

# Fit both models with ML
imp_model_Q10_6_ml <- gls(as.numeric(Q9_6_post) ~ as.numeric(Q10_6_pre) + Instructor, data = Q_6Clean, 
                          method = "ML")
lme_model_Q10_6_ml <- lme(fixed = as.numeric(Q9_6_post) ~ as.numeric(Q10_6_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_6Clean, method = "ML")
compare_performance(imp_model_Q10_6_ml, lme_model_Q10_6_ml)
anova(imp_model_Q10_6_ml, lme_model_Q10_6_ml)
```

*Instructor* meets alpha cutoff.

### Q10_7

```{r Q10_7, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_7_pre, Q9_7_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_7_pre", y = "Q9_7_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[7], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_7_pre, Q9_7_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_7Clean

imp_model_Q10_7 <- glm(as.numeric(Q9_7_post) ~ 
                      as.numeric(Q10_7_pre) + Instructor + Rookie, data = Q_7Clean)
summary(imp_model_Q10_7)
car::Anova(imp_model_Q10_7, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_7 <- lmerTest::lmer(as.numeric(Q9_7_post) ~ as.numeric(Q10_7_pre) + Instructor + (1 | Classroom),
                                   data = Q_7Clean)
summary(lmer_model_Q10_7)
car::Anova(lmer_model_Q10_7, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_7, lmer_model_Q10_7)

# Fit both models with ML
imp_model_Q10_7_ml <- gls(as.numeric(Q9_7_post) ~ as.numeric(Q10_7_pre) + Instructor, data = Q_7Clean, 
                          method = "ML")
lme_model_Q10_7_ml <- lme(fixed = as.numeric(Q9_7_post) ~ as.numeric(Q10_7_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_7Clean, method = "ML")
compare_performance(imp_model_Q10_7_ml, lme_model_Q10_7_ml)
anova(imp_model_Q10_7_ml, lme_model_Q10_7_ml)
```

Nothing meets cutoff.

### Q10_8

```{r Q10_8, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_8_pre, Q9_8_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_8_pre", y = "Q9_8_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[8], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_8_pre, Q9_8_post, Instructor, Rookie, Classroom) %>%
  na.omit() %>%
  mutate(Q9_8_post = as.numeric(Q9_8_post)) %>%
  mutate(Q10_8_pre = as.numeric(Q10_8_pre)) -> Q_8Clean

imp_model_Q10_8 <- glm(Q9_8_post ~ Q10_8_pre + Instructor + Rookie, data = Q_8Clean)
summary(imp_model_Q10_8)
car::Anova(imp_model_Q10_8, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_8 <- lmerTest::lmer(as.numeric(Q9_8_post) ~ as.numeric(Q10_8_pre) + Instructor + (1 | Classroom),
                                   data = Q_8Clean)
summary(lmer_model_Q10_8)
car::Anova(lmer_model_Q10_8, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_8, lmer_model_Q10_8)

# Fit both models with ML
imp_model_Q10_8_ml <- gls(as.numeric(Q9_8_post) ~ as.numeric(Q10_8_pre) + Instructor, data = Q_8Clean, 
                          method = "ML")
lme_model_Q10_8_ml <- lme(fixed = as.numeric(Q9_8_post) ~ as.numeric(Q10_8_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_8Clean, method = "ML")
compare_performance(imp_model_Q10_8_ml, lme_model_Q10_8_ml)
anova(imp_model_Q10_8_ml, lme_model_Q10_8_ml)
```

Nothing meets alpha cutoff.

### Q10_9

```{r Fig 3 Q10_9, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_9_pre, Q9_9_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_9_pre", y = "Q9_9_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[9], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_9_pre, Q9_9_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_9Clean

imp_model_Q10_9 <- glm(as.numeric(Q9_9_post) ~ 
                      as.numeric(Q10_9_pre) + Instructor + Rookie, data = Q_9Clean)
summary(imp_model_Q10_9)
car::Anova(imp_model_Q10_9, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_9 <- lmerTest::lmer(as.numeric(Q9_9_post) ~ as.numeric(Q10_9_pre) + Instructor + (1 | Classroom),
                                   data = Q_9Clean)
summary(lmer_model_Q10_9)
car::Anova(lmer_model_Q10_9, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_9, lmer_model_Q10_9)

# Fit both models with ML
imp_model_Q10_9_ml <- gls(as.numeric(Q9_9_post) ~ as.numeric(Q10_9_pre) + Instructor, data = Q_9Clean, 
                          method = "ML")
lme_model_Q10_9_ml <- lme(fixed = as.numeric(Q9_9_post) ~ as.numeric(Q10_9_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_9Clean, method = "ML")
compare_performance(imp_model_Q10_9_ml, lme_model_Q10_9_ml)
anova(imp_model_Q10_9_ml, lme_model_Q10_9_ml)
```

Nothing meets cutoff.

### Q10_10

```{r Q10_10, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_10_pre, Q9_10_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_10_pre", y = "Q9_10_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[10], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_10_pre, Q9_10_post, Instructor, Rookie, Classroom) %>%
  na.omit() %>%
  mutate(Q9_10_post = as.numeric(Q9_10_post)) %>%
  mutate(Q10_10_pre = as.numeric(Q10_10_pre)) -> Q_10Clean

imp_model_Q10_10 <- glm(Q9_10_post ~ Q10_10_pre + Instructor + Rookie, data = Q_10Clean)
summary(imp_model_Q10_10)
car::Anova(imp_model_Q10_10, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_10 <- lmerTest::lmer(as.numeric(Q9_10_post) ~ as.numeric(Q10_10_pre) + Instructor + (1 | Classroom),
                                   data = Q_10Clean)
summary(lmer_model_Q10_10)
car::Anova(lmer_model_Q10_10, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_10, lmer_model_Q10_10)

# Fit both models with ML
imp_model_Q10_10_ml <- gls(as.numeric(Q9_10_post) ~ as.numeric(Q10_10_pre) + Instructor, data = Q_10Clean, 
                          method = "ML")
lme_model_Q10_10_ml <- lme(fixed = as.numeric(Q9_10_post) ~ as.numeric(Q10_10_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_10Clean, method = "ML")
compare_performance(imp_model_Q10_10_ml, lme_model_Q10_10_ml)
anova(imp_model_Q10_10_ml, lme_model_Q10_10_ml)
```

*Instructor* meets cutoff.

### Q10_11

```{r Fig 3 Q10_11, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_11_pre, Q9_11_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_11_pre", y = "Q9_11_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[11], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_11_pre, Q9_11_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_11Clean

imp_model_Q10_11 <- glm(as.numeric(Q9_11_post) ~ 
                      as.numeric(Q10_11_pre) + Instructor + Rookie, data = Q_11Clean)
summary(imp_model_Q10_11)

imp_model_Q10_11 <- glm(as.numeric(Q9_11_post) ~ 
                          as.numeric(Q10_11_pre) + Instructor + Rookie, data = Q_11Clean)
summary(imp_model_Q10_11)
car::Anova(imp_model_Q10_11, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_11 <- lmerTest::lmer(as.numeric(Q9_11_post) ~ as.numeric(Q10_11_pre) + Instructor + (1 | Classroom),
                                   data = Q_11Clean)
summary(lmer_model_Q10_11)
car::Anova(lmer_model_Q10_11, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_11, lmer_model_Q10_11)

# Fit both models with ML
imp_model_Q10_11_ml <- gls(as.numeric(Q9_11_post) ~ as.numeric(Q10_11_pre) + Instructor, data = Q_11Clean, 
                          method = "ML")
lme_model_Q10_11_ml <- lme(fixed = as.numeric(Q9_11_post) ~ as.numeric(Q10_11_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_11Clean, method = "ML")
compare_performance(imp_model_Q10_11_ml, lme_model_Q10_11_ml)
anova(imp_model_Q10_11_ml, lme_model_Q10_11_ml)
```

*Pre-survey* and *Instructor* meet cutoff.

### Q10_12

```{r Fig 3 Q10_12, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_12_pre, Q9_12_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_12_pre", y = "Q9_12_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[12], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_12_pre, Q9_12_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_12Clean

imp_model_Q10_12 <- glm(as.numeric(Q9_12_post) ~ 
                      as.numeric(Q10_12_pre) + Instructor + Rookie, data = Q_12Clean)
summary(imp_model_Q10_12)
drop1(imp_model_Q10_12, test = "LRT")
car::Anova(imp_model_Q10_12, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_12 <- lmerTest::lmer(as.numeric(Q9_12_post) ~ as.numeric(Q10_12_pre) + Instructor + (1 | Classroom),
                                   data = Q_12Clean)
summary(lmer_model_Q10_12)
car::Anova(lmer_model_Q10_12, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_12, lmer_model_Q10_12)

# Fit both models with ML
imp_model_Q10_12_ml <- gls(as.numeric(Q9_12_post) ~ as.numeric(Q10_12_pre) + Instructor, data = Q_12Clean, 
                          method = "ML")
lme_model_Q10_12_ml <- lme(fixed = as.numeric(Q9_12_post) ~ as.numeric(Q10_12_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_12Clean, method = "ML")
compare_performance(imp_model_Q10_12_ml, lme_model_Q10_12_ml)
anova(imp_model_Q10_12_ml, lme_model_Q10_12_ml)
```

Nothing meets cutoff.

### Q10_13

```{r Q10_13, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_13_pre, Q9_13_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_13_pre", y = "Q9_13_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[13], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_13_pre, Q9_13_post, Instructor, Rookie, Classroom) %>%
  na.omit() %>%
  mutate(Q9_13_post = as.numeric(Q9_13_post)) %>%
  mutate(Q10_13_pre = as.numeric(Q10_13_pre)) -> Q_13Clean

imp_model_Q10_13 <- glm(as.numeric(Q9_13_post) ~ 
                      as.numeric(Q10_13_pre) + Instructor + Rookie, data = Q_13Clean)
summary(imp_model_Q10_13)
car::Anova(imp_model_Q10_13, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_13 <- lmerTest::lmer(as.numeric(Q9_13_post) ~ as.numeric(Q10_13_pre) + Instructor + (1 | Classroom),
                                   data = Q_13Clean)
summary(lmer_model_Q10_13)
car::Anova(lmer_model_Q10_13, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_13, lmer_model_Q10_13)

# Fit both models with ML
imp_model_Q10_13_ml <- gls(as.numeric(Q9_13_post) ~ as.numeric(Q10_13_pre) + Instructor, data = Q_13Clean, 
                          method = "ML")
lme_model_Q10_13_ml <- lme(fixed = as.numeric(Q9_13_post) ~ as.numeric(Q10_13_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_13Clean, method = "ML")
compare_performance(imp_model_Q10_13_ml, lme_model_Q10_13_ml)
anova(imp_model_Q10_13_ml, lme_model_Q10_13_ml)
```

*Presurvey* and *Instructor* meet cutoff

### Q10_14

```{r Fig 3 Q10_14, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_14_pre, Q9_14_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_14_pre", y = "Q9_14_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[14], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_14_pre, Q9_14_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_14Clean

imp_model_Q10_14 <- glm(as.numeric(Q9_14_post) ~ 
                      as.numeric(Q10_14_pre) + Instructor + Rookie, data = Q_14Clean)
summary(imp_model_Q10_14)
car::Anova(imp_model_Q10_14, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_14 <- lmerTest::lmer(as.numeric(Q9_14_post) ~ as.numeric(Q10_14_pre) + Instructor + (1 | Classroom),
                                   data = Q_14Clean)
summary(lmer_model_Q10_14)
car::Anova(lmer_model_Q10_14, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_14, lmer_model_Q10_14)

# Fit both models with ML
imp_model_Q10_14_ml <- gls(as.numeric(Q9_14_post) ~ as.numeric(Q10_14_pre) + Instructor, data = Q_14Clean, 
                          method = "ML")
lme_model_Q10_14_ml <- lme(fixed = as.numeric(Q9_14_post) ~ as.numeric(Q10_14_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_14Clean, method = "ML")
compare_performance(imp_model_Q10_14_ml, lme_model_Q10_14_ml)
anova(imp_model_Q10_14_ml, lme_model_Q10_14_ml)
```

*Presurvey* and *Instructor* meet cutoff

### Q10_15

```{r Fig 3 Q10_15, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_15_pre, Q9_15_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_15_pre", y = "Q9_15_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[15], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_15_pre, Q9_15_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_15Clean

imp_model_Q10_15 <- glm(as.numeric(Q9_15_post) ~ 
                      as.numeric(Q10_15_pre) + Instructor + Rookie, data = Q_15Clean)
summary(imp_model_Q10_15)
car::Anova(imp_model_Q10_15, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_15 <- lmerTest::lmer(as.numeric(Q9_15_post) ~ as.numeric(Q10_15_pre) + Instructor + (1 | Classroom),
                                   data = Q_15Clean)
summary(lmer_model_Q10_15)
car::Anova(lmer_model_Q10_15, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_15, lmer_model_Q10_15)

# Fit both models with ML
imp_model_Q10_15_ml <- gls(as.numeric(Q9_15_post) ~ as.numeric(Q10_15_pre) + Instructor, data = Q_15Clean, 
                          method = "ML")
lme_model_Q10_15_ml <- lme(fixed = as.numeric(Q9_15_post) ~ as.numeric(Q10_15_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_15Clean, method = "ML")
compare_performance(imp_model_Q10_15_ml, lme_model_Q10_15_ml)
anova(imp_model_Q10_15_ml, lme_model_Q10_15_ml)
```

*Presurvey* and *Instructor* meets cutoff

### Q10_16

```{r Fig 3 Q10_16, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_16_pre, Q9_16_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_16_pre", y = "Q9_16_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[16], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_16_pre, Q9_16_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_16Clean

imp_model_Q10_16 <- glm(as.numeric(Q9_16_post) ~ 
                      as.numeric(Q10_16_pre) + Instructor + Rookie, data = Q_16Clean)
summary(imp_model_Q10_16)
car::Anova(imp_model_Q10_16, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_16 <- lmerTest::lmer(as.numeric(Q9_16_post) ~ as.numeric(Q10_16_pre) + Instructor + (1 | Classroom),
                                   data = Q_16Clean)
summary(lmer_model_Q10_16)
car::Anova(lmer_model_Q10_16, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_16, lmer_model_Q10_16)

# Fit both models with ML
imp_model_Q10_16_ml <- gls(as.numeric(Q9_16_post) ~ as.numeric(Q10_16_pre) + Instructor, data = Q_16Clean, 
                          method = "ML")
lme_model_Q10_16_ml <- lme(fixed = as.numeric(Q9_16_post) ~ as.numeric(Q10_16_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_16Clean, method = "ML")
compare_performance(imp_model_Q10_16_ml, lme_model_Q10_16_ml)
anova(imp_model_Q10_16_ml, lme_model_Q10_16_ml)
```

*Presurvey* and *Instructor* meet cutoff

### Q10_17

```{r Q10_17, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_17_pre, Q9_17_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_17_pre", y = "Q9_17_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[17], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_17_pre, Q9_17_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_17Clean

imp_model_Q10_17 <- glm(as.numeric(Q9_17_post) ~ 
                      as.numeric(Q10_17_pre) + Instructor + Rookie, data = Q_17Clean)
summary(imp_model_Q10_17)
car::Anova(imp_model_Q10_17, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_17 <- lmerTest::lmer(as.numeric(Q9_17_post) ~ as.numeric(Q10_17_pre) + Instructor + (1 | Classroom),
                                   data = Q_17Clean)
summary(lmer_model_Q10_17)
car::Anova(lmer_model_Q10_17, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_17, lmer_model_Q10_17)

# Fit both models with ML
imp_model_Q10_17_ml <- gls(as.numeric(Q9_17_post) ~ as.numeric(Q10_17_pre) + Instructor, data = Q_17Clean, 
                          method = "ML")
lme_model_Q10_17_ml <- lme(fixed = as.numeric(Q9_17_post) ~ as.numeric(Q10_17_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_17Clean, method = "ML")
compare_performance(imp_model_Q10_17_ml, lme_model_Q10_17_ml)
anova(imp_model_Q10_17_ml, lme_model_Q10_17_ml)
```

*Instructor* meets cutoff.

### Q10_18

```{r Fig 3 Q10_18, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_18_pre, Q9_18_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_18_pre", y = "Q9_18_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[18], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_18_pre, Q9_18_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_18Clean

imp_model_Q10_18 <- glm(as.numeric(Q9_18_post) ~ 
                      as.numeric(Q10_18_pre) + Instructor + Rookie, data = Q_18Clean)
summary(imp_model_Q10_18)
car::Anova(imp_model_Q10_18, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_18 <- lmerTest::lmer(as.numeric(Q9_18_post) ~ as.numeric(Q10_18_pre) + Instructor + (1 | Classroom),
                                   data = Q_18Clean)
summary(lmer_model_Q10_18)
car::Anova(lmer_model_Q10_18, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_18, lmer_model_Q10_18)

# Fit both models with ML
imp_model_Q10_18_ml <- gls(as.numeric(Q9_18_post) ~ as.numeric(Q10_18_pre) + Instructor, data = Q_18Clean, 
                          method = "ML")
lme_model_Q10_18_ml <- lme(fixed = as.numeric(Q9_18_post) ~ as.numeric(Q10_18_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_18Clean, method = "ML")
compare_performance(imp_model_Q10_18_ml, lme_model_Q10_18_ml)
anova(imp_model_Q10_18_ml, lme_model_Q10_18_ml)
```

*Presurvey* and *Instructor* meets cutoff.

### Q10_19

```{r Q10_19, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_19_pre, Q9_19_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_19_pre", y = "Q9_19_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[19], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_19_pre, Q9_19_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_19Clean

imp_model_Q10_19 <- glm(as.numeric(Q9_19_post) ~ 
                      as.numeric(Q10_19_pre) + Instructor + Rookie, data = Q_19Clean)
summary(imp_model_Q10_19)
car::Anova(imp_model_Q10_19, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_19 <- lmerTest::lmer(as.numeric(Q9_19_post) ~ as.numeric(Q10_19_pre) + Instructor + (1 | Classroom),
                                   data = Q_19Clean)
summary(lmer_model_Q10_19)
car::Anova(lmer_model_Q10_19, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_19, lmer_model_Q10_19)

# Fit both models with ML
imp_model_Q10_19_ml <- gls(as.numeric(Q9_19_post) ~ as.numeric(Q10_19_pre) + Instructor, data = Q_19Clean, 
                          method = "ML")
lme_model_Q10_19_ml <- lme(fixed = as.numeric(Q9_19_post) ~ as.numeric(Q10_19_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_19Clean, method = "ML")
compare_performance(imp_model_Q10_19_ml, lme_model_Q10_19_ml)
anova(imp_model_Q10_19_ml, lme_model_Q10_19_ml)
```

Nothing meets cutoff.

### Q10_20

```{r Q10_20, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_20_pre, Q9_20_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_20_pre", y = "Q9_20_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[20], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_20_pre, Q9_20_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_20Clean

imp_model_Q10_20 <- glm(as.numeric(Q9_20_post) ~ 
                      as.numeric(Q10_20_pre) + Instructor + Rookie, data = Q_20Clean)
summary(imp_model_Q10_20)
car::Anova(imp_model_Q10_20, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_20 <- lmerTest::lmer(as.numeric(Q9_20_post) ~ as.numeric(Q10_20_pre) + Instructor + (1 | Classroom),
                                   data = Q_20Clean)
summary(lmer_model_Q10_20)
car::Anova(lmer_model_Q10_20, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_20, lmer_model_Q10_20)

# Fit both models with ML
imp_model_Q10_20_ml <- gls(as.numeric(Q9_20_post) ~ as.numeric(Q10_20_pre) + Instructor, data = Q_20Clean, 
                          method = "ML")
lme_model_Q10_20_ml <- lme(fixed = as.numeric(Q9_20_post) ~ as.numeric(Q10_20_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_20Clean, method = "ML")
compare_performance(imp_model_Q10_20_ml, lme_model_Q10_20_ml)
anova(imp_model_Q10_20_ml, lme_model_Q10_20_ml)
```

Nothing meets cutoff.

### Q10_21

```{r Q10_21, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_21_pre, Q9_21_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_21_pre", y = "Q9_21_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[21], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_21_pre, Q9_21_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_21Clean

imp_model_Q10_21 <- glm(as.numeric(Q9_21_post) ~ 
                      as.numeric(Q10_21_pre) + Instructor + Rookie, data = Q_21Clean)
summary(imp_model_Q10_21)
car::Anova(imp_model_Q10_21, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_21 <- lmerTest::lmer(as.numeric(Q9_21_post) ~ as.numeric(Q10_21_pre) + Instructor + (1 | Classroom),
                                   data = Q_21Clean)
summary(lmer_model_Q10_21)
car::Anova(lmer_model_Q10_21, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_21, lmer_model_Q10_21)

# Fit both models with ML
imp_model_Q10_21_ml <- gls(as.numeric(Q9_21_post) ~ as.numeric(Q10_21_pre) + Instructor, data = Q_21Clean, 
                          method = "ML")
lme_model_Q10_21_ml <- lme(fixed = as.numeric(Q9_21_post) ~ as.numeric(Q10_21_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_21Clean, method = "ML")
compare_performance(imp_model_Q10_21_ml, lme_model_Q10_21_ml)
anova(imp_model_Q10_21_ml, lme_model_Q10_21_ml)
```

Nothing meets cutoff.

### Q10_22

```{r Q10_22, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_22_pre, Q9_22_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_22_pre", y = "Q9_22_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[22], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_22_pre, Q9_22_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_22Clean

imp_model_Q10_22 <- glm(as.numeric(Q9_22_post) ~ 
                      as.numeric(Q10_22_pre) + Instructor + Rookie, data = Q_22Clean)
summary(imp_model_Q10_22)
car::Anova(imp_model_Q10_22, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_22 <- lmerTest::lmer(as.numeric(Q9_22_post) ~ as.numeric(Q10_22_pre) + Instructor + (1 | Classroom),
                                   data = Q_22Clean)
summary(lmer_model_Q10_22)
car::Anova(lmer_model_Q10_22, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_22, lmer_model_Q10_22)

# Fit both models with ML
imp_model_Q10_22_ml <- gls(as.numeric(Q9_22_post) ~ as.numeric(Q10_22_pre) + Instructor, data = Q_22Clean, 
                          method = "ML")
lme_model_Q10_22_ml <- lme(fixed = as.numeric(Q9_22_post) ~ as.numeric(Q10_22_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_22Clean, method = "ML")
compare_performance(imp_model_Q10_22_ml, lme_model_Q10_22_ml)
anova(imp_model_Q10_22_ml, lme_model_Q10_22_ml)
```

Nothing meets cutoff.

### Q10_23

```{r Q10_23, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_23_pre, Q9_23_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_23_pre", y = "Q9_23_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[23], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_23_pre, Q9_23_post, Instructor, Rookie, Classroom) %>%
  na.omit() %>% 
  mutate(Q9_23_post = as.numeric(Q9_23_post)) %>%
  mutate(Q10_23_pre = as.numeric(Q10_23_pre)) -> Q_23Clean

imp_model_Q10_23 <- glm(Q9_23_post ~ Q10_23_pre + Instructor + Rookie, data = Q_23Clean)
summary(imp_model_Q10_23)
car::Anova(imp_model_Q10_23, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_23 <- lmerTest::lmer(as.numeric(Q9_23_post) ~ as.numeric(Q10_23_pre) + Instructor + (1 | Classroom),
                                   data = Q_23Clean)
summary(lmer_model_Q10_23)
car::Anova(lmer_model_Q10_23, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_23, lmer_model_Q10_23)

# Fit both models with ML
imp_model_Q10_23_ml <- gls(as.numeric(Q9_23_post) ~ as.numeric(Q10_23_pre) + Instructor, data = Q_23Clean, 
                          method = "ML")
lme_model_Q10_23_ml <- lme(fixed = as.numeric(Q9_23_post) ~ as.numeric(Q10_23_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_23Clean, method = "ML")
compare_performance(imp_model_Q10_23_ml, lme_model_Q10_23_ml)
anova(imp_model_Q10_23_ml, lme_model_Q10_23_ml)
```

*Presurvey* and *Instructor* meet cutoff.

### Final Figure 3B Q10_24

```{r Fig 3 Q10_24, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_24_pre, Q9_24_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_24_pre", y = "Q9_24_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[24], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_24_pre, Q9_24_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_24Clean

imp_model_Q10_24 <- glm(as.numeric(Q9_24_post) ~ 
                      as.numeric(Q10_24_pre) + Instructor + Rookie, data = Q_24Clean)
summary(imp_model_Q10_24)
car::Anova(imp_model_Q10_24, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_24 <- lmerTest::lmer(as.numeric(Q9_24_post) ~ as.numeric(Q10_24_pre) + Instructor + (1 | Classroom),
                                   data = Q_24Clean)
summary(lmer_model_Q10_24)
car::Anova(lmer_model_Q10_24, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_24, lmer_model_Q10_24)

# Fit both models with ML
imp_model_Q10_24_ml <- gls(as.numeric(Q9_24_post) ~ as.numeric(Q10_24_pre) + Instructor, data = Q_24Clean, 
                          method = "ML")
lme_model_Q10_24_ml <- lme(fixed = as.numeric(Q9_24_post) ~ as.numeric(Q10_24_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_24Clean, method = "ML")
compare_performance(imp_model_Q10_24_ml, lme_model_Q10_24_ml)
anova(imp_model_Q10_24_ml, lme_model_Q10_24_ml)
```

*Presurvey* and *Instructor* meet cutoff.

### Q10_25

```{r Q10_25, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_25_pre, Q9_25_post, Instructor) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Post = colorcolumn) %>%
  ggballoonplot(x = "Q10_25_pre", y = "Q9_25_post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Instructor",
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[25], 72), collapse = "\n")) + 
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE"))

# Using glm() to determine if post response depends on pre response or on instructor and rookie status:
Q10Clean_withNA %>%
  select(Q10_25_pre, Q9_25_post, Instructor, Rookie, Classroom) %>%
  na.omit() -> Q_25Clean

imp_model_Q10_25 <- glm(as.numeric(Q9_25_post) ~ 
                      as.numeric(Q10_25_pre) + Instructor + Rookie, data = Q_25Clean)
summary(imp_model_Q10_25)
car::Anova(imp_model_Q10_25, type = "3", test.statistic = "F")

# Testing a glmm approach 

lmer_model_Q10_25 <- lmerTest::lmer(as.numeric(Q9_25_post) ~ as.numeric(Q10_25_pre) + Instructor + (1 | Classroom),
                                   data = Q_25Clean)
summary(lmer_model_Q10_25)
car::Anova(lmer_model_Q10_25, type = "3", test.statistic = "F")

compare_performance(imp_model_Q10_25, lmer_model_Q10_25)

# Fit both models with ML
imp_model_Q10_25_ml <- gls(as.numeric(Q9_25_post) ~ as.numeric(Q10_25_pre) + Instructor, data = Q_25Clean, 
                          method = "ML")
lme_model_Q10_25_ml <- lme(fixed = as.numeric(Q9_25_post) ~ as.numeric(Q10_25_pre) + Instructor, 
                          random = ~ 1 | Classroom, 
                          data = Q_25Clean, method = "ML")
compare_performance(imp_model_Q10_25_ml, lme_model_Q10_25_ml)
anova(imp_model_Q10_25_ml, lme_model_Q10_25_ml)
```

*Presurvey* and *Instructor* meet cutoff.

## Summary

For each question, a generalized mixed effects model with a Gaussian linking function determined if the student's post-survey response was dependent on (1) that student's pre-survey response and (2) which instructor they had, after controlling for the random effect of which class they were in.
An alpha value of 0.05 using Type III Wald F tests with Kenward-Roger df was used to define statistical significance.

Removing "Q10_02", "Q10_19", "Q10_20", "Q10_21", "Q10_22", "Q10_25" *See below (not emphasized by any instructors)


The following questions showed dependence on *pre-survey response* and *instructor*:

11, 13, 14, 15, 16, 18, 23, 24, -25-

- [11] "Read primary scientific literature" 
- [13] "Collect data" 
- [14] "Analyze data" 
- [15] "Present results orally"
- [16] "Present results in written papers or reports"
- [18] "Critique the work of other students"
- [23] "Discuss reading materials in class"  
-  [24] "Maintain a lab notebook"   
-  [25] "Computer modeling" *Removed 

The following questions showed dependence on *instructor*, but not pre-survey response:

4, 5, 6, 10, 17

- [4] "At least one project that is assigned and structured by the instructor" 
- [5] "A project in which students have some input into the research process and/or what is being studied"
- [6] "A project entirely of student design"  
- [10] "Become responsible for a part of the project"  
- [17] "Present posters"


And the responses to these survey questions were independent of pre-survey responses and the instructor:

1, -2-, 3, 7, 8, 9, 12, -19-, -20-, 21

- [1] "A scripted lab or project in which the students know the expected outcome" 
- [2] "A lab or project in which only the instructor knows the outcome" *Removed   
- [3] "A lab or project where no one knows the outcome"   
- [7] "Work individually" 
- [8] "Work as a whole class" 
- [9] "Work in small groups"  
- [12] "Write a research proposal" 
- [19] "Listen to lectures" *Removed     
- [20] "Read a textbook" *Removed 
- [21] "Work on problem sets" *Removed  
- [22] "Take tests in class" *Removed 



## Figures

For questions 4 and 23 we want to show the interaction between instructor and rookie.
Although for 4, the presurvey response wasn't important, so we will use a cat plot.

### Figure 4A 4B and 4C

Questions 8, 10, and 13 need a cat plot showing Instructor and Rookie

```{r Catplot 8, echo=FALSE}
cat_plot(model = imp_model_Q10_8, pred = Instructor, modx = Rookie,
              interval = TRUE, x.label = "Instructor",  
              y.label = "Student Perceived\nImprovement")
catplot8 <- cat_plot(model = imp_model_Q10_8, pred = Instructor, modx = Rookie,
              interval = TRUE, x.label = "Instructor",  
              y.label = "Student Perceived\nImprovement")
```

```{r Catplot 10, echo=FALSE}
cat_plot(model = imp_model_Q10_10, pred = Instructor, modx = Rookie,
              interval = TRUE, x.label = "Instructor",  
              y.label = "Student Perceived\nImprovement")
catplot10 <- cat_plot(model = imp_model_Q10_10, pred = Instructor, modx = Rookie,
              interval = TRUE, x.label = "Instructor",  
              y.label = "Student Perceived\nImprovement")
```

```{r Catplot 13, echo=FALSE}
cat_plot(model = imp_model_Q10_13, pred = Instructor, modx = Rookie,
              interval = TRUE, x.label = "Instructor",  
              y.label = "Student Perceived\nImprovement")
catplot13 <- cat_plot(model = imp_model_Q10_13, pred = Instructor, modx = Rookie,
              interval = TRUE, x.label = "Instructor",  
              y.label = "Student Perceived\nImprovement")
```


### Removed Figure Q10_2

This was not emphasized

```{r Q10_2 No instructor, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_2_pre, Post = Q9_2_post) %>%
  table() %>%
  as.data.frame() %>%
  ggballoonplot(x = "Q10_2_pre", y = "Post", size = "Freq", 
                ggtheme = theme_gray(), 
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[2], 72), collapse = "\n")) + 
  fill_palette(c("#FFFEFE","#b0cafb","#6598f8","#3c54cd","#21327b"))
```

### Removed Figure Q10_21

This was not emphasized.

```{r Q10_21 No instructor, echo=FALSE}
Q10Clean_withNA %>%
  select(Q10_21_pre, Post=Q9_21_post) %>%
  table() %>%
  as.data.frame() %>%
  ggballoonplot(x = "Q10_21_pre", y = "Post", size = "Freq", 
                ggtheme = theme_gray(), 
                fill = "Post", size.range = c(0, 8),
                title = paste(strwrap(Q10TextClean$Question[21], 72), collapse = "\n")) + 
  fill_palette(c("#FFFEFE","#b0cafb","#6598f8","#3c54cd","#21327b"))
```

For questions where the instructor was included in the final model, but not Rookie status or the pre-survey response (3, 6, and 17) and ALSO the question where it did not depend on any of the variables (7):


### Final Figure 2 v 2026

Depend on Instructor only:

3, 4, 6, 9, 12, 17

```{r Figure 2 Instructor Questions, echo=FALSE}
instructor_q <- Q10Clean_withNA %>%
  select(Instructor, Q03=Q9_3_post, Q04=Q9_4_post, Q06=Q9_6_post, 
         Q09=Q9_9_post, Q12=Q9_12_post, Q17=Q9_17_post)
instructor_q_long <- instructor_q %>% 
  pivot_longer(cols = `Q03`:`Q17`, 
               names_to = c("Question"), 
               values_to = "Post")

instructor_q_long %>%
  table() %>%
  as.data.frame() %>%
  ggballoonplot(x = "Instructor", y = "Post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Question",
                fill = "Post", 
                size.range = c(0, 6)) + 
  fill_palette(c("#FFFEFE","#b0cafb","#6598f8","#3c54cd","#21327b")) +
  scale_x_discrete(guide = guide_axis(angle=70))

print(Q10TextClean$Question[c(3, 4, 6, 9, 12, 17 )])
```

Note that we lost "Figure 4" because it is now incorporated into Figure 2. 
I am instead going to convert Figure 3B (with 9 parts!) into Figure 4.

### Final Figure 4 v 2026

Figure 4 is the combined Cat plots.

-  [8] "Work as a whole class"   
-  [10] "Become responsible for a part of the project"  
-  [13] "Collect data" 

```{r Figure 4, fig.height= 6, fig.width=3, echo = FALSE}
catplot8b <- catplot8 + theme(panel.grid.major = element_blank(),
                              axis.title.x = element_blank(),
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(),
                  axis.line = element_line(colour = "black"),
                  legend.position="none", 
                  plot.title = element_text(size = 10, face = "plain")) +
  coord_flip() +
  ggtitle("Work as a whole class")

catplot8c <- catplot8 + theme(panel.grid.major = element_blank(),
                              axis.title.x = element_blank(),
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(),
                  axis.line = element_line(colour = "black"),
                  legend.position="none", 
                  plot.title = element_text(size = 10, face = "plain")) +
  ggtitle("Work as a whole class")

catplot10b <- catplot10 + theme(panel.grid.major = element_blank(),
                                axis.title.x = element_blank(),
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(),
                  axis.line = element_line(colour = "black"),
                  legend.position="none", 
                  plot.title = element_text(size = 10, face = "plain")) +
  coord_flip() +
  ggtitle("Responsible for a part \nof the project")

catplot13b <- catplot13 + theme(panel.grid.major = element_blank(),
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(),
                  axis.line = element_line(colour = "black"),
                  legend.position="none", 
                  plot.title = element_text(size = 10, face = "plain")) +
  coord_flip() +
  ggtitle("Collect data")

ggarrange(catplot8b, catplot10b,
          catplot13b, ncol = 1, nrow = 3,
          heights = c(0.8, 0.9, 1))
```

```{r Figure 4 Part B}
catplot8c
```


## Instructor Survey Results

We will now examine how the responses to the CURE Instructor Survey might correlate with the student perceptions of gain corresponding to each course element. 
We predict that instructors who placed a greater emphasis on a course element will demonstrate greater perceived gains due to that element.

The five instructors filled out the forms in the summer of 2022. 
Note that it is possible that instructor emphasis shifted slightly in later years, but none of those shifts were dramatic enough to affect these results. 
The forms were PDFs that were sent by email, so I will manually enter the results here.

```{r Entering Data, echo=FALSE}
Instructor_survey <- Q10TextClean %>%
  rename(Q = value)
Instructor_survey$Q <- gsub("_pre", "", Instructor_survey$Q)
Instructor_survey$Q <- gsub("Q10_", "", Instructor_survey$Q)
Instructor_survey$Q <- paste0("Q10_", str_pad(Instructor_survey$Q, 2, side = "left", pad = "0"))
Instructor_survey_complete <- Instructor_survey %>%
  add_column(McGonagall = c(1, 1, 3, 0, 3, 3, 1, 2, 
                            3, 3, 3, 2, 3, 3, 2, 3, 3, 3, 0, 0, 0, 0, 3, 3, 0)) %>%
  add_column(Lupin = c(2, 1, 3, 2, 3, 2, 1, 3, 
                       3, 3, 3, 1, 3, 3, 2, 2, 3, 2, 1, 1, 0, 0, 2, 3, 0)) %>%
  add_column(Dumbledore = c(1, 0, 3, 2, 3, 1, 1, 2, 
                            3, 3, 3, 1, 3, 3, 1, 3, 2, 3, 0, 0, 0, 0, 3, 3, 0)) %>%
  add_column(Hagrid = c(1, 0, 3, 2, 2, 1, 1, 0, 
                        2, 2, 3, 3, 3, 3, 3, 3, 3, 2, 2, 1, 0, 0, 1, 1, 1)) %>%
  add_column(Sinistra = c(2, 0, 3, 2, 2, 3, 2, 1, 
                          3, 3, 3, 3, 3, 3, 3, 3, 3, 2, 0, 0, 0, 0, 2, 3, 0))
Instructor_long <- Instructor_survey_complete %>%
  select(-Question) %>%
  pivot_longer(!Q, names_to = "Instructor", values_to = "Emphasis")
```

First to visualize how much variability there is in each question.

```{r Instructor Emphasis, echo=FALSE}
Instructor_recode <- Instructor_long 
Instructor_recode$Emphasis = recode(as.factor(Instructor_recode$Emphasis), 
                                    "0" = "None/NA", "1" = "Minor", "2" = "Moderate", "3"= "Major")

ggplot(Instructor_recode) +
  geom_bar(aes(x = Q, fill = Emphasis), width = 0.75) +
  coord_flip() +
  fill_palette(c("#FFFEFE", "#b0cafb", "#3c54cd",  "#21327b")) +
  scale_x_discrete(limits=rev) +
  xlab("Question") +
  ylab("Instructors") +
  theme_gray()
```

I want to see if certain questions and instructors cluster together to help decide if there are questions that are more interesting to look at than others.

### Final Figure 5A

```{r Fig 5A Emphasis Heatmap, echo=FALSE}
Instructor_matrix <- Instructor_survey_complete %>%
  select(-Q, -Question) %>%
  as.matrix()
rownames(Instructor_matrix) <- Instructor_survey_complete$Q
pheatmap(Instructor_matrix, cutree_rows = 2, 
         color=c("#FFFEFE", "#b0cafb", "#3c54cd",  "#21327b"), 
         legend_breaks = c(0.4, 1.1, 2, 2.7),
         legend_labels = c("None/NA", "Minor", "Moderate", "Major"), 
         angle_col = 0)
```

The following six questions have at least three instructors who selected NA/None for the Emphasis:

```{r, echo=FALSE}
Instructor_survey_complete %>%
  filter(Q %in% c("Q10_19", "Q10_20", "Q10_02", "Q10_25", "Q10_21", "Q10_22")) %>%
  select(Question) %>%
  print()
```

It is also interesting to note that the following four questions had Major Emphasis in all five sections:

```{r, echo=FALSE}
Instructor_survey_complete %>%
  filter(Q %in% c("Q10_14", "Q10_13", "Q10_03", "Q10_11")) %>%
  select(Question) %>%
  print()
```

Now to test whether student-perceived gains are correlated with instructor emphasis on each course element.

Looking at all the questions together, including those in the previous list where we did not emphasize them.

```{r, echo=FALSE}
Q10_post_long <- Q10Clean_withNA %>%
  select(Instructor, ends_with("_post")) %>%
  pivot_longer(!Instructor, names_to = "Question", values_to = "Gain")
Q10_post_long$Question <- gsub("_post", "", Q10_post_long$Question)
Q10_post_long$Question <- gsub("Q9_", "", Q10_post_long$Question)
Q10_post_long$Question <- paste0("Q10_", str_pad(Q10_post_long$Question, 2, side = "left", pad = "0"))

Q10_post_merged <- Q10_post_long %>%
  left_join(Instructor_long, by = c("Question" = "Q", "Instructor")) %>%
  drop_na()
str(Q10_post_merged)
summary(Q10_post_merged)


emphasis_model <- glm(as.numeric(Gain) ~ Emphasis ,data = Q10_post_merged)
summary(emphasis_model)
drop1(emphasis_model, test = "LRT")
car::Anova(emphasis_model, type = "3", test.statistic = "F")
```

Self-reported gain in these skills is highly dependent on the emphasis placed by the instructor (p < 2e-16).

Now to explore whether this also depended on the instructor.

### Final Figure 5B

```{r Fig 5B Gain Emphasis Interaction, echo=FALSE}
interact_model <- glm(as.numeric(Gain) ~ Emphasis * Instructor, data = Q10_post_merged)

car::Anova(interact_model, type = "3", test.statistic = "F")

no_interact_model <- glm(as.numeric(Gain) ~ Emphasis + Instructor, data = Q10_post_merged)

car::Anova(no_interact_model, type = "3", test.statistic = "F")

interact_plot(model = no_interact_model, pred = Emphasis, modx = Instructor, 
              interval = TRUE, x.label = "Instructor Emphasis",  
              y.label = "Student Percieved Gain")


Q10_post_refactored <- Q10_post_merged %>%
  mutate(Emphasis = as.factor(Emphasis)) %>%
  mutate(Gain = as.numeric(Gain))

cat_model <- glm(Gain ~ Emphasis + Instructor, data = Q10_post_refactored)

summary(cat_model)

car::Anova(cat_model, type = "3", test.statistic = "F")

new_fig5b <- cat_plot(model = cat_model, pred = Emphasis, modx = Instructor, 
              interval = TRUE, x.label = "Instructor Emphasis",  
              y.label = "Student Perceived Gain")

cat_plot(
  model = cat_model, 
  pred = Emphasis, 
  modx = Instructor, 
  interval = TRUE, 
  x.label = "Instructor Emphasis", 
  y.label = "Student Perceived Gain") + 
  theme(
    axis.line = element_line(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) +
  geom_vline(xintercept = c(1.5, 2.5, 3.5), color = "gray80", linetype = "solid")
```

Just to show the interaction:

```{r}
interact_plot(model = interact_model, pred = Emphasis, modx = Instructor, 
              interval = TRUE, x.label = "Instructor Emphasis",  
              y.label = "Student Percieved Gain")
```

## Presurvey by Semester

Responses on the presurvey had an effect on the student perceived gain for several questions.
We want to check to see if the presurvey responses were significantly different in the two semesters,
because that could be a confounding factor.

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_1_pre, Q9_1_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_1Clean_Semester

Q_1_pre_model <- glm(as.numeric(Q10_1_pre) ~ FallSpring, data = Q_1Clean_Semester)
summary(Q_1_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_2_pre, Q9_2_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_2Clean_Semester

Q_2_pre_model <- glm(as.numeric(Q10_2_pre) ~ FallSpring, data = Q_2Clean_Semester)
summary(Q_2_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_3_pre, Q9_3_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_3Clean_Semester

Q_3_pre_model <- glm(as.numeric(Q10_3_pre) ~ FallSpring, data = Q_3Clean_Semester)
summary(Q_3_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_4_pre, Q9_4_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_4Clean_Semester

Q_4_pre_model <- glm(as.numeric(Q10_4_pre) ~ FallSpring, data = Q_4Clean_Semester)
summary(Q_4_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_5_pre, Q9_5_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_5Clean_Semester

Q_5_pre_model <- glm(as.numeric(Q10_5_pre) ~ FallSpring, data = Q_5Clean_Semester)
summary(Q_5_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_6_pre, Q9_6_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_6Clean_Semester

Q_6_pre_model <- glm(as.numeric(Q10_6_pre) ~ FallSpring, data = Q_6Clean_Semester)
summary(Q_6_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_7_pre, Q9_7_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_7Clean_Semester

Q_7_pre_model <- glm(as.numeric(Q10_7_pre) ~ FallSpring, data = Q_7Clean_Semester)
summary(Q_7_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_8_pre, Q9_8_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_8Clean_Semester

Q_8_pre_model <- glm(as.numeric(Q10_8_pre) ~ FallSpring, data = Q_8Clean_Semester)
summary(Q_8_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_9_pre, Q9_9_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_9Clean_Semester

Q_9_pre_model <- glm(as.numeric(Q10_9_pre) ~ FallSpring, data = Q_9Clean_Semester)
summary(Q_9_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_10_pre, Q9_10_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_10Clean_Semester

Q_10_pre_model <- glm(as.numeric(Q10_10_pre) ~ FallSpring, data = Q_10Clean_Semester)
summary(Q_10_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_11_pre, Q9_11_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_11Clean_Semester

Q_11_pre_model <- glm(as.numeric(Q10_11_pre) ~ FallSpring, data = Q_11Clean_Semester)
summary(Q_11_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_12_pre, Q9_12_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_12Clean_Semester

Q_12_pre_model <- glm(as.numeric(Q10_12_pre) ~ FallSpring, data = Q_12Clean_Semester)
summary(Q_12_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_13_pre, Q9_13_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_13Clean_Semester

Q_13_pre_model <- glm(as.numeric(Q10_13_pre) ~ FallSpring, data = Q_13Clean_Semester)
summary(Q_13_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_14_pre, Q9_14_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_14Clean_Semester

Q_14_pre_model <- glm(as.numeric(Q10_14_pre) ~ FallSpring, data = Q_14Clean_Semester)
summary(Q_14_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_15_pre, Q9_15_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_15Clean_Semester

Q_15_pre_model <- glm(as.numeric(Q10_15_pre) ~ FallSpring, data = Q_15Clean_Semester)
summary(Q_15_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_16_pre, Q9_16_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_16Clean_Semester

Q_16_pre_model <- glm(as.numeric(Q10_16_pre) ~ FallSpring, data = Q_16Clean_Semester)
summary(Q_16_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_17_pre, Q9_17_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_17Clean_Semester

Q_17_pre_model <- glm(as.numeric(Q10_17_pre) ~ FallSpring, data = Q_17Clean_Semester)
summary(Q_17_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_18_pre, Q9_18_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_18Clean_Semester

Q_18_pre_model <- glm(as.numeric(Q10_18_pre) ~ FallSpring, data = Q_18Clean_Semester)
summary(Q_18_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_19_pre, Q9_19_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_19Clean_Semester

Q_19_pre_model <- glm(as.numeric(Q10_19_pre) ~ FallSpring, data = Q_19Clean_Semester)
summary(Q_19_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_20_pre, Q9_20_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_20Clean_Semester

Q_20_pre_model <- glm(as.numeric(Q10_20_pre) ~ FallSpring, data = Q_20Clean_Semester)
summary(Q_20_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_21_pre, Q9_21_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_21Clean_Semester

Q_21_pre_model <- glm(as.numeric(Q10_21_pre) ~ FallSpring, data = Q_21Clean_Semester)
summary(Q_21_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_22_pre, Q9_22_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_22Clean_Semester

Q_22_pre_model <- glm(as.numeric(Q10_22_pre) ~ FallSpring, data = Q_22Clean_Semester)
summary(Q_22_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_23_pre, Q9_23_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_23Clean_Semester

Q_23_pre_model <- glm(as.numeric(Q10_23_pre) ~ FallSpring, data = Q_23Clean_Semester)
summary(Q_23_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_24_pre, Q9_24_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_24Clean_Semester

Q_24_pre_model <- glm(as.numeric(Q10_24_pre) ~ FallSpring, data = Q_24Clean_Semester)
summary(Q_24_pre_model)
```

```{r, echo=FALSE}
Q10Clean_withNA %>%
  mutate(FallSpring = case_when(str_detect(Semester, "Fall") ~ "Fall",
                                str_detect(Semester, "Spring") ~ "Spring")) %>%
  select(Q10_25_pre, Q9_25_post, Instructor, Rookie, FallSpring) %>%
  na.omit() -> Q_25Clean_Semester

Q_25_pre_model <- glm(as.numeric(Q10_25_pre) ~ FallSpring, data = Q_25Clean_Semester)
summary(Q_25_pre_model)
```

```{r}
Q10TextClean$Question[3] # p = 0.000878, Estimate = 0.4662
Q10TextClean$Question[4] # p = 0.106, Estimate = 0.17299
Q10TextClean$Question[6] # p = 0.107, Estimate = 0.2634
Q10TextClean$Question[11] # p = 3.37e-08, Estimate = 0.70836
Q10TextClean$Question[12] # p = 0.0146, Estimate = 0.3751
Q10TextClean$Question[18] # p = 0.00017, Estimate = 0.5295
Q10TextClean$Question[19] # p = 0.0158, Estimate =  0.3499
```

After discussion with Moria, we would like to show, as a supplemental table the questions that have p.adjust < 0.05.

## Table S4

```{r Table S4}
stats_table <- tibble(Question = Q10TextClean$Question[11], 
                      Estimate = Q_11_pre_model$coefficients[[2]],
                      p = coef(summary(Q_11_pre_model))[,4][[2]],
                      `p.adj` = p.adjust(coef(summary(Q_11_pre_model))[,4][[2]], n = 25))
stats_table <- stats_table %>%
  add_row(Question = Q10TextClean$Question[18], 
          Estimate = Q_18_pre_model$coefficients[[2]], 
          p = coef(summary(Q_18_pre_model))[,4][[2]], 
          `p.adj` = p.adjust(coef(summary(Q_18_pre_model))[,4][[2]], n = 25))
stats_table <- stats_table %>%
  add_row(Question = Q10TextClean$Question[3], 
          Estimate = Q_3_pre_model$coefficients[[2]], 
          p = coef(summary(Q_3_pre_model))[,4][[2]], 
          `p.adj` = p.adjust(coef(summary(Q_3_pre_model))[,4][[2]], n = 25))

kable(stats_table, "simple")
```


