---
title: "Outcomes"
author: "Ken Field"
date: "Last compiled on `r Sys.Date()`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("ltm")) install.packages("ltm"); library(ltm) #Cronbach’s Alpha
if (!require("MASS")) install.packages("MASS"); library(MASS) #stepAIC() function
if (!require('interactions')) install.packages('interactions'); library(interactions) #Interaction plots
if (!require('sandwich')) install.packages('sandwich'); library(sandwich) #robust errors
if (!require('pheatmap')) install.packages('pheatmap'); library(pheatmap) #heatmap
if (!require('pdftools')) install.packages('pdftools'); library(pdftools) #reading tables from pdfs
if (!require('performance')) install.packages('performance'); library(performance) # visualizing glm
if (!require('pscl')) install.packages('pscl'); library(pscl) # zero-inflated glm
# Always load last
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
```

We wish to determine if the new core classes (CURE Lab and BIO Seminar) are helping students to succeed academically.

## Loading Results

I asked the registrar to help me answer the following questions:
1. What was the DFW rate for first-year students in BIOL 205 and 206 from SP 2017 to FA 2019?
2. What was the DFW rate for first-year students in BIOL 201 and 202 from FA 2021 to SP 2022?

They sent us the files located in the "Grade Outcomes" folder.

Note that this analysis only includes first-year students in the Biology classes, even though there are other students in these classes.

I began working on reading those files in using pdf_text, but that looked like it was going to be a nightmare, so I am going to enter the results in manually.
I later got all the results in excel form and could have imported them more easily, but it was too late.

```{r Entering Results 1}
DFW <- tibble(Class = "BIOL201", Year = "21-22", Semester = "Fall", DFW = 6, Total = 103)
DFW <- DFW %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Fall", DFW = 1, Total = 43) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Spring", DFW = 0, Total = 64) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Spring", DFW = 0, Total = 60) %>%
  add_row(Class = "BIOL205", Year = "17-18", Semester = "Fall", DFW = 4+19, Total = 149) %>%
  add_row(Class = "BIOL205", Year = "18-19", Semester = "Fall", DFW = 9+6+22, Total = 160) %>%
  add_row(Class = "BIOL205", Year = "19-20", Semester = "Fall", DFW = 7+3+7, Total = 162) %>%
  add_row(Class = "BIOL206", Year = "16-17", Semester = "Spring", DFW = 1+1+3, Total = 119) %>%
  add_row(Class = "BIOL206", Year = "17-18", Semester = "Spring", DFW = 5+1+9, Total = 123) %>%
  add_row(Class = "BIOL206", Year = "18-19", Semester = "Spring", DFW = 1+2+4, Total = 149)
DFW <- DFW %>%
  mutate(Pass = Total - DFW) %>%
  mutate(`DFW Rate (%)` = DFW / Total * 100)
```

Summarizing Results

```{r Summary}
DFW %>%
  group_by(Class) %>%
  summarise(`Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
DFW %>%
  group_by(Year) %>%
  summarise(`Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
# Fall Semester
DFW %>%
  filter(Semester == "Fall") %>%
  group_by(Class) %>%
  summarise(DFW = mean(DFW), Enrollment = mean(Total), 
            `Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
# Spring Semester
DFW %>%
  filter(Semester == "Spring") %>%
  group_by(Class) %>%
  summarise(DFW = mean(DFW), Enrollment = mean(Total),
            `Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
```

Initial data exploration:
Although the sample size is quite low, I am going to try a one-sample T test to 
provide some measure of confidence in the difference between the new and old classes.

```{r}
Fall_DFW <- DFW %>%
  filter(Semester == "Fall", Class == "BIOL205") %>%
  select(`DFW Rate (%)`)
t.test(Fall_DFW$`DFW Rate (%)`, mu = 5.82)
t.test(Fall_DFW$`DFW Rate (%)`, mu = 2.32)
```

In the Fall: 

For BIOL201, p = 0.1032

For BIOL202, p = 0.06226


```{r}
Spring_DFW <- DFW %>%
  filter(Semester == "Spring", Class == "BIOL206") %>%
  select(`DFW Rate (%)`)
t.test(Spring_DFW$`DFW Rate (%)`, mu = 0)
```

In the Spring

p = 0.1128

This applies equally to BIOL 201 and 202 because both had a DFW Rate of 0 in the Spring.

However, this is really count data and should be handled by a negative binomial GLM. 

## First year affiliated majors only

Including only first-year students who are undeclared, Biology, Animal Behavior, Cell Biology/Biochemistry, Biophysics, and Neuroscience. 

```{r Entering Results 3}
Majors_DFW <- tibble(Class = "BIOL205", Year = "17-18", Semester = "Fall", DFW = 21, Total = 124+21)
Majors_DFW <- Majors_DFW %>%
  add_row(Class = "BIOL205", Year = "18-19", Semester = "Fall", DFW = 37, Total = 122+37) %>%
  add_row(Class = "BIOL205", Year = "19-20", Semester = "Fall", DFW = 17, Total = 137+17) %>%
  add_row(Class = "BIOL206", Year = "16-17", Semester = "Spring", DFW = 4, Total = 111+4) %>%
  add_row(Class = "BIOL206", Year = "17-18", Semester = "Spring", DFW = 13, Total = 106+13) %>%
  add_row(Class = "BIOL206", Year = "18-19", Semester = "Spring", DFW = 5, Total = 139+5) 
Majors_DFW <- Majors_DFW %>%
  mutate(Pass = Total - DFW) %>%
  mutate(`DFW Rate (%)` = DFW / Total * 100)
```


```{r}
Majors_DFW %>%
  group_by(Class) %>%
  summarise(`Mean DFW Rate (%)` = mean(`DFW Rate (%)`), 
            Sd = sd(`DFW Rate (%)`))
```

Going to compare BIOL205 to BIOL201/202 Fall and BIOL206 to BIOL201/202 Spring.

```{r}
DFW_205 <- Majors_DFW %>%
  filter(Class == "BIOL205") %>%
  select(`DFW Rate (%)`)
DFW_Fall <- DFW %>%
  filter(Class %in% c("BIOL201", "BIOL202")) %>%
  filter(Semester == "Fall") 
DFW_Fall
t.test(DFW_205$`DFW Rate (%)`, mu = (6 + 1)/(103+43) * 100)
```


```{r}
DFW_206 <- Majors_DFW %>%
  filter(Class == "BIOL206") %>%
  select(`DFW Rate (%)`)
DFW_Spring <- DFW %>%
  filter(Class %in% c("BIOL201", "BIOL202")) %>%
  filter(Semester == "Spring") 
DFW_Spring
t.test(DFW_206$`DFW Rate (%)`, mu = 0)
```

This is a better comparison than I did initially, but the results are quite similar.

Comparing 205 to Fall 201/202: t = 3.1497, df = 2, p-value = 0.08774

Comparing 206 to Spring 201/202: t = 2.3996, df = 2, p-value = 0.1385

## Modeling results with negative binomial glm

First I need to convert the summarized results into individual counts. 

https://www.r-bloggers.com/2019/10/expanding-binomial-counts-to-binary-0-1-with-purrrpmap/

```{r Example Data}
dat = structure(list(plot = structure(1:8, .Label = c("plot1", "plot2", 
"plot3", "plot4", "plot5", "plot6", "plot7", "plot8"), class = "factor"), 
    group = structure(c(1L, 1L, 1L, 1L, 2L, 2L, 2L, 2L), .Label = c("g1", 
    "g2"), class = "factor"), num_dead = c(4L, 6L, 6L, 5L, 1L, 4L, 
    3L, 2L), total = c(5L, 7L, 9L, 7L, 8L, 10L, 10L, 7L)), class = "data.frame", row.names = c(NA, 
-8L))

dat

binary_dat = pmap_dfr(dat, 
                      function(group, plot, num_dead, total) {
                           data.frame(plot = plot,
                                      group = group,
                                      dead = c( rep(1, num_dead),
                                                rep(0, total - num_dead) ) )
                      }
)
head(binary_dat)
```

Now to try with the DFW data. 
First, I will select just the data that we need.

```{r}
Old_DFW_dat <- Majors_DFW %>%
  select(Class:Total) %>%
  mutate(Curriculum = "Old")
New_DFW_dat <- DFW %>%
  select(Class:Total) %>%
  filter(Class %in% c("BIOL201", "BIOL202")) %>%
  mutate(Curriculum = "New")
DFW_dat <- rbind(Old_DFW_dat, New_DFW_dat)
DFW_binary_dat = pmap_dfr(DFW_dat, 
                      function(Class, Year, Semester, DFW, Total, Curriculum) {
                           data.frame(Class = Class,
                                      Year = Year,
                                      Semester = Semester,
                                      Curriculum = Curriculum,
                                      DFW = c( rep(1, DFW),
                                                rep(0, Total - DFW) ) )
                      }
)
```

That worked. Now to use that dataframe for a glm.

```{r}
model1 <- glm.nb(DFW ~ Curriculum, data = DFW_binary_dat)
summary(model1)
model_full <- glm.nb(DFW ~ Class * Year * Semester * Curriculum, data = DFW_binary_dat)
summary(model_full)
```

The full model has too many interacting variables to be useful. 
Even with the interactions removed, the model does not converge properly.
I will stick with Model 1 for further exploration.

```{r}
newdata <- data.frame(Curriculum = c("Old", "New"))
newdata
predict.glm(model1, newdata=newdata, type="response")
model1
check_zeroinflation(model1)
check_overdispersion(model1)
performance(model1)
summary(model1)
```

```{r}
exp(1.4986)
exp(1.4986+0.3914)
exp(1.4986-0.3914)
```

The model indicates that students under the old curriculum were 4.5-fold (3.0 - 6.6) more likely to earn a DFW in the first two Biology courses (p = 0.000129).

## Adding results from second year of new curriculum

```{r}
Newer_DFW_dat <- New_DFW_dat %>%
  rbind(c("BIOL201", "22-23", "Fall", 3, 107, "New")) %>%
  rbind(c("BIOL201", "22-23", "Spring", 4, 70, "New")) %>%
  rbind(c("BIOL202", "22-23", "Fall", 2, 42, "New")) %>%
  rbind(c("BIOL201", "22-23", "Spring", 1, 63, "New"))
Newer_DFW_dat <- Newer_DFW_dat %>%
  mutate(DFW = as.numeric(DFW)) %>%
  mutate(Total = as.numeric(Total))
DFW_dat2 <- rbind(Old_DFW_dat, Newer_DFW_dat)
DFW_binary_dat2 <- pmap_dfr(DFW_dat2, 
                      function(Class, Year, Semester, DFW, Total, Curriculum) {
                           data.frame(Class = Class,
                                      Year = Year,
                                      Semester = Semester,
                                      Curriculum = Curriculum,
                                      DFW = c( rep(1, DFW),
                                                rep(0, Total - DFW) ) )
                      }
)
new_model1 <- glm.nb(DFW ~ Curriculum, data = DFW_binary_dat2)
summary(new_model1)
check_zeroinflation(new_model1)
```

That looks good. And I am glad to have checked the zero-inflated model even though we don't need it.

```{r}
exp(1.3256)
exp(1.3256+0.2690)
exp(1.3256-0.2690)
```

The model including the second year data indicates that students under the old curriculum were 3.8-fold (2.9 - 4.9) more likely to earn a DFW in the first two Biology courses (p = 0.000000835).

How does it look with just the old data, but with the zero-inflated model?
However, I determined that the data does not actually have a zero-inflation problem so this was not needed.

```{r}
zero_model1 <- zeroinfl(DFW ~ Curriculum, data = DFW_binary_dat)
summary(zero_model1)
```

```{r}
exp(1.4981)
exp(1.4981+0.3984)
exp(1.4981-0.3984)
```

That is almost identical. And we see that the zero inflation coefficients have very high p values.

## Effect of race/ethnicity and gender

First looking at the old curriculum. 

```{r}
Old_FullDFW <- tibble(Class = "BIOL205", Year = "17-18", Semester = "Fall", Gender = "Female", SoC = "Non-White", 
                      DFW = 5, Total = 30)
Old_FullDFW <- Old_FullDFW %>%
  add_row(Class = "BIOL205", Year = "17-18", Semester = "Fall", Gender = "Female", SoC = "White", DFW = 11, Total = 76) %>%
  add_row(Class = "BIOL205", Year = "17-18", Semester = "Fall", Gender = "Male", SoC = "Non-White", DFW = 4, Total = 15) %>%
  add_row(Class = "BIOL205", Year = "17-18", Semester = "Fall", Gender = "Male", SoC = "White", DFW = 3, Total = 28) %>%
  add_row(Class = "BIOL205", Year = "18-19", Semester = "Fall", Gender = "Female", SoC = "Non-White", DFW = 10, Total = 37) %>%
  add_row(Class = "BIOL205", Year = "18-19", Semester = "Fall", Gender = "Female", SoC = "White", DFW = 19, Total = 89) %>%
  add_row(Class = "BIOL205", Year = "18-19", Semester = "Fall", Gender = "Male", SoC = "Non-White", DFW = 3, Total = 9) %>%
  add_row(Class = "BIOL205", Year = "18-19", Semester = "Fall", Gender = "Male", SoC = "White", DFW = 5, Total = 25) %>%
  add_row(Class = "BIOL205", Year = "19-20", Semester = "Fall", Gender = "Female", SoC = "Non-White", DFW = 3, Total = 25) %>%
  add_row(Class = "BIOL205", Year = "19-20", Semester = "Fall", Gender = "Female", SoC = "White", DFW = 7, Total = 89) %>%
  add_row(Class = "BIOL205", Year = "19-20", Semester = "Fall", Gender = "Male", SoC = "Non-White", DFW = 2, Total = 23) %>%
  add_row(Class = "BIOL205", Year = "19-20", Semester = "Fall", Gender = "Male", SoC = "White", DFW = 5, Total = 25) %>%
  add_row(Class = "BIOL206", Year = "16-17", Semester = "Spring", Gender = "Female", SoC = "Non-White", DFW = 5, Total = 30) %>%
  add_row(Class = "BIOL206", Year = "16-17", Semester = "Spring", Gender = "Female", SoC = "White", DFW = 1, Total = 21) %>%
  add_row(Class = "BIOL206", Year = "16-17", Semester = "Spring", Gender = "Male", SoC = "Non-White", DFW = 2, Total = 11) %>%
  add_row(Class = "BIOL206", Year = "16-17", Semester = "Spring", Gender = "Male", SoC = "White", DFW = 0, Total = 26) %>%
  add_row(Class = "BIOL206", Year = "17-18", Semester = "Spring", Gender = "Female", SoC = "Non-White", DFW = 4, Total = 27) %>%
  add_row(Class = "BIOL206", Year = "17-18", Semester = "Spring", Gender = "Female", SoC = "White", DFW = 4, Total = 61) %>%
  add_row(Class = "BIOL206", Year = "17-18", Semester = "Spring", Gender = "Male", SoC = "Non-White", DFW = 4, Total = 13) %>%
  add_row(Class = "BIOL206", Year = "17-18", Semester = "Spring", Gender = "Male", SoC = "White", DFW = 3, Total = 22) %>%
  add_row(Class = "BIOL206", Year = "18-19", Semester = "Spring", Gender = "Female", SoC = "Non-White", DFW = 3, Total = 38) %>%
  add_row(Class = "BIOL206", Year = "18-19", Semester = "Spring", Gender = "Female", SoC = "White", DFW = 3, Total = 81) %>%
  add_row(Class = "BIOL206", Year = "18-19", Semester = "Spring", Gender = "Male", SoC = "Non-White", DFW = 1, Total = 7) %>%
  add_row(Class = "BIOL206", Year = "18-19", Semester = "Spring", Gender = "Male", SoC = "White", DFW = 0, Total = 23)
summary(Old_FullDFW)
Old_FullDFW_binary_dat <- pmap_dfr(Old_FullDFW, 
                      function(Class, Year, Semester, Gender, SoC, DFW, Total) {
                           data.frame(Class = as.factor(Class),
                                      Year = as.factor(Year),
                                      Semester = as.factor(Semester),
                                      Gender = as.factor(Gender),
                                      SoC = as.factor(SoC),
                                      DFW = c( rep(1, DFW),
                                                rep(0, Total - DFW) ) )
                      }
)
Old_FullDFW_binary_dat <- Old_FullDFW_binary_dat %>%
  mutate(SoC = factor(SoC, levels = c("White", "Non-White")))
summary(Old_FullDFW_binary_dat)
```

Now for the model.

```{r}
glm_model_old_full <- glm.nb(DFW ~ Gender * SoC, data = Old_FullDFW_binary_dat)
summary(glm_model_old_full)
```

This is consistent with my original analysis. 
Neither Race/ethnicity nor Gender had a major effect on DFW rates in the old curriculum. 
Students of color did have a higher rate, but the p value was marginal (0.0925).

Now to look at the data for 201 and 202.

```{r}
New_FullDFW <- tibble(Class = "BIOL201", Year = "22-23", Semester = "Fall", Gender = "Female", SoC = "Non-White", 
                      DFW = 3, Total = 25)
New_FullDFW <- New_FullDFW %>%
  add_row(Class = "BIOL201", Year = "22-23", Semester = "Fall", Gender = "Female", SoC = "White", DFW = 0, Total = 57) %>%
  add_row(Class = "BIOL201", Year = "22-23", Semester = "Fall", Gender = "Male", SoC = "Non-White", DFW = 0, Total = 8) %>%
  add_row(Class = "BIOL201", Year = "22-23", Semester = "Fall", Gender = "Male", SoC = "White", DFW = 0, Total = 17) %>%
  add_row(Class = "BIOL201", Year = "22-23", Semester = "Spring", Gender = "Female", SoC = "Non-White", DFW = 3, Total = 18) %>%
  add_row(Class = "BIOL201", Year = "22-23", Semester = "Spring", Gender = "Female", SoC = "White", DFW = 0, Total = 29) %>%
  add_row(Class = "BIOL201", Year = "22-23", Semester = "Spring", Gender = "Male", SoC = "Non-White", DFW = 0, Total = 7) %>%
  add_row(Class = "BIOL201", Year = "22-23", Semester = "Spring", Gender = "Male", SoC = "White", DFW = 1, Total = 16) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Fall", Gender = "Female", SoC = "Non-White", DFW = 1, Total = 11) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Fall", Gender = "Female", SoC = "White", DFW = 1, Total = 15) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Fall", Gender = "Male", SoC = "Non-White", DFW = 0, Total = 4) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Fall", Gender = "Male", SoC = "White", DFW = 0, Total = 12) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Spring", Gender = "Female", SoC = "Non-White", DFW = 1, Total = 16) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Spring", Gender = "Female", SoC = "White", DFW = 0, Total = 33) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Spring", Gender = "Male", SoC = "Non-White", DFW = 0, Total = 3) %>%
  add_row(Class = "BIOL202", Year = "22-23", Semester = "Spring", Gender = "Male", SoC = "White", DFW = 0, Total = 11) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Fall", Gender = "Female", SoC = "Non-White", DFW = 2, Total = 15) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Fall", Gender = "Female", SoC = "White", DFW = 2, Total = 65) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Fall", Gender = "Male", SoC = "Non-White", DFW = 2, Total = 7) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Fall", Gender = "Male", SoC = "White", DFW = 3, Total = 26) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Spring", Gender = "Female", SoC = "Non-White", DFW = 0, Total = 11) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Spring", Gender = "Female", SoC = "White", DFW = 0, Total = 35) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Spring", Gender = "Male", SoC = "Non-White", DFW = 0, Total = 4) %>%
  add_row(Class = "BIOL201", Year = "21-22", Semester = "Spring", Gender = "Male", SoC = "White", DFW = 0, Total = 17) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Fall", Gender = "Female", SoC = "Non-White", DFW = 0, Total = 8) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Fall", Gender = "Female", SoC = "White", DFW = 0, Total = 25) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Fall", Gender = "Male", SoC = "Non-White", DFW = 1, Total = 3) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Fall", Gender = "Male", SoC = "White", DFW = 0, Total = 7) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Spring", Gender = "Female", SoC = "Non-White", DFW = 0, Total = 7) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Spring", Gender = "Female", SoC = "White", DFW = 0, Total = 40) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Spring", Gender = "Male", SoC = "Non-White", DFW = 0, Total = 2) %>%
  add_row(Class = "BIOL202", Year = "21-22", Semester = "Spring", Gender = "Male", SoC = "White", DFW = 0, Total = 12)
summary(New_FullDFW)
New_FullDFW_binary_dat <- pmap_dfr(New_FullDFW, 
                      function(Class, Year, Semester, Gender, SoC, DFW, Total) {
                           data.frame(Class = as.factor(Class),
                                      Year = as.factor(Year),
                                      Semester = as.factor(Semester),
                                      Gender = as.factor(Gender),
                                      SoC = as.factor(SoC),
                                      DFW = c( rep(1, DFW),
                                                rep(0, Total - DFW) ) )
                      }
)
New_FullDFW_binary_dat <- New_FullDFW_binary_dat %>%
  mutate(SoC = factor(SoC, levels = c("White", "Non-White")))
summary(New_FullDFW_binary_dat)
```

```{r}
glm_model_new_full <- glm.nb(DFW ~ Gender * SoC, data = New_FullDFW_binary_dat)
summary(glm_model_new_full)
logLik(glm_model_new_full)
performance(glm_model_new_full)
check_zeroinflation(glm_model_new_full)
check_model(glm_model_new_full)
```

```{r}
cat_plot(glm_model_new_full, pred = Gender, modx = SoC, interval = TRUE)
```

```{r}
New_FullDFW_binary_dat <- New_FullDFW_binary_dat %>%
  mutate(Curriculum = "New")
Old_FullDFW_binary_dat <- Old_FullDFW_binary_dat %>%
  mutate(Curriculum = "Old")
FullDFW_binary_dat <- rbind(Old_FullDFW_binary_dat, New_FullDFW_binary_dat) %>%
  mutate(Curriculum = factor(Curriculum, levels = c("Old", "New")))
glm_model_all <- glm.nb(DFW ~ Curriculum * Gender * SoC, data = FullDFW_binary_dat)
summary(glm_model_all)
glm_model_full <- glm.nb(DFW ~ Curriculum + Gender * SoC, data = FullDFW_binary_dat)
summary(glm_model_full)
stepAIC(glm_model_full, direction = "backward")
glm_model_selected <- glm.nb(DFW ~ Curriculum + SoC, data = FullDFW_binary_dat)
summary(glm_model_selected)
```

```{r}
1/exp(-1.2522)
1/exp(-1.2522+0.2439)
1/exp(-1.2522-0.2439)

exp(0.6590)
exp(0.6590+0.1781)
exp(0.6590-0.1781)
```



```{r}
check_model(glm_model_full)
cat_plot(glm_model_full, pred = SoC, modx = Curriculum, mod2 = Gender, 
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Students of Color"),
         mod2.labels = c("Female Students", "Male Students"),
         modx.labels = c("Prior", "CURE"),
         x.label = "", y.label = "DFW Likelihood")
```

And using the selected model, that shows only curriculum and SoC are critical:

```{r}
cat_plot(glm_model_selected, pred = SoC, modx = Curriculum, 
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Students of Color"),
         modx.labels = c("Prior", "BIO Seminar/CURE Lab"),
         x.label = "", y.label = "DFW Likelihood")
```

Compare by class instead of old vs new curriculum:

```{r}
glm_model_full2 <- glm.nb(DFW ~ Class + Gender * SoC, data = FullDFW_binary_dat)
summary(glm_model_full2)
cat_plot(glm_model_full2, pred = SoC, modx = Class, mod2 = Gender,
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Students of Color"),
         mod2.labels = c("Female Students", "Male Students"),
         x.label = "", y.label = "DFW Likelihood")
```

## Figure 8

Let's look at just the first year of the CURE (for the paper).

```{r Figure 8}
summary(FullDFW_binary_dat)
FullDFW_binary_dat %>% 
  filter(Year != "22-23") %>%
  filter(Class != "BIOL201") -> filtered_binary_dat
summary(filtered_binary_dat)
Just1year202.glm <- glm.nb(DFW ~ Curriculum + SoC, data = filtered_binary_dat) 
summary(Just1year202.glm)
check_overdispersion(Just1year202.glm)
check_zeroinflation(Just1year202.glm)
check_model(Just1year202.glm)
cat_plot(Just1year202.glm, pred = SoC, modx = Curriculum, 
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Students of Color"),
         modx.labels = c("Prior", "CURE"),
         x.label = "", y.label = "DFW Likelihood")
```

```{r}
1/exp(-2.5235)
1/exp(-2.5235+1.0051)
1/exp(-2.5235-1.0051)

exp(0.5039)
exp(0.5039+0.1942)
exp(0.5039-0.1942)
```


How does it look if we compare by class instead of just curriculum?

```{r}
Just1year202.glm2 <- glm.nb(DFW ~ Class + Gender * SoC, data = filtered_binary_dat) 
summary(Just1year202.glm2)
cat_plot(Just1year202.glm2, pred = SoC, modx = Class, mod2 = Gender, 
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Students of Color"),
         mod2.labels = c("Female Students", "Male Students"),
         x.label = "", y.label = "DFW Likelihood")
```

And now let's isolate just BIOL202 to see if SoC and/or gender effect DFW rates.

```{r}
filtered_binary_dat %>%
  filter(Class == "BIOL202") -> only202year1_binary_dat
summary(only202year1_binary_dat)
table(only202year1_binary_dat$Gender, only202year1_binary_dat$SoC)
only202year1.glm <- glm.nb(DFW ~ Gender * SoC, data = only202year1_binary_dat) 
summary(only202year1.glm)
cat_plot(only202year1.glm, pred = SoC, modx = Gender, interval = TRUE)
```

Well that is an ugly graphic because the numbers of DFWs are so low, but the model does confirm that there is no significant effect of Gender or Race/ethnicity on DFW rates in the first year of BIOL 202.
