---
title: "Outcomes"
author: "Ken Field"
date: "Last compiled on `r Sys.Date()`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dpi = 300)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("ltm")) install.packages("ltm"); library(ltm) #Cronbach’s Alpha
if (!require("MASS")) install.packages("MASS"); library(MASS) #stepAIC() function
if (!require('interactions')) install.packages('interactions'); library(interactions) #Interaction plots
if (!require('sandwich')) install.packages('sandwich'); library(sandwich) #robust errors
if (!require('pheatmap')) install.packages('pheatmap'); library(pheatmap) #heatmap
if (!require('pdftools')) install.packages('pdftools'); library(pdftools) #reading tables from pdfs
if (!require('performance')) install.packages('performance'); library(performance) # visualizing glm
if (!require('pscl')) install.packages('pscl'); library(pscl) # zero-inflated glm
if (!require('DHARMa')) install.packages('DHARMa'); library(DHARMa) # for testing glms
if (!require("magrittr")) install.packages("magrittr"); library(magrittr)
if (!require("conflicted")) install.packages("conflicted"); library(conflicted)
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
conflict_prefer_all("dplyr", quiet = TRUE)
```

We wish to determine if the new core classes (CURE Lab and BIO Seminar) are helping students to succeed academically.

## Loading Results

I asked the registrar to help me answer the following questions:
1. What was the DFW rate for first-year students in BIOL 205 and 206 from SP 2017 to FA 2019?
2. What was the DFW rate for all students in BIOL 201 and 202 from FA 2021 to SP 2024?

They sent us the files located in the "Grade Outcomes" folder.
I have removed any identifying information for the students and instructors.

Note that the analysis 205 and 206 only includes first-year students in these Biology classes, even though there are other students in these classes.
This is to make it more comparable to 201 and 202 which are not taken by nearly as broad a spectrum of students.

Importing data for 205 and 206.

```{r Entering Results 1, echo=FALSE}
BIOL205_206 <- read_excel("Grade Outcomes/BIOL205_206 Grade Distribution_First Years by Gender & Ethnicity.xlsx", 
                          sheet = "Detail by Student") %>%
  select("Academic Period Description", "Course Identification", "Student Classification", 
         "Gender Description", "Ethnicity Description", "First-Generation Indicator", "Final Grade") %>%
  filter(`Student Classification` == "FR") %>%
  select(-`Student Classification`) %>%
  rename(Semester = `Academic Period Description`, Course = `Course Identification`,
         Gender = `Gender Description`, 
         Grade = `Final Grade`) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  mutate(across(Grade, str_replace, 'A|B|C', 'Pass')) %>%
  mutate(across(Grade, str_replace, 'Pass-', 'Pass')) %>%
  mutate(across(Grade, str_replace, 'Pass\\+', 'Pass')) %>%
  filter(`Ethnicity Description` != "Unknown") %>%
  mutate(isWhite = `Ethnicity Description`=="White") %>%
  mutate(`Race/Ethnicity` = if_else(isWhite, "White", "nonWhite")) %>%
  select(-`Ethnicity Description`, -isWhite) %>%
  mutate(Curriculum = "Old")


names(BIOL205_206)
summary(as.factor(BIOL205_206$Course))
summary(as.factor(BIOL205_206$Grade))
summary(as.factor(BIOL205_206$Semester))
summary(as.factor(BIOL205_206$Gender))
summary(as.factor(BIOL205_206$`Race/Ethnicity`))
```

Importing data from 201 and 202.
The spreadsheets have a very awkward format and were checked carefully. 
Before I imported the data, I consolidated it within excel to make the three years have a consistent format.

```{r, echo=FALSE}
D_F_W_Report_BIOL201_202_AY21_22 <- read_excel("Grade Outcomes/D, F, W Report_BIOL201 & 202 AY21-22.xlsx", 
                                               sheet = "forImport")
D_F_W_Report_BIOL201_202_AY22_23 <- read_excel("Grade Outcomes/D, F, W Report_BIOL201 & 202 AY22-23.xlsx", 
                                               sheet = "forImport")
Grade_Distribution_BIOL_201_202_AY23_24 <- read_excel("Grade Outcomes/Grade Distribution_BIOL 201 & 202 AY23-24.xlsx", 
                                                      sheet = "forImport")
```

Converting Totals into Passes by subtracting each D, F, or W.

```{r, echo=FALSE}
names(D_F_W_Report_BIOL201_202_AY21_22)
DFW_21_22 <- D_F_W_Report_BIOL201_202_AY21_22 %>%
  mutate(Pass_Female_White = Female_Total_White - (F_Female_White + W_Female_White)) %>%
  select(-Female_Total_White) %>%
  mutate(Pass_Male_White = Male_Total_White - (D_Male_White + W_Male_White)) %>%
  select(-Male_Total_White) %>%
  mutate(Pass_Female_nonWhite = Female_Total_nonWhite - (F_Female_nonWhite + W_Female_nonWhite)) %>%
  select(-Female_Total_nonWhite) %>%
  mutate(Pass_Male_nonWhite = Male_Total_nonWhite - (D_Male_nonWhite + W_Male_nonWhite)) %>%
  select(-Male_Total_nonWhite)

names(D_F_W_Report_BIOL201_202_AY22_23)
DFW_22_23 <- D_F_W_Report_BIOL201_202_AY22_23 %>%
  mutate(Pass_Female_White = Female_Total_White - (D_Female_White + F_Female_White + W_Female_White)) %>%
  select(-Female_Total_White) %>%
  mutate(Pass_Male_White = Male_Total_White - (W_Male_White)) %>%
  select(-Male_Total_White) %>%
  mutate(Pass_Female_nonWhite = Female_Total_nonWhite - (D_Female_nonWhite + F_Female_nonWhite + W_Female_nonWhite)) %>%
  select(-Female_Total_nonWhite) %>%
  mutate(Pass_Male_nonWhite = Male_Total_nonWhite - (W_Male_nonWhite)) %>%
  select(-Male_Total_nonWhite)

names(Grade_Distribution_BIOL_201_202_AY23_24)
DFW_23_24 <- Grade_Distribution_BIOL_201_202_AY23_24 %>%
  mutate(Pass_Female_White = Female_Total_White - (D_Female_White + F_Female_White + W_Female_White)) %>%
  select(-Female_Total_White) %>%
  mutate(Pass_Male_White = Male_Total_White - (D_Male_White + F_Male_White)) %>%
  select(-Male_Total_White) %>%
  mutate(Pass_Female_nonWhite = Female_Total_nonWhite - (D_Female_nonWhite + F_Female_nonWhite + W_Female_nonWhite)) %>%
  select(-Female_Total_nonWhite) %>%
  mutate(Pass_Male_nonWhite = Male_Total_nonWhite - (D_Male_nonWhite + F_Male_nonWhite)) %>%
  select(-Male_Total_nonWhite)
```

Now pivoting the table and splitting the categories

```{r}
names(DFW_21_22)
DFW_21_22_long <- DFW_21_22 %>%
  pivot_longer(cols = D_Male_White:Pass_Male_nonWhite, 
               names_to = "Group", values_to = "Count") %>%
  separate_wider_delim(Group, delim = "_", names = c("Grade", "Gender", "Race/Ethnicity")) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  uncount(weights = Count) 
summary(as.factor(DFW_21_22_long$Grade))

names(DFW_22_23)
DFW_22_23_long <- DFW_22_23 %>%
  pivot_longer(cols = D_Female_White:Pass_Male_nonWhite, 
               names_to = "Group", values_to = "Count") %>%
  separate_wider_delim(Group, delim = "_", names = c("Grade", "Gender", "Race/Ethnicity")) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  uncount(weights = Count) 
summary(as.factor(DFW_22_23_long$Grade))

names(DFW_23_24)
DFW_23_24_long <- DFW_23_24 %>%
  pivot_longer(cols = D_Female_White:Pass_Male_nonWhite, 
               names_to = "Group", values_to = "Count") %>%
  separate_wider_delim(Group, delim = "_", names = c("Grade", "Gender", "Race/Ethnicity")) %>%
  mutate(across(Grade, str_replace, 'D|F|W', 'DFW')) %>%
  uncount(weights = Count) 
summary(as.factor(DFW_23_24_long$Grade))

DFW_201_202 <- DFW_21_22_long %>%
  add_row(DFW_22_23_long) %>%
  add_row(DFW_23_24_long) %>%
  mutate(Curriculum = "New")

```

Combining the two datasets

```{r}
All_DFW <- BIOL205_206 %>%
  select(names(DFW_201_202)) %>%
  add_row(DFW_201_202) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(Curriculum = fct_relevel(Curriculum, c("Old", "New"))) %>%
  mutate(`Race/Ethnicity` = fct_relevel(`Race/Ethnicity`, c("White", "nonWhite")))

Only202_DFW <- All_DFW %>%
  filter(Course != "BIOL201")

summary(All_DFW)
summary(Only202_DFW)

All_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())

Only202_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())
Only202_DFW %>%
  group_by(Course, Grade) %>%
  summarise(n = n())
```

## Modeling results with negative binomial glm

### Both 201 and 202

```{r, echo=FALSE, warning=FALSE}
All_DFW <- All_DFW %>%
  mutate(DFW = Grade == "DFW")

model1 <- glm.nb(DFW ~ Curriculum, data = All_DFW)
summary(model1)
model_full <- glm.nb(DFW ~ Curriculum * Gender * `Race/Ethnicity`, data = All_DFW)
summary(model_full)
```

```{r, echo=FALSE, warning=FALSE}
selected_model <- model_full %>%
  stepAIC(direction = "backward")
summary(selected_model)
```

A very big effect of the new curriculum and a small effect of the interaction between curriculum and race/ethnicity.

```{r, echo=FALSE}
newdata <- data.frame(Curriculum = c("Old", "New", "Old", "New")) %>%
  mutate('Race/Ethnicity' = c("White", "White", "nonWhite", "nonWhite"))
predict.glm(selected_model, newdata=newdata, type="response")
selected_model
check_zeroinflation(selected_model)
check_overdispersion(selected_model)
performance(selected_model)
summary(selected_model)
```

```{r, echo=FALSE}
exp(-2.2797)
exp(-2.2797+0.3154)
exp(-2.2797-0.3154)
```


```{r, echo=FALSE}
exp(-1.6256)
exp(-1.6256+0.1270)
exp(-1.6256-0.1270)

1/ exp(-1.6256)
1/ exp(-1.6256+0.1270)
1/ exp(-1.6256-0.1270)
```

The model indicates that students under the old curriculum were 5.1-fold (4.4 - 5.8) more likely to earn a DFW in the first two Biology courses (p = 2.54e-07).

```{r, Combo 201 and 202, echo=FALSE}
cat_plot(selected_model, pred = Curriculum, modx = `Race/Ethnicity`, interval = TRUE)
```

### Only 202

Adding Fall vs Spring to the full model.

```{r, echo=FALSE, warning=FALSE}
Only202_DFW <- Only202_DFW %>%
  mutate(DFW = Grade == "DFW") %>%
  mutate(Fall_Spring = case_when(str_detect(Semester, "Fall") ~ "Fall", 
                                 str_detect(Semester, "Spring") ~ "Spring"))

model1_202 <- glm.nb(DFW ~ Curriculum, data = Only202_DFW)
summary(model1_202)
model_full_202 <- glm.nb(DFW ~ Fall_Spring * Curriculum * Gender * `Race/Ethnicity`, data = Only202_DFW)
summary(model_full_202)
```

Fall_Spring is playing a bigger role than Curriculum. 
We need to account for that.

```{r, echo=FALSE, warning=FALSE}
selected_model_202 <- model_full_202 %>%
  stepAIC(direction = "backward")
summary(selected_model_202)
```


```{r, echo=FALSE}
selected_model_202
check_zeroinflation(selected_model_202)
check_overdispersion(selected_model_202)
performance(selected_model_202)
summary(selected_model_202)
```

Fall semester:

```{r, echo=FALSE}
exp(-1.9040)
exp(-1.9040+0.1409)
exp(-1.9040-0.1409)
```

Spring semester:

```{r, echo=FALSE}
exp(-1.9040-1.2884)
exp(-1.9040-1.2884+0.1409)
exp(-1.9040-1.2884-0.1409)
```

Curriculum effect:

```{r, echo=FALSE}
exp(-2.0715)
exp(-2.0715+0.5104)
exp(-2.0715-0.5104)

1/ exp(-2.0715)
1/ exp(-2.0715+0.5104)
1/ exp(-2.0715-0.5104)
```

The model indicates that students in CURE Lab were 7.9-fold (4.76 - 13.2) less likely to earn a DFW than in first two Biology courses of the prior curriculum (p = 4.94e-05), after controlling for the effect of semester. There was no significant interaction between curriculum and either race/ethnicity or gender identity.

```{r, echo=FALSE}
exp(0.4801)
exp(0.4801+0.1999)
exp(0.4801-0.1999)
```

```{r, echo=FALSE}
cat_plot(selected_model_202, pred = Curriculum, modx = `Race/Ethnicity`, mod2 = Fall_Spring, interval = TRUE)
```


## Figure 9

```{r Figure 9, echo=FALSE}
catplot_202 <- cat_plot(selected_model_202, pred = `Race/Ethnicity`, modx = Curriculum, mod2 = Fall_Spring,
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("White Students","Students of Color"),
         modx.labels = c("Prior", "CURE"),
         x.label = "", y.label = "DFW Likelihood")
catplot_202
catplot_202_fixed <- catplot_202 + theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(), 
                  axis.line = element_line(colour = "black"), 
                  legend.position="none",
                  plot.title = element_text(size = 10, face = "plain")) 

catplot_202_fixed
```

### Only 201

```{r, echo=FALSE, warning=FALSE}
Only201_DFW <- All_DFW %>%
  filter(Course != "BIOL202") %>%
  mutate(Fall_Spring = case_when(str_detect(Semester, "Fall") ~ "Fall", 
                                 str_detect(Semester, "Spring") ~ "Spring"))

summary(All_DFW)
summary(Only201_DFW)

All_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())

Only201_DFW %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())
Only201_DFW %>%
  group_by(Course, Grade) %>%
  summarise(n = n())
Only201_DFW <- Only201_DFW %>%
  mutate(DFW = Grade == "DFW")

model1_201 <- glm.nb(DFW ~ Curriculum, data = Only201_DFW)
summary(model1_201)
model_full_201 <- glm.nb(DFW ~ Fall_Spring * Curriculum * Gender * `Race/Ethnicity`, data = Only201_DFW)
summary(model_full_201)
```


```{r, echo=FALSE, warning=FALSE}
selected_model_201 <- model_full_201 %>%
  stepAIC(direction = "backward")
summary(selected_model_201)
```


```{r, echo=FALSE}
selected_model_201
check_zeroinflation(selected_model_201)
check_overdispersion(selected_model_201)
performance(selected_model_201)
summary(selected_model_201)
```

That is very messy.
Let's just add semester to the simple model.

```{r, echo=FALSE, warning=FALSE}
model2_201 <- glm.nb(DFW ~ Fall_Spring * Curriculum, data = Only201_DFW)
summary(model2_201)
selected_model2_201 <- stepAIC(model2_201, direction = "backward")
summary(selected_model2_201)
```


```{r, echo=FALSE}
exp(-1.8297)
exp(-1.8297+0.1122)
exp(-1.8297-0.1122)
```


```{r, echo=FALSE}
exp(-1.0288)
exp(-1.0288 +0.2228)
exp(-1.0288 -0.2228)

1/ exp(-1.0288 )
1/ exp(-1.0288 +0.2228)
1/ exp(-1.0288 -0.2228)
```

The model indicates that students in BIOL 201 were  2.80-fold (2.24 - 3.50) less likely to earn a DFW than in first two Biology courses of the prior curriculum (p = 3.87e-06), after controlling for the effect of semester.

```{r, echo=FALSE}
exp(0.5556)
exp(0.5556+0.1779)
exp(0.5556-0.1779)
```

```{r, echo=FALSE}
cat_plot(selected_model_201, pred = Curriculum, modx = `Race/Ethnicity`, interval = TRUE)
```


## Figure 9 201 version

```{r Figure 9 201, echo=FALSE}
catplot_201 <- cat_plot(selected_model2_201, pred = Fall_Spring, modx = Curriculum,
         interval = TRUE, errorbar.width = 0.5, 
         pred.labels = c("Fall","Spring"),
         modx.labels = c("Prior", "CURE"),
         x.label = "", y.label = "DFW Likelihood")
catplot_201
catplot_201_fixed <- catplot_201 + theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_blank(), 
                  axis.line = element_line(colour = "black"), 
                  legend.position="none",
                  plot.title = element_text(size = 10, face = "plain")) 

catplot_201_fixed
```

## First-gen status

One of the studies of COVID impacts demonstrated that first-gen students were more highly impacted than other students.
We would like to see how that factor translates to our outcomes.

```{r, echo=FALSE}
Firstgen_201_202 <- read_excel("Grade Outcomes/Grade Distribution_BIOL 201 & 202_2021 to 2024.Firstgen.xlsx", 
                               sheet = "Grade Detail", col_types = c("skip", "text", "text", 
                                                                     "text", "text", "skip", "text", "text"))
Firstgen_201_202 <- Firstgen_201_202 %>%
  select(Course = `Course Identification`, Semester = `Academic Period Description`, `Final Grade`,
         Gender = `Gender Description`, `First-Generation Indicator`) %>%
  filter(`Final Grade` != "NC")
Firstgen_201_202_clean <- Firstgen_201_202 %>%
  mutate(Grade = case_when(`Final Grade` %in% c("D", "F", "W") ~ "DFW",
                           .default = "Pass")) %>%
  mutate(Curriculum = "New") %>%
  select(-`Final Grade`)

All_DFW_Firstgen <- BIOL205_206 %>%
  select(names(Firstgen_201_202_clean)) %>%
  add_row(Firstgen_201_202_clean) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(Curriculum = fct_relevel(Curriculum, c("Old", "New"))) %>%
  mutate(Fall_Spring = case_when(str_detect(Semester, "Fall") ~ "Fall", 
                                 str_detect(Semester, "Spring") ~ "Spring")) %>%
  mutate(Fall_Spring = as.factor(Fall_Spring)) %>%
  mutate(DFW = (Grade == "DFW"))

Only202_DFW_Firstgen <- All_DFW_Firstgen %>%
  filter(Course != "BIOL201")
Only201_DFW_Firstgen <- All_DFW_Firstgen %>%
  filter(Course != "BIOL202")

summary(All_DFW_Firstgen)
summary(Only202_DFW_Firstgen)

All_DFW_Firstgen %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())

Only202_DFW_Firstgen %>%
  group_by(Curriculum, Grade) %>%
  summarise(n = n())
Only202_DFW_Firstgen %>%
  group_by(Course, Grade) %>%
  summarise(n = n())
```

```{r, echo=FALSE, warning=FALSE}
model1_Firstgen_202 <- glm.nb(DFW ~ `First-Generation Indicator` * Curriculum, data = Only202_DFW_Firstgen)
summary(model1_Firstgen_202)
model_full_Firstgen_202 <- glm.nb(DFW ~ `First-Generation Indicator` * Fall_Spring * Curriculum, data = Only202_DFW_Firstgen)
summary(model_full_Firstgen_202)
```


```{r, echo=FALSE, warning=FALSE}
selected_model_Firstgen_202 <- model_full_Firstgen_202 %>%
  stepAIC(direction = "backward")
summary(selected_model_Firstgen_202)
```

```{r}
# First gen
exp(0.4003)
exp(0.4003-0.2582)
exp(0.4003+0.2582)
# Race/ethnicity (from earlier 202 model)
exp(0.3117)
exp(0.3117-0.2326)
exp(0.3117+0.2326)
```


That analysis showed that including first-generation status marginally improved the model, but it was very minor compared to semester and curriculum. This was true for both the effect size and the significance.

The effect size of first-gen status (1.49 (1.15-1.93)) and significance (p = 0.121) was similar to the effect of race/ethnicity in the earlier model, (1.36 (1.08-1.72), p = 0.1803), after accounting for the effects of semester and curriculum.

