---
title: "Opinion Change Question"
author: "Ken Field"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("skimr")) install.packages("skimr"); library(skimr) #skim() function
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("ltm")) install.packages("ltm"); library(ltm) #Cronbach’s Alpha
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
```

## Loading Results

Loading in the results without instructor information:

```{r}
NoInstructor <- read_delim("Deidentified Surveys/NoInstructor.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
NoInstructorQuestions <- read_delim("Deidentified Surveys/NoInstructorQuestions.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
```

## Opinion change

Comparing the responses to Pre11 and Post13:

```{r Pre Q11}
PreQ11 <- NoInstructor %>%
  select(Semester = Semester_pre, starts_with("Q11")) %>%
  select(Semester, ends_with("_pre"))
Q11Text <- NoInstructorQuestions %>%
  filter(startsWith(value, "Q11")) %>%
  filter(endsWith(value, "_pre"))
Q11Text$Question[1]
Q11TextClean <- Q11Text %>%
  mutate(Question = str_remove(Q11Text$Question, "It has become common to say that no student is an empty bucket, waiting for a teacher to pour in knowledge. Research on learning acknowledges that students approach a course with well-formed opinions of themselves and of the subject matter. In this section we present questions about science and questions about you. These will help us put learning in context. For each item below please rate your agreement with the item - "))
Q11TextClean$Question
```

```{r Post Q13}
PostQ13 <- NoInstructor %>%
  select(Semester = Semester_pre, starts_with("Q13")) %>%
  select(Semester, ends_with("_post"))

Q13Text <- NoInstructorQuestions %>%
  filter(startsWith(value, "Q13")) %>%
  filter(endsWith(value, "_post"))
Q13Text$Question[1]
Q13TextClean <- Q13Text %>%
  mutate(Question = str_remove(Q13Text$Question, "In the pretest you responded to questions about science. Below the questions are posed again. Your answers will help us decide between two hypotheses, that the opinions are reliable over time \\(test-retest reliability\\) or that the opinions change as a result of your experience. For each item below please rate your agreement with the item - "))
Q13TextClean$Question

Q11TextClean$Question == Q13TextClean$Question
```

Now to compare the pre and post responses for those questions:

```{r}
MergedQ11 <- bind_cols(PreQ11, PostQ13) %>%
  rename(Semester = `Semester...1`) %>%
  select(-`Semester...24`)
head(MergedQ11)
Q11Factors <- MergedQ11 %>%
  select(starts_with("Q")) %>%
  mutate_all(funs(ordered(.,(levels = c("Strongly disagree", "Disagree", 
                                       "Neutral", "Agree", "Strongly agree"))))) 
Q11Clean <- MergedQ11 %>%
  select(-starts_with("Q")) %>%
  cbind(Q11Factors)
```

First let's just look at the contingency tables to see if everything looks right.

```{r}
print("Rows represents pre-survey response, Columns represent post-survey response.")
print("First for All sections then for then for Fall 2021, Spring 2022.")
Q11TextClean$Question[1]
table(Q11Clean$Q11_1_pre, Q11Clean$Q13_1_post)
print("By Semester")
Q11TextClean$Question[1]
table(Q11Clean$Q11_1_pre, Q11Clean$Q13_1_post, Q11Clean$Semester)
```

Experimenting with some other visualizations

```{r Setup}
addmargins(xtabs(~Q11_1_pre+Q13_1_post, data=Q11Clean))
addmargins(table(Q11Clean$Q11_1_pre, Q11Clean$Q13_1_post))

Q11Clean %>%
  select(Q11_1_pre, Q13_1_post, Semester) %>%
  table() 

Q11Clean %>%
  select(Q11_1_pre, Q13_1_post) %>%
  table()

# Colors are set up to be white for no change, blue for increase, red for decrease. 
# Dark colors are for changes of 2 or more categories.
# Palette came from https://www.schemecolor.com/red-white-blue-gradient.php (Happy Independence Day!)

# colorcolumn = c("#FFFEFE", "#DB7A7B", "#BB0103", "#BB0103", "#BB0103", 
#                 "#8F88D2", "#FFFEFE", "#DB7A7B", "#BB0103", "#BB0103",
#                 "#1207A3", "#8F88D2", "#FFFEFE", "#DB7A7B", "#BB0103",
#                 "#1207A3", "#1207A3", "#8F88D2", "#FFFEFE", "#DB7A7B",
#                 "#1207A3", "#1207A3", "#1207A3", "#8F88D2", "#FFFEFE")

colorcolumn = c("No Change", "Disagree +1", "Disagree >1", "Disagree >1", "Disagree >1", 
                "Agree +1", "No Change", "Disagree +1", "Disagree >1", "Disagree >1",
                "Agree >1", "Agree +1", "No Change", "Disagree +1", "Disagree >1",
                "Agree >1", "Agree >1", "Agree +1", "No Change", "Disagree +1",
                "Agree >1", "Agree >1", "Agree >1", "Agree +1", "No Change")

colorcolumn <- factor(colorcolumn, 
                         levels = c("Agree >1", "Agree +1", "No Change", "Disagree +1", "Disagree >1"))
```

```{r Q11_1}
Q11Clean %>%
  select(Q11_1_pre, Q13_1_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(colorcolumn = colorcolumn)

Q11Clean %>%
  select(Q11_1_pre, Q13_1_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_1_pre", y = "Q13_1_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[1], 72), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))
```

The stated goal of this series of questions, according to the survey itself, is to decide between two hypotheses, that the opinions are reliable over time (test-retest reliability) or that the opinions change as a result of your experience.

According to some quick review of the statistics literature, at least two alternatives can be considered:

1.  "Chronbach's Alpha is a way to measure the internal consistency of a questionnaire or survey." <https://www.statology.org/cronbachs-alpha-in-r/>

2.  "For measuring reliability for two tests, use the Pearson Correlation Coefficient. One disadvantage: it overestimates the true relationship for small samples (under 15)." <https://www.statisticshowto.com/test-retest-reliability/>

Other alternatives that we might want to consider are intraclass correlation (might be useful to look at different demographic groups) <https://www.statisticshowto.com/intraclass-correlation/> or this newer test-retest reliability package: <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6536112/> <https://github.com/mathesong/relfeas>

I will use Chronbach's Alpha for my analysis because it appears well-suited for this type of measurement. 
After discussing the preliminary results with some of the other authors, we decided to use a cutoff of 0.7 or higher for support of the null hypothesis (corresponding to Acceptable, Good, or Excellent consistency between the pre- and post- surveys). 
Support for the alternative hypothesis, that the experience in the course influenced the survey results, will be inferred from an alpha value less than 0.5 (Unacceptable). 
Alpha values between 0.5 and 0.7 will be inconclusive. 

```{r}
Q11Clean %>%
  select(Q11_1_pre, Q13_1_post) %>%
  cronbach.alpha(CI = TRUE)

my_skim <-skim_with(numeric = sfl(median, iqr = IQR))

Q11Clean %>%
  transmute(Q11_1_pre = as.numeric(Q11_1_pre), 
            Q13_1_post = as.numeric(Q13_1_post), 
            Difference = Q13_1_post - Q11_1_pre) %>%
  my_skim()
```


## Cronbach's Alpha

The following table describes how different values of Cronbach's Alpha are usually interpreted:

| Cronbach's Alpha | Internal consistency |
|------------------|----------------------|
| 0.9 ≤ α          | Excellent            |
| 0.8 ≤ α \< 0.9   | Good                 |
| 0.7 ≤ α \< 0.8   | Acceptable           |
| 0.6 ≤ α \< 0.7   | Questionable         |
| 0.5 ≤ α \< 0.6   | Poor                 |
| α \< 0.5         | Unacceptable         |

The conclusion is that the internal consistency of the survey result for question 1 is Unacceptable (alpha: 0.32), supporting the alternative hypothesis that the students experiences influenced their responses to this question.

Student perception changed by 0.1764706	+/- 0.8190655 on the survey.

```{r Q11_2}
Q11Clean %>%
  select(Q11_2_pre, Q13_2_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_2_pre", y = "Q13_2_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[2], 72), collapse = "\n")) + 
 fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_2_pre, Q13_2_post) %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_2_pre = as.numeric(Q11_2_pre), 
            Q13_2_post = as.numeric(Q13_2_post), 
            Difference = Q13_2_post - Q11_2_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 2 is Unacceptable (alpha: 0.457), supporting the alternative hypothesis that the students experiences influenced their responses to this question.

Student perception increased by an average -0.09411765 +/- 1.0073956 on the survey.
	

```{r Q11_3}
Q11Clean %>%
  select(Q11_3_pre, Q13_3_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_3_pre", y = "Q13_3_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[3], 72), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_3_pre, Q13_3_post) %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_3_pre = as.numeric(Q11_3_pre), 
            Q13_3_post = as.numeric(Q13_3_post), 
            Difference = Q13_3_post - Q11_3_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 3 is Poor (alpha: 0.565), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception increased by an average 0.1411765 +/- 0.7096770 on the survey.


```{r Q11_4}
Q11Clean %>%
  select(Q11_4_pre, Q13_4_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_4_pre", y = "Q13_4_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[4], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_4_pre, Q13_4_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_4_pre = as.numeric(Q11_4_pre), Q13_4_post = as.numeric(Q13_4_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_4_post - Q11_4_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 4 is Questionable (alpha: 0.663), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average 0.2317073 +/- 1.0098133 on the survey.

```{r Q11_5}
Q11Clean %>%
  select(Q11_5_pre, Q13_5_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_5_pre", y = "Q13_5_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[5], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_5_pre, Q13_5_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_5_pre = as.numeric(Q11_5_pre), Q13_5_post = as.numeric(Q13_5_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_5_post - Q11_5_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 5 is Questionable (alpha: 0.621), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average 0.1411765 +/- 1.0818078 on the survey.

```{r Q11_6}
Q11Clean %>%
  select(Q11_6_pre, Q13_6_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_6_pre", y = "Q13_6_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[6], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_6_pre, Q13_6_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_6_pre = as.numeric(Q11_6_pre), Q13_6_post = as.numeric(Q13_6_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_6_post - Q11_6_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 6 is Questionable (alpha: 0.698), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average -0.1428571 +/- 0.9711856 on the survey.

```{r Q11_7}
Q11Clean %>%
  select(Q11_7_pre, Q13_7_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_7_pre", y = "Q13_7_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[7], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_7_pre, Q13_7_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_7_pre = as.numeric(Q11_7_pre), Q13_7_post = as.numeric(Q13_7_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_7_post - Q11_7_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 7 is Poor (alpha: 0.557), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average -0.1882353 +/- 0.6453887 on the survey.

```{r Q11_8}
Q11Clean %>%
  select(Q11_8_pre, Q13_8_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_8_pre", y = "Q13_8_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[8], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_8_pre, Q13_8_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_8_pre = as.numeric(Q11_8_pre), Q13_8_post = as.numeric(Q13_8_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_8_post - Q11_8_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 8 is Poor (alpha: 0.501), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average -0.09411765 +/- 0.8677218 on the survey.

```{r Q11_9}
Q11Clean %>%
  select(Q11_9_pre, Q13_9_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_9_pre", y = "Q13_9_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[9], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_9_pre, Q13_9_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_9_pre = as.numeric(Q11_9_pre), Q13_9_post = as.numeric(Q13_9_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_9_post - Q11_9_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 9 is Unacceptable (alpha: 0.49), supporting the alternative hypothesis that the students experiences influenced their responses to this question.

Student perception changed by an average -0.09638554 +/- 1.0074655 on the survey.


```{r Q11_10}
Q11Clean %>%
  select(Q11_10_pre, Q13_10_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_10_pre", y = "Q13_10_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[10], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_10_pre, Q13_10_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_10_pre = as.numeric(Q11_10_pre), Q13_10_post = as.numeric(Q13_10_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_10_post - Q11_10_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 10 is Unacceptable (alpha: 0.444), supporting the alternative hypothesis that the students experiences influenced their responses to this question.

Student perception changed by an average 0.000000 +/- 0.6942101 on the survey.

```{r Q11_11}
Q11Clean %>%
  select(Q11_11_pre, Q13_11_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_11_pre", y = "Q13_11_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[11], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_11_pre, Q13_11_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_11_pre = as.numeric(Q11_11_pre), Q13_11_post = as.numeric(Q13_11_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_11_post - Q11_11_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 11 is Acceptable (alpha: 0.719), not supporting the alternative hypothesis that the students experiences influenced their responses to this question.

```{r Q11_12}
Q11Clean %>%
  select(Q11_12_pre, Q13_12_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_12_pre", y = "Q13_12_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[12], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_12_pre, Q13_12_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_12_pre = as.numeric(Q11_12_pre), Q13_12_post = as.numeric(Q13_12_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_12_post - Q11_12_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 12 is Poor (alpha: 0.578), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average -0.1764706 +/- 1.0598346 on the survey.

```{r Q11_13}
Q11Clean %>%
  select(Q11_13_pre, Q13_13_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_13_pre", y = "Q13_13_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[13], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_13_pre, Q13_13_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_13_pre = as.numeric(Q11_13_pre), Q13_13_post = as.numeric(Q13_13_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_13_post - Q11_13_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 13 is Questionable (alpha: 0.665), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average 0.2235294 +/- 0.6432150 on the survey.

```{r Q11_14}
Q11Clean %>%
  select(Q11_14_pre, Q13_14_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_14_pre", y = "Q13_14_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[14], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_14_pre, Q13_14_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_14_pre = as.numeric(Q11_14_pre), Q13_14_post = as.numeric(Q13_14_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_14_post - Q11_14_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 14 is Questionable (alpha: 0.617), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average 0.3614458 +/- 0.8493658 on the survey.

```{r Q11_15}
Q11Clean %>%
  select(Q11_15_pre, Q13_15_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_15_pre", y = "Q13_15_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[15], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_15_pre, Q13_15_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_15_pre = as.numeric(Q11_15_pre), Q13_15_post = as.numeric(Q13_15_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_15_post - Q11_15_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 15 is Questionable (alpha: 0.671), supporting inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average -0.08333333 +/- 0.9468824 on the survey.


```{r Q11_16}
Q11Clean %>%
  select(Q11_16_pre, Q13_16_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_16_pre", y = "Q13_16_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[16], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_16_pre, Q13_16_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_16_pre = as.numeric(Q11_16_pre), Q13_16_post = as.numeric(Q13_16_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_16_post - Q11_16_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 16 is Questionable (alpha: 0.622), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average 0.1411765 +/- 0.8884569 on the survey.

```{r Q11_17}
Q11Clean %>%
  select(Q11_17_pre, Q13_17_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_17_pre", y = "Q13_17_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[17], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_17_pre, Q13_17_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_17_pre = as.numeric(Q11_17_pre), Q13_17_post = as.numeric(Q13_17_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_17_post - Q11_17_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 17 is Unacceptable (alpha: 0.351), supporting the alternative hypothesis that the students experiences influenced their responses to this question.

Student perception changed by an average -0.02352941 +/- 0.8725506 on the survey.

```{r Q11_18}
Q11Clean %>%
  select(Q11_18_pre, Q13_18_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_18_pre", y = "Q13_18_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[18], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_18_pre, Q13_18_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_18_pre = as.numeric(Q11_18_pre), Q13_18_post = as.numeric(Q13_18_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_18_post - Q11_18_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 18 is Unacceptable (alpha: 0.405), supporting the alternative hypothesis that the students experiences influenced their responses to this question.

Student perception changed by an average 0.07142857 +/- 0.8328455 on the survey.

```{r Q11_19}
Q11Clean %>%
  select(Q11_19_pre, Q13_19_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_19_pre", y = "Q13_19_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[19], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_19_pre, Q13_19_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_19_pre = as.numeric(Q11_19_pre), Q13_19_post = as.numeric(Q13_19_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_19_post - Q11_19_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 19 is Poor (alpha: 0.562), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average 0.1294118 +/- 1.0887765 on the survey.

```{r Q11_20}
Q11Clean %>%
  select(Q11_20_pre, Q13_20_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_20_pre", y = "Q13_20_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[20], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_20_pre, Q13_20_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_20_pre = as.numeric(Q11_20_pre), Q13_20_post = as.numeric(Q13_20_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_20_post - Q11_20_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 20 is Acceptable (alpha: 0.772), not supporting the alternative hypothesis that the students experiences influenced their responses to this question.

```{r Q11_21}
Q11Clean %>%
  select(Q11_21_pre, Q13_21_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_21_pre", y = "Q13_21_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[21], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_21_pre, Q13_21_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_21_pre = as.numeric(Q11_21_pre), Q13_21_post = as.numeric(Q13_21_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_21_post - Q11_21_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 21 is Poor (alpha: 0.546), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average 0.1071429 +/- 0.9696336 on the survey.

```{r Q11_22}
Q11Clean %>%
  select(Q11_22_pre, Q13_22_post) %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = colorcolumn) %>%
  ggballoonplot(x = "Q11_22_pre", y = "Q13_22_post", size = "Freq", 
                ggtheme = theme_gray(), fill = "Change", size.range = c(0, 20), 
                title = paste(strwrap(Q11TextClean$Question[22], 60), collapse = "\n")) + 
  fill_palette(c( "#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" ))

Q11Clean %>%
  select(Q11_22_pre, Q13_22_post) %>%
  na.omit() %>%
  cronbach.alpha(CI = TRUE)

Q11Clean %>%
  transmute(Q11_22_pre = as.numeric(Q11_22_pre), Q13_22_post = as.numeric(Q13_22_post) ) %>%
  na.omit() %>%
  mutate(Difference = Q13_22_post - Q11_22_pre) %>%
  my_skim()
```

The conclusion is that the internal consistency of the survey result for question 22 is Questionable (alpha: 0.616), providing inconclusive support that the students experiences influenced their responses to this question.

Student perception changed by an average -0.1529412 +/- 0.6268949 on the survey.

## Combined Figure

To show some of these figures together, I will make a facet plot so that they are all on the same scale. 

We want to combine 1, 2, 9, 10, 17, and 18.

### Final Figure 1

```{r Combined Q11 Figure}
pre_q <- Q11Clean %>%
  select(Q01=Q11_1_pre, 
         Q02=Q11_2_pre, 
         Q09=Q11_9_pre, 
         Q10=Q11_10_pre, 
         Q17=Q11_17_pre, 
         Q18=Q11_18_pre)

pre_q_long <- pre_q %>% 
    pivot_longer(cols= `Q01`:`Q18`,
                 names_to = c("Question"), 
               values_to = "Pre")

post_q <- Q11Clean %>%
  select(Q01=Q13_1_post, 
         Q02=Q13_2_post, 
         Q09=Q13_9_post, 
         Q10=Q13_10_post, 
         Q17=Q13_17_post, 
         Q18=Q13_18_post)

post_q_long <- post_q %>% 
    pivot_longer(cols= `Q01`:`Q18`,
                 names_to = c("Question"), 
               values_to = "Post")
combined_q_long <- pre_q_long %>%
  cbind(select(post_q_long, "Post")) %>%
  na.omit()

combined_q_long %>%
  table() %>%
  as.data.frame() %>%
  add_column(Change = rep(colorcolumn, each = 6)) %>%
  ggballoonplot(x = "Pre", y = "Post", size = "Freq", 
                ggtheme = theme_gray(), facet.by = "Question",
                fill = "Change", 
                size.range = c(0, 6)) + 
  fill_palette(c("#1207A3","#8F88D2","#FFFEFE", "#DB7A7B","#BB0103" )) +
  scale_x_discrete(guide = guide_axis(angle=45))
```

