---
title: "Post Benefits Question"
author: "Ken Field"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    keep_md: yes
  pdf_document: default
---

IMPORTANT NOTE

This Rmd uses the deidentified results and is safe to share.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
if (!require("ggpubr")) install.packages("ggpubr"); library(ggpubr)
if (!require("kableExtra")) install.packages("kableExtra"); library(kableExtra)
if (!require("plotly")) install.packages("plotly"); library(plotly)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("stringr")) install.packages("stringr"); library(stringr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
if (!require("car")) install.packages("car"); library(car) #Anova
if (!require("conflicted")) install.packages("conflicted"); library(conflicted) #dplyr to rule them all
if (!require('interactions')) install.packages('interactions'); library(interactions) #Interaction plots
if (!require('nlme')) install.packages('nlme'); library(nlme) #to use ML estimates in glm
if (!require('lme4')) install.packages('lme4'); library(lme4) #mixed effects models
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)
conflict_prefer_all("dplyr", quiet = TRUE)
```

## Loading Results

Loading in the results without instructor information. 
Note that because we want to analyze demographics for this question, we cannot look at instructor because that would lead to individuals being identifiable. 
We also need to be careful about looking at both gender and race at the same time.

```{r Load data}
NoInstructorYear1 <- read_delim("Deidentified Surveys/Year1.NoInstructor.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE) %>%
  rename(Semester = Semester_pre)
NoInstructorYear2 <- read_delim("Deidentified Surveys/Year2.NoInstructor.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
NoInstructorYear3 <- read_delim("Deidentified Surveys/Year3.NoInstructor.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
NoInstructor <- bind_rows(NoInstructorYear1, NoInstructorYear2, NoInstructorYear3)

NoInstructorQuestions <- read_delim("Deidentified Surveys/Year3.NoInstructorQuestions.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
```

Removing any student who did not agree with the informed consent question:

```{r, echo=FALSE}
NoInstructor <- NoInstructor %>%
  filter(Q1_pre == "Agree")
```

## Benefits of research experience

This question (post-survey question 10) was only in the post-survey.
I am going to try to keep the demographics for this analysis later.

Note that pre-survey question 10 matched with post-survey question 9, while pre-survey question 11 matched with post-survey question 13. Post-survey question 10 was not matched with a pre-survey question.

```{r Post Q10, echo=FALSE}
PostQ10 <- NoInstructor %>%
  select(Semester, Q4_pre, ends_with("_post")) %>%
  select(Semester, Gender = Q2_post, 
         Ethnicity = Q3_post, ClassYear = Q4_pre,
         starts_with("Q10"))
PostQ10 <- PostQ10 %>%
  mutate(ClassYear=recode(ClassYear, 
                          'I am a first-year college undergraduate.'='First', 
                          'I am a second-year college undergraduate'='Second',
                          'I am a third-year college undergraduate'='Third'))

Q10Text <- NoInstructorQuestions %>%
  filter(startsWith(value, "Q10")) %>%
  filter(endsWith(value, "_post"))
Q10Text$Question[01]
Q10TextClean <- Q10Text %>%
  mutate(Question = str_remove(Q10Text$Question, "In this section of the survey you will be asked to consider a variety of possible benefits you may have gained from your research experience. If for any reason you prefer not to answer, or consider the question irrelevant to you, please choose the \"\"Not applicable / Prefer not to answer\"\" option - "))
Q10TextClean$Question
```

Now to see the responses:

```{r, echo=FALSE}
head(PostQ10)
Q10Factors <- PostQ10 %>%
  select(starts_with("Q")) %>%
  mutate_all(funs(ordered(.,(levels = c("Very large gain", "Large gain", 
                                       "Moderate gain", "Small gain", 
                                       "No gain or very small gain"))))) 
Q10Clean <- PostQ10 %>%
  select(-starts_with("Q")) %>%
  cbind(Q10Factors) %>%
  mutate(Gender = as.factor(Gender)) %>%
  mutate(Ethnicity = as.factor(Ethnicity)) %>%
  mutate(ClassYear = as.factor(ClassYear))
summary(Q10Clean)
```

```{r, echo=FALSE}
dataQ10 <- as.data.frame(table(Q10Clean$Q10_1_post)) %>%
  full_join(as.data.frame(table(Q10Clean$Q10_2_post)), by = "Var1") %>% 
  full_join(as.data.frame(table(Q10Clean$Q10_3_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_4_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_5_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_6_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_7_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_8_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_9_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_10_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_11_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_12_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_13_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_14_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_15_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_16_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_17_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_18_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_19_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_20_post)), by = "Var1") %>%
  full_join(as.data.frame(table(Q10Clean$Q10_21_post)), by = "Var1") 

names(dataQ10) <- c("Var1", names(Q10Clean)[4:24])
names(dataQ10) <- gsub("_post", "", names(dataQ10))
rownames(dataQ10) <- dataQ10$Var1
dataQ10 <- dataQ10 %>%
  select(-Var1)

ggballoonplot(t(dataQ10))

print("In this section of the survey you will be asked to consider a variety of possible benefits you may have gained from your research experience. If for any reason you prefer not to answer, or consider the question irrelevant to you, please choose the Not applicable / Prefer not to answer option - ")

print(Q10TextClean)
```

## Cleaning Demographics 

Note that we decided to simplify the race/ethnicity variable in the hopes of keeping a large enough
sample size for analysis. This is still necessary even though we have 3 years of results.

```{r Demographics}
Q10 <- Q10Clean 
names(Q10) <- gsub("Q10_", "Q", names(Q10))
names(Q10) <- gsub("_post", "", names(Q10))

# Remove Prefer not to answer and recode to white and other race/ethnicity.
Q10_demo <- Q10 %>%
  filter(Ethnicity != "Prefer not to answer") %>% 
  mutate(`Race/Ethnicity` = recode(Ethnicity, 
                                   "White" = "White Students", "Filipino" = "Asian Students",
                                   "Asian American" = "Asian Students",
                                   .default = "Other Students of Color")) %>%
  mutate(`Race/Ethnicity` = factor(`Race/Ethnicity`, levels = c("White Students", "Asian Students", "Other Students of Color"))) %>%
  mutate(ClassYear = as.factor(recode(ClassYear, 
                                      "First" = "First", "Second" = "not First", "Third" = "not First"))) %>%
  select(-Ethnicity) %>%
  rename(Q01=Q1, Q02=Q2, Q03=Q3, Q04=Q4, Q05=Q5, Q06=Q6, Q07=Q7, Q08=Q8, Q09=Q9)

table(Q10$Ethnicity, Q10$Gender)
table(Q10$Ethnicity)
table(Q10$Gender)
table(Q10_demo$`Race/Ethnicity`)
```

## Bar plots

```{r Q10 Bar, echo=FALSE}
ggplot(Q10_demo) +
  geom_bar(aes(x = Gender, fill = Q01), position = 'fill', width = 0.5, na.rm = TRUE) +
  facet_grid(Q10_demo$Race) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Gender') +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

With only one year of data, we did not look at each question by both Gender and Race. 
This was revisited when we got more data.

```{r, echo=FALSE}
table(Q10_demo$`Race/Ethnicity`, Q10_demo$Gender)
```

We will need to remove the Non-binary and Prefer not to answer students, but we can keep 
the Male and Female students separate.

```{r, echo=FALSE}
Q10_demo <- Q10_demo %>%
  filter(Gender %in% c("Female", "Male"))

table(Q10_demo$`Race/Ethnicity`, Q10_demo$Gender)
```

The numbers of non-white students who are not first years is quite small (only 3).
We should not look at both class year and race together.

```{r, echo=FALSE}
table(Q10_demo$`Race/Ethnicity`, Q10_demo$ClassYear)
```

Prepare the data to look at all of the questions at once.

```{r, echo=FALSE}
Q10_demo_long <- Q10_demo %>% 
  pivot_longer(cols = `Q01`:`Q21`, 
               names_to = "Question", 
               values_to = "Response")
```

```{r Q10 By Gender, fig.width=4, fig.height=8, echo=FALSE}
ggplot(Q10_demo_long) +
  geom_bar(aes(x = Gender, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_long$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Gender') +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray() +
  theme(legend.position="none")
```

```{r Q10 By Race, fig.width=4, fig.height=8, echo=FALSE}
ggplot(Q10_demo_long) +
  geom_bar(aes(x = `Race/Ethnicity`, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_long$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Race/Ethnicity') +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray() +
  theme(legend.position="none")
```

```{r Q10 By Class Year, fig.width=4, fig.height=8, echo=FALSE}
ggplot(Q10_demo_long) +
  geom_bar(aes(x = `ClassYear`, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_long$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Class Year') +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray() +
  theme(legend.position="none")
```

```{r Q10 By 6 Semesters, fig.width=4, fig.height=8, echo=FALSE}
ggplot(Q10_demo_long) +
  geom_bar(aes(x = `Semester`, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_long$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Semester') +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray() +
  theme(legend.position="none")
```

Simplifying the semesters to compare Fall to Spring.

```{r, echo=FALSE}
Q10_demo_long <- Q10_demo_long %>%
  mutate(across(Semester, str_replace, ' 2021| 2022| 2023| 2024', '')) %>%
  mutate(Semester = as.factor(Semester))
```


```{r Q10 By Semester, fig.width=4, fig.height=8, echo=FALSE}
ggplot(Q10_demo_long) +
  geom_bar(aes(x = `Semester`, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_long$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Semester') +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray() +
  theme(legend.position="none")
```

## Statistical models 

For each question, testing whether gender or race were significant.
I am also including semester because we expect students who have had a prior semester of the new Biology core to also have had some influence on their responses.

For this analysis we will consider all Fall and Spring semesters together.
We will also look at the first-year students versus the others. 

Should the sophomores and junior  be put into "Spring" for the previous experience analysis? 
(probably, but just leaving them out of the semester analysis is much easier)

Note that the dependent variable in the model is calculated as "5-as.numeric(Response)" because the responses range from 1=Very large gain to 5=No gain or very small gain. 
This converts the response variable into a numeric value from 0 to 4 with a positive estimate meaning an improvement in the response on the qualitative scale.

## Analysis by ClassYear and Gender {.tabset .tabset-pills}

### Q10_01

```{r Q01 model 1, echo=FALSE}
print(Q10TextClean$Question[01])
Q01_select <- Q10_demo_long %>%
  filter(Question == "Q01") %>%
  na.omit() 
Q01_model_1 <- glm(data = Q01_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q01_model_1)
Q01_drop1 <- drop1(Q01_model_1, test = "LRT") %>% print()
```

### Q10_02

```{r Q02 model 1, echo=FALSE}
print(Q10TextClean$Question[02])
Q02_select <- Q10_demo_long %>%
  filter(Question == "Q02") %>%
  na.omit() 
Q02_model_1 <- glm(data = Q02_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q02_model_1)
Q02_drop1 <- drop1(Q02_model_1, test = "LRT") %>% print()
```

### Q10_03

```{r Q03 model 1, echo=FALSE}
print(Q10TextClean$Question[03])
Q03_select <- Q10_demo_long %>%
  filter(Question == "Q03") %>%
  na.omit() 
Q03_model_1 <- glm(data = Q03_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q03_model_1)
Q03_drop1 <- drop1(Q03_model_1, test = "LRT") %>% print()

Q03_select %>% group_by(Response) %>% tally()
```

### Q10_04

```{r Q04 model 1, echo=FALSE}
print(Q10TextClean$Question[04])
Q04_select <- Q10_demo_long %>%
  filter(Question == "Q04") %>%
  na.omit() 
Q04_model_1 <- glm(data = Q04_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q04_model_1)
Q04_drop1 <- drop1(Q04_model_1, test = "LRT") %>% print()
```

### Q10_05

```{r Q05 model 1, echo=FALSE}
print(Q10TextClean$Question[05])
Q05_select <- Q10_demo_long %>%
  filter(Question == "Q05") %>%
  na.omit() 
Q05_model_1 <- glm(data = Q05_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q05_model_1)
Q05_drop1 <- drop1(Q05_model_1, test = "LRT") %>% print()
```

### Q10_06

```{r Q06 model 1, echo=FALSE}
print(Q10TextClean$Question[06])
Q06_select <- Q10_demo_long %>%
  filter(Question == "Q06") %>%
  na.omit() 
Q06_model_1 <- glm(data = Q06_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q06_model_1)
Q06_drop1 <- drop1(Q06_model_1, test = "LRT") %>% print()
```

### Q10_07

```{r Q07 model 1, echo=FALSE}
print(Q10TextClean$Question[07])
Q07_select <- Q10_demo_long %>%
  filter(Question == "Q07") %>%
  na.omit() 
Q07_model_1 <- glm(data = Q07_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q07_model_1)
Q07_drop1 <- drop1(Q07_model_1, test = "LRT") %>% print()
```

### Q10_08

```{r Q08 model 1, echo=FALSE}
print(Q10TextClean$Question[08])
Q08_select <- Q10_demo_long %>%
  filter(Question == "Q08") %>%
  na.omit() 
Q08_model_1 <- glm(data = Q08_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q08_model_1)
Q08_drop1 <- drop1(Q08_model_1, test = "LRT") %>% print()
```

### Q10_09

```{r Q09 model 1, echo=FALSE}
print(Q10TextClean$Question[09])
Q09_select <- Q10_demo_long %>%
  filter(Question == "Q09") %>%
  na.omit() 
Q09_model_1 <- glm(data = Q09_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q09_model_1)
Q09_drop1 <- drop1(Q09_model_1, test = "LRT") %>% print()
```

### Q10_10

```{r Q10 model 1, echo=FALSE}
print(Q10TextClean$Question[10])
Q10_select <- Q10_demo_long %>%
  filter(Question == "Q10") %>%
  na.omit() 
Q10_model_1 <- glm(data = Q10_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q10_model_1)
drop1(Q10_model_1, test = "LRT")
Q10_drop1 <- drop1(Q10_model_1, test = "LRT") %>% print()
```

### Q10_11

```{r Q11 model 1, echo=FALSE}
print(Q10TextClean$Question[11])
Q11_select <- Q10_demo_long %>%
  filter(Question == "Q11") %>%
  na.omit() 
Q11_model_1 <- glm(data = Q11_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q11_model_1)
Q11_drop1 <- drop1(Q11_model_1, test = "LRT") %>% print()
```

### Q10_12

```{r Q12 model 1, echo=FALSE}
print(Q10TextClean$Question[12])
Q12_select <- Q10_demo_long %>%
  filter(Question == "Q12") %>%
  na.omit() 
Q12_model_1 <- glm(data = Q12_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q12_model_1)
Q12_drop1 <- drop1(Q12_model_1, test = "LRT") %>% print()
```

### Q10_13

```{r Q13 model 1, echo=FALSE}
print(Q10TextClean$Question[13])
Q13_select <- Q10_demo_long %>%
  filter(Question == "Q13") %>%
  na.omit() 
Q13_model_1 <- glm(data = Q13_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q13_model_1)
Q13_drop1 <- drop1(Q13_model_1, test = "LRT") %>% print()
```

### Q10_14

```{r Q14 model 1, echo=FALSE}
print(Q10TextClean$Question[14])
Q14_select <- Q10_demo_long %>%
  filter(Question == "Q14") %>%
  na.omit() 
Q14_model_1 <- glm(data = Q14_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q14_model_1)
Q14_drop1 <- drop1(Q14_model_1, test = "LRT") %>% print()
```

### Q10_15

```{r Q15 model 1, echo=FALSE}
print(Q10TextClean$Question[15])
Q15_select <- Q10_demo_long %>%
  filter(Question == "Q15") %>%
  na.omit() 
Q15_model_1 <- glm(data = Q15_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q15_model_1)
Q15_drop1 <- drop1(Q15_model_1, test = "LRT") %>% print()
```

### Q10_16

```{r Q16 model 1, echo=FALSE}
print(Q10TextClean$Question[16])
Q16_select <- Q10_demo_long %>%
  filter(Question == "Q16") %>%
  na.omit() 
Q16_model_1 <- glm(data = Q16_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q16_model_1)
Q16_drop1 <- drop1(Q16_model_1, test = "LRT") %>% print()
```

### Q10_17

```{r Q17 model 1, echo=FALSE}
print(Q10TextClean$Question[17])
Q17_select <- Q10_demo_long %>%
  filter(Question == "Q17") %>%
  na.omit() 
Q17_model_1 <- glm(data = Q17_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q17_model_1)
Q17_drop1 <- drop1(Q17_model_1, test = "LRT") %>% print()
```

### Q10_18

```{r Q18 model 1, echo=FALSE}
print(Q10TextClean$Question[18])
Q18_select <- Q10_demo_long %>%
  filter(Question == "Q18") %>%
  na.omit() 
Q18_model_1 <- glm(data = Q18_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q18_model_1)
Q18_drop1 <- drop1(Q18_model_1, test = "LRT") %>% print()
```

### Q10_19

```{r Q19 model 1, echo=FALSE}
print(Q10TextClean$Question[19])
Q19_select <- Q10_demo_long %>%
  filter(Question == "Q19") %>%
  na.omit() 
Q19_model_1 <- glm(data = Q19_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q19_model_1)
Q19_drop1 <- drop1(Q19_model_1, test = "LRT") %>% print()
```

### Q10_20

```{r Q20 model 1, echo=FALSE}
print(Q10TextClean$Question[20])
Q20_select <- Q10_demo_long %>%
  filter(Question == "Q20") %>%
  na.omit() 
Q20_model_1 <- glm(data = Q20_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender)
summary(Q20_model_1)
Q20_drop1 <- drop1(Q20_model_1, test = "LRT") %>% print()
```

### Q10_21

```{r Q21 model 1, echo=FALSE}
print(Q10TextClean$Question[21])
Q21_select <- Q10_demo_long %>%
  filter(Question == "Q21") %>%
  na.omit() 
Q21_model_1 <- glm(data = Q21_select, 
                 5-as.numeric(Response) ~ ClassYear * Gender) 
summary(Q21_model_1)
Q21_drop1 <- drop1(Q21_model_1, test = "LRT") %>% print()
```

## Summary of Analysis by ClassYear and Gender

**This analysis was not changed by separating Asian Students**

Most of the questions depended on Gender alone, but that question is better dealt in Model 2.

The following questions showed dependence on Class Year alone:

- Q10_04: "Readiness for more demanding research" Estimate -0.508 for not First Year.
- Q10_12: "Learning ethical conduct in your field" Estimate -0.446 for not First Year.

The following questions showed dependence on Class Year and also an interaction with Gender:

- Q10_03: "Tolerance for obstacles faced in the research process" Estimate -0.979 for not First Year.
- Q10_08: "Understanding of how scientists work on real problems" Estimate -0.473 for not First Year.
- Q10_11: "Understanding science" Estimate -0.660 for not First Year.
- Q10_18: "Understanding of how scientists think" Estimate -0.615 for not First Year.
- Q10_21: "Confidence in my potential to be a teacher of science" Estimate -0.835 for not First Year.

For each of these questions that maintained the interaction during model selection, 
the effect size of the interaction was always at least as large (and usually larger) than that of Class Year alone. 
This means that male students who were not first-year students showed similar perceived benefits as first-year students, 
while female students showed significantly less perceived benefits. 

Here are the cat_plots showing these interactions:

```{r Interaction Q10_03, echo=FALSE}
cat_plot(model = Q03_model_1, pred = ClassYear, modx = Gender,
              interval = TRUE, x.label = "Class Year",  
              y.label = "Student Percieved Gain")
```


```{r Interaction Q10_08, echo=FALSE}
cat_plot(model = Q08_model_1, pred = ClassYear, modx = Gender,
              interval = TRUE, x.label = "Class Year",  
              y.label = "Student Percieved Gain")
```

```{r Interaction Q10_11, echo=FALSE}
cat_plot(model = Q11_model_1, pred = ClassYear, modx = Gender,
              interval = TRUE, x.label = "Class Year",  
              y.label = "Student Percieved Gain")
```

```{r Interaction Q10_18, echo=FALSE}
cat_plot(model = Q18_model_1, pred = ClassYear, modx = Gender,
              interval = TRUE, x.label = "Class Year",  
              y.label = "Student Percieved Gain")
```

```{r Interaction Q10_32, echo=FALSE}
cat_plot(model = Q21_model_1, pred = ClassYear, modx = Gender, 
              interval = TRUE, x.label = "Class Year",  
              y.label = "Student Percieved Gain")
```


## Analysis by Semester and Demo {.tabset .tabset-pills}

For the new and improved analysis, we have removed the interaction between gender and race/ethnicity, separated asian students from other students of color, and also changed to using an alpha value cutoff of 0.05 instead of AIC for model selection.

After further consideration, we are also using a mixed effects model.

### Q10_01

```{r Q01 model 2, echo=FALSE}
print(Q10TextClean$Question[01])
Q01_select <- Q10_demo_long %>%
  filter(Question == "Q01") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q01_model <- glm(data = Q01_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q01_model)

Anova(Q01_model, type = "3", test.statistic = "F")

# Testing a glmm approach 
lmer_model_Q10_1 <- lmer(5-as.numeric(Response) ~ 
                           Gender + `Race/Ethnicity` + (1 | Semester), data = Q01_select)
summary(lmer_model_Q10_1)
Anova(lmer_model_Q10_1, type = "3", test.statistic = "F")

# Fit both models with ML
Q01_fixed <- Q01_select |>
  rename(Race_Ethnicity = `Race/Ethnicity`)
imp_model_Q10_1_ml <- gls(5-as.numeric(Response) ~ Semester + Gender + Race_Ethnicity, 
                          data = Q01_fixed, method = "ML")
lme_model_Q10_1_ml <- lme(fixed = 5-as.numeric(Response) ~ Semester + Gender + Race_Ethnicity, 
                          random = ~ 1 | Semester, 
                          data = Q01_fixed, method = "ML")
compare_performance(imp_model_Q10_1_ml, lme_model_Q10_1_ml)
anova(imp_model_Q10_1_ml, lme_model_Q10_1_ml)
```

None of Semester, Gender, or Race/Ethnicity meet the 0.05 alpha threshold.

### Q10_02

```{r Q02 model 2, echo=FALSE}
print(Q10TextClean$Question[02])
Q02_select <- Q10_demo_long %>%
  rename(Race_Ethnicity = `Race/Ethnicity`) %>%
  filter(Question == "Q02") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q02_model <- glm(data = Q02_select, 
                 5-as.numeric(Response) ~ Semester + Gender + Race_Ethnicity)
summary(Q02_model)
Anova(Q02_model, type = "3", test.statistic = "F")

# Testing a glmm approach 
lmer_model_Q10_2 <- lmer(5-as.numeric(Response) ~ 
                           Gender + Race_Ethnicity + (1 | Semester), data = Q02_select)
summary(lmer_model_Q10_2)
Anova(lmer_model_Q10_2, type = "3", test.statistic = "F")

# Fit both models with ML
imp_model_Q10_2_ml <- gls(5-as.numeric(Response) ~ Gender + Race_Ethnicity, 
                          data = Q02_select, method = "ML")
summary(imp_model_Q10_2_ml)
lme_model_Q10_2_ml <- lme(fixed = 5-as.numeric(Response) ~ Gender + Race_Ethnicity, 
                          random = ~ 1 | Semester, 
                          data = Q02_select, method = "ML")
summary(lme_model_Q10_2_ml)
compare_performance(imp_model_Q10_2_ml, lme_model_Q10_2_ml)
anova(imp_model_Q10_2_ml, lme_model_Q10_2_ml)
```

Semester meets the cutoff.

## Summary of mixed effects model

We are unable to incorporate Classroom or Section as a random effect in this set of models to protect the anonymity of the students. 
We had previously determined that combining student demographic information with instructor, semester, or section information results in unique combinations that allow identification of individual students. 

I did explore using semester as a random effect instead of a fixed effect, but it did not improve the model (by AICc) and did not allow differences in demographics to be unmasked regardless of whether a significant difference was found in the glm for semester.

### Q10_03

```{r Q03 model 2, echo=FALSE}
print(Q10TextClean$Question[03])
Q03_select <- Q10_demo_long %>%
  filter(Question == "Q03") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q03_model <- glm(data = Q03_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q03_model)
Anova(Q03_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_04

```{r Q04 model 2, echo=FALSE}
print(Q10TextClean$Question[04])
Q04_select <- Q10_demo_long %>%
  filter(Question == "Q04") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q04_model <- glm(data = Q04_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`) 
Anova(Q04_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_05

```{r Q05 model 2, echo=FALSE}
print(Q10TextClean$Question[05])
Q05_select <- Q10_demo_long %>%
  filter(Question == "Q05") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q05_model <- glm(data = Q05_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`) 
summary(Q05_model)
Anova(Q05_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_06

```{r Q06 model 2, echo=FALSE}
print(Q10TextClean$Question[06])
Q06_select <- Q10_demo_long %>%
  filter(Question == "Q06") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q06_model <- glm(data = Q06_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q06_model)
Anova(Q06_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_07

```{r Q07 model 2, echo=FALSE}
print(Q10TextClean$Question[07])
Q07_select <- Q10_demo_long %>%
  filter(Question == "Q07") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q07_model <- glm(data = Q07_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q07_model)
Anova(Q07_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_08

```{r Q08 model 2, echo=FALSE}
print(Q10TextClean$Question[08])
Q08_select <- Q10_demo_long %>%
  filter(Question == "Q08") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q08_model <- glm(data = Q08_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q08_model)
Anova(Q08_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_09

```{r Q09 model 2, echo=FALSE}
print(Q10TextClean$Question[09])
Q09_select <- Q10_demo_long %>%
  filter(Question == "Q09") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q09_model <- glm(data = Q09_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q09_model)
Anova(Q09_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_10

```{r Q10 model 2, echo=FALSE}
print(Q10TextClean$Question[10])
Q10_select <- Q10_demo_long %>%
  filter(Question == "Q10") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q10_model <- glm(data = Q10_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q10_model)
Anova(Q10_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_11

```{r Q11 model 2, echo=FALSE}
print(Q10TextClean$Question[11])
Q11_select <- Q10_demo_long %>%
  filter(Question == "Q11") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q11_model <- glm(data = Q11_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q11_model)
Anova(Q11_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_12

```{r Q12 model 2, echo=FALSE}
print(Q10TextClean$Question[12])
Q12_select <- Q10_demo_long %>%
  filter(Question == "Q12") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q12_model <- glm(data = Q12_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q12_model)
Anova(Q12_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_13

```{r Q13 model 2, echo=FALSE}
print(Q10TextClean$Question[13])
Q13_select <- Q10_demo_long %>%
  filter(Question == "Q13") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q13_model <- glm(data = Q13_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q13_model)
Anova(Q13_model, type = "3", test.statistic = "F")
```

Semester meets the cutoff.

### Q10_14

```{r Q14 model 2, echo=FALSE}
print(Q10TextClean$Question[14])
Q14_select <- Q10_demo_long %>%
  filter(Question == "Q14") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q14_model <- glm(data = Q14_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q14_model)
Anova(Q14_model, type = "3", test.statistic = "F")
```

Semester meets the cutoff.

### Q10_15

```{r Q15 model 2, echo=FALSE}
print(Q10TextClean$Question[15])
Q15_select <- Q10_demo_long %>%
  filter(Question == "Q15") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q15_model <- glm(data = Q15_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q15_model)
Anova(Q15_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_16

```{r Q16 model 2, echo=FALSE}
print(Q10TextClean$Question[16])
Q16_select <- Q10_demo_long %>%
  filter(Question == "Q16") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q16_model <- glm(data = Q16_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q16_model)
Anova(Q16_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_17

```{r Q17 model 2, echo=FALSE}
print(Q10TextClean$Question[17])
Q17_select <- Q10_demo_long %>%
  filter(Question == "Q17") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q17_model <- glm(data = Q17_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q17_model)
Anova(Q17_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_18

```{r Q18 model 2, echo=FALSE}
print(Q10TextClean$Question[18])
Q18_select <- Q10_demo_long %>%
  filter(Question == "Q18") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q18_model <- glm(data = Q18_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`) 
summary(Q18_model)
Anova(Q18_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_19

```{r Q19 model 2, echo=FALSE}
print(Q10TextClean$Question[19])
Q19_select <- Q10_demo_long %>%
  filter(Question == "Q19") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q19_model <- glm(data = Q19_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q19_model)
Anova(Q19_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_20

```{r Q20 model 2, echo=FALSE}
print(Q10TextClean$Question[20])
Q20_select <- Q10_demo_long %>%
  filter(Question == "Q20") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q20_model <- glm(data = Q20_select, 
                 5-as.numeric(Response) ~ Semester + Gender + `Race/Ethnicity`)
summary(Q20_model)
Anova(Q20_model, type = "3", test.statistic = "F")
```

None meet the cutoff.

### Q10_21

I tried the lme here too, because this question had one of the strongest gender/race/ethnicity contributions.

```{r Q21 model 2, echo=FALSE}
print(Q10TextClean$Question[21])
Q21_select <- Q10_demo_long %>%
  rename(Race_Ethnicity = `Race/Ethnicity`) %>%
  filter(Question == "Q21") %>%
  filter(ClassYear == "First") %>% na.omit() 
Q21_model <- glm(data = Q21_select, 
                 5-as.numeric(Response) ~ Semester + Gender + Race_Ethnicity)
summary(Q21_model)
Anova(Q21_model, type = "3", test.statistic = "F")

# Testing a glmm approach 
lmer_model_Q10_21 <- lmer(5-as.numeric(Response) ~ 
                           Gender + Race_Ethnicity + (1 | Semester), data = Q21_select)
summary(lmer_model_Q10_21)
Anova(lmer_model_Q10_21, type = "3", test.statistic = "F")

# Fit both models with ML
imp_model_Q10_21_ml <- gls(5-as.numeric(Response) ~ Gender + Race_Ethnicity, 
                          data = Q21_select, method = "ML")
summary(imp_model_Q10_21_ml)
lme_model_Q10_21_ml <- lme(fixed = 5-as.numeric(Response) ~ Gender + Race_Ethnicity, 
                          random = ~ 1 | Semester, 
                          data = Q21_select, method = "ML")
summary(lme_model_Q10_21_ml)
compare_performance(imp_model_Q10_21_ml, lme_model_Q10_21_ml)
anova(imp_model_Q10_21_ml, lme_model_Q10_21_ml)
```

None meet the cutoff. 

## Summary

**UPDATED TO INDICATE THE EFFECT OF SEPARATING ASIAN STUDENTS**

The reanalysis shows that neither Gender or Race/Ethnicity were significant in any of the models.

*Indicates stayed the same*

Note that only first-year students are included in this analysis.

Most of the responses showed a dependence on the semester, although the significance was sometimes marginal. 
This needs to be interpreted carefully as the responses in the Spring semester, if different, were always less positive than in the Fall. 
That is, the students in the Spring perceived less of a gain in these measures due to the CURE Lab than those in the Fall semester. 
This is consistent with the hypothesis that BIO Seminar provided some gain in these measures and, therefore, the gains due to the CURE Lab were smaller. 

Questions that showed dependence on the Semester, but not Race or Gender:

*2*   
4 <- NOW NONE 
*13*    
*14*    
15  <- NOW NONE   
16   <- NOW NONE  

Question that showed dependence on Gender and Race, but not Semester:

1 <- NOW NONE

Question that showed dependence on Semester and Race, but not Gender: 

21 <- NOW NONE

Question that showed dependence on Semester and Gender, but not Race: 

7 <- NOW NONE

Questions that showed dependence on Race, Gender, and the interaction between Race and Gender, but not Semester:

6 <- NOW NONE
9 <- NOW NONE
12 <- NOW NONE

Questions that did not depend on Semester, Race, or Gender:

*3*   
*5* 
*8*   
*10*    
*11*    
*17*    
*18*    
*19*    
*20*

Here is the list of questions for reference:

Preface: In this section of the survey you will be asked to consider a variety of possible benefits you may have gained from your research experience. If for any reason you prefer not to answer, or consider the question irrelevant to you, please choose the "Not applicable / Prefer not to answer" option 

 [1] "Clarification of a career path"                                      
 [2] "Skill in the interpretation of results"                              
 [3] "Tolerance for obstacles faced in the research process"               
 [4] "Readiness for more demanding research"                               
 [5] "Understanding how knowledge is constructed"                          
 [6] "Understanding of the research process in your field"                 
 [7] "Ability to integrate theory and practice"                            
 [8] "Understanding of how scientists work on real problems"               
 [9] "Understanding that scientific assertions require supporting evidence"
[10] "Ability to analyze data and other information"                       
[11] "Understanding science"                                               
[12] "Learning ethical conduct in your field"                              
[13] "Learning laboratory techniques"                                      
[14] "Ability to read and understand primary literature"                   
[15] "Skill in how to give an effective oral presentation"                 
[16] "Skill in science writing"                                            
[17] "Self-confidence"                                                     
[18] "Understanding of how scientists think"                               
[19] "Learning to work independently"                                      
[20] "Becoming part of a learning community"                               
[21] "Confidence in my potential to be a teacher of science"

## Final Figures


### 2026 Final Figure 6

*2*   
*13*    
*14*  

```{r Figure 6, fig.height=3, echo=FALSE}
Q10_demo_semester <- Q10_demo_long %>%
  filter(Question %in% c('Q02', 'Q13','Q14'))
ggplot(Q10_demo_semester) +
  geom_bar(aes(x = Semester, fill = Response), position = 'fill', width = 0.75) +
  facet_grid(as.factor(Q10_demo_semester$Question)) +
  coord_flip() +
  ylab('Proportion') +
  xlab('Semester') +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

### 2026 Final Figure 7 (Was 8)

Everything except 
*2*   
*13*    
*14*  

```{r Figure 7, fig.height=4, echo=FALSE}
Q10_demo_none <- Q10_demo_long %>%
  filter(Question %notin% c('Q02', 'Q13','Q14'))
ggplot(Q10_demo_none) +
  geom_bar(aes(x = fct_rev(Question), fill = Response), width = 0.75) +
  coord_flip() +
  ylab('Proportion') +
  xlab(NULL) +
  fill_palette(c("#21327b","#3c54cd","#6598f8","#b0cafb","#FFFEFE")) +
  scale_x_discrete(na.translate = FALSE) +
  theme_gray()
```

## Stats Summary Table

```{r}
# 1. Automatically gather all 21 models into a single named list
# This looks for Q01_model, Q02_model, ... Q21_model in your environment
model_names <- sprintf("Q%02d_model", 1:21)
model_list <- mget(model_names, envir = .GlobalEnv)

# 2. Loop through the models, run ANOVA, and bind the results
anova_table <- map_dfr(model_list, function(model) {
  
  # Run the Type III ANOVA
  res <- car::Anova(model, type = "3", test.statistic = "F")
  
  # Convert the ANOVA matrix to a data frame and grab the row names
  as.data.frame(res) %>% 
    rownames_to_column(var = "Variable")
  
}, .id = "Question") %>% 
  
  # 3. Filter down to the specific variables you care about
  filter(Variable %in% c("Semester", "Gender", "`Race/Ethnicity`")) %>% 
  
  # 4. Keep only the columns you need and rename them for convenience
  select(Question, Variable, F_value = `F values`, p_value = `Pr(>F)`) %>% 
  
  # 5. Pivot the table wider so each variable gets its own F and p columns
  pivot_wider(
    names_from = Variable,
    values_from = c(F_value, p_value),
    names_glue = "{Variable}_{.value}"
  ) |>
  select(
    Question,
    Semester_F_value, Semester_p_value,
    Gender_F_value, Gender_p_value,
    `\`Race/Ethnicity\`_F_value`, `\`Race/Ethnicity\`_p_value`
  )

# View your final consolidated table

write_tsv(anova_table, file = "Post_Benefits_ANOVA.tsv")
kable(anova_table)
```

